### 2023-03-24 paper/admin/cover_letter.tex
copying in old draft of paper + supplement

\title{Psychological Science Submission Letter}
%
% See http://texblog.org/2013/11/11/latexs-alternative-letter-class-newlfm/
% and http://www.ctan.org/tex-archive/macros/latex/contrib/newlfm
% for more information.
%
\documentclass[10pt,stdletter,orderfromtodate,sigleft]{newlfm}
\usepackage{blindtext, xfrac, animate, hyperref, pxfonts}

  \setlength{\voffset}{0in}

\newlfmP{dateskipbefore=0pt}
\newlfmP{sigsize=20pt}
\newlfmP{sigskipbefore=10pt}

\newlfmP{Headlinewd=0pt,Footlinewd=0pt}

\namefrom{Jeremy R. Manning, Ph.D.}
\addrfrom{
	Dartmouth College\\
    Department of Psychological \& Brain Sciences\\
    HB 6207 Moore Hall\\
	Hanover, NH  03755}

\addrto{}
\dateset{\today}

\greetto{To the editors of \textit{Psychological Science}:}

\closeline{Sincerely,}

\begin{document}
\begin{newlfm}
We have enclosed our manuscript entitled \textit{Feature-based and
  location-based volitional covert attention affect memory at different timescales}, which we wish
to submit for publication as a Research Article in
\textit{Psychonomic Bulletin \& Review}.

Our manuscript reports two experiments that examine how feature-based
and location-based attention affect recognition memory.  We asked our
participants to view a series of composite (blended face-scene) image
pairs.  We instructed the participants to focus their attention to a
specific image category (face or scene) and location (left or right)
without moving their eyes from a central fixation point.  The two
experiments differed in how often we changed the attention cue.  We
found that the memory consequences of location-based attention were
measurable after just a single attention cue instruction
(5.5~seconds), and persisted for at least 2~minutes.  Our data suggest
that location-based attention enhances memory encoding at the attended
location.  By contrast, feature-based attention must be sustained for
an extended interval to substantially affect memory.  Our data suggest
that feature-based attention suppresses the encoding into memory of
unattended stimulus features.

The impact of attention on memory is of central importance to a wide
variety of scientifically and socially current issues.  For example,
the interplay between attention and memory affects how we remember our
ongoing experiences in everyday life, how students learn in the
classroom (and which teaching strategies might be most effective), how
(or whether) we recognize a face we notice in a crowd and
happen to encounter later, and so on.  These issues also relate to
attention disorders (e.g., ADD, ADHD) and memory disorders
(e.g., age-related memory impairment, Alzheimer's, etc.).  Discovering
the mechanisms that underlie how our experiences are encoded into
memories can lead to new tools for identifying when those mechanisms
are not operating within their expected parameters.

We have suggested the following scientists as expert reviewers: Marvin
Chun (Marvin.Chun@Yale.edu), Brice Kuhl (bkuhl@uoregon.edu), Joel Voss (Joel-Voss@Northwestern.edu),
Edward Vogel (Ed\-Vogel@UChi\-ca\-go.edu), and Judith Fan
(jefan@ucsd.edu).  We have also published and documented all of our
experimental stimuli, code, and data, along with the code used to
generate the figures and analyses we report in our manuscript.  These
may be found at
\href{https://github.com/ContextLab/attention-memory-task}{\texttt{https://github.com/ContextLab/attention-memory-task}}.

Thank you for considering our manuscript for publication in
Psychonomic Bulletin \& Review.

\end{newlfm}
\end{document}

### 2023-03-24 paper/main.tex
copying in old draft of paper + supplement

\documentclass[english]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{apacite}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage[utf8]{inputenc}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage[left]{lineno}
\usepackage{soul}
\usepackage{setspace,caption}
\doublespacing
\captionsetup[figure]{labelsep=period,labelfont=it,justification=justified,
 singlelinecheck=false,font=doublespacing}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\linenumbers

\newcommand{\familiarity}{S1}
\newcommand{\fixation}{S2}
\newcommand{\timecourseCuedCategory}{S3}
\newcommand{\timecourseUncuedCategory}{S4}
\newcommand{\timecourseCuedLocation}{S5}
\newcommand{\timecourseUncuedLocation}{S6}
\newcommand{\timecourseNovel}{S7}
\newcommand{\timecourseDiff}{S8}

\begin{document}

\title{Category-based and location-based volitional covert attention affect memory at different timescales}

\author{Kirsten Ziman$^1, 2$,
Madeline R. Lee$^1$,
Alejandro R. Martinez$^1$,\\
Ethan D. Adner$^1$,
and
Jeremy R. Manning\textsuperscript{$1, \dagger$}\\[0.1in]$^1$Dartmouth College\\
$^2$Princeton University\\
\textsuperscript{$\dagger$}Address correspondence to jeremy.r.manning@dartmouth.edu}

\maketitle

\begin{abstract}

Our ongoing subjective experiences, and our memories of those experiences, are
shaped by our prior experiences, goals, and situational understanding. These
factors shape how we allocate our attentional resources over different aspects
of our ongoing experiences. These attentional shifts may happen overtly (e.g.,
when we change where we are looking) or covertly (e.g., without any explicit
physical manifestation). Additionally, we may attend to what is happening at a
specific spatial location (e.g., because we think something important is
happening there) or we may attend to particular features irrespective of their
locations (e.g., when we search for a friend's face in a crowd versus a
location on a map). We ran a covert attention experiment with two conditions
that differed in how long they asked participants to maintain the focus of the
categories and locations they were attending. Later, the participants performed
a recognition memory task for attended, unattended, and novel stimuli.
Participants were able to shift the location of their covert attentional focus
more rapidly than they were able to shift their focus of covert attention to
stimulus categories, and the effects of location-based attention on memory were
longer-lasting than the effects of category-based attention.

\noindent\textbf{Keywords: covert attention, spatial attention, category-based
attention, recognition memory, perception}

\end{abstract}

\section*{Introduction}

Our brains' cognitive systems detect and exploit patterns in our prior and
ongoing experiences, enabling us to function and adapt in an ever-changing
world. However we do not attend to or treat all types of remembered or incoming
information equally, and our ability to flexibly adapt our thinking and
behaviors can vary markedly with the specific set of concepts or tasks relevant
to a given setting or situation~\citep{ChunTurk07, AlyTurk17, HardNade09,
RangRitc12}. There is also substantial variability across people with respect
to which aspects of experience (sensory, social, emotional, etc.) are noticed,
discriminated between, and acted upon~\citep{HuntEtal89}. This implies that the
same physical (objective) experience may give rise to very different perceived
(subjective) experiences across people~\citep{FreeSimo11, ChanEtal18}.

The aspects of our experience we attend may be under our volitional control or
may be unconscious or automatic~\citep{JacoEtal92}. Both volitional and
unconscious attention may be expressed overtly, for example through intentional
eye movements~\citep{HoffSubr95} or covertly, without any volitional physical
change~\citep{EngbKlie03}. Prior work has explored the similarities and
differences in the neural basis of overt versus covert
attention~\citep{PosnEtal87, HuntKing03} as well as the behavioral and neural
underpinnings of volitional versus unconscious attention~\citep{DijkAart10} and
their differential effects on memory. There is a general consensus that
sustained volitional attention enhances memory relative to unconscious
attentional processes~\citep{UncaEtal11, GoloEtal13}. However, volitional
attention takes many forms, such as attention to particular spatial locations
or attention to particular visual features or other stimulus properties. How
different \textit{types} of volitional attention combine (or compete) to
enhance memory remains an open question. Volitional covert attention is of
particular interest in that it allows us to dynamically and intentionally
manipulate our experience, even when our sensory input remains largely
static~\citep[i.e., constant physical stimuli, retinal image, etc.][]{YiEtal06,
OcraEtal99}.

Here we examine the ways different types of volitional covert attention
interact to affect memory. We designed an experimental
paradigm~\citep[following][]{Posn80} that asked participants to attend to a
series of presented composite image pairs while keeping their gaze fixed on a
central point. The image pairs comprised a left and right image, each
constructed by blending an image of a face and scene. The stimuli and
presentation durations were constant across the two experiments, but the
experiments differed in how often we asked participants to change the focus of
their attention with respect to image category (face versus scene) and image
location (left versus right). After the participants attended to a series of
images, we used a recognition memory test to assess which aspects of the
presented images had been encoded into memory. In both experiments we found
that the images participants covertly attended to were better recognized than
other images, supporting the notion that attention enhances memory
encoding~\citep[i.e., they rated attended images as more familiar than
unattended images][]{Yone02}. After maintaining the focus of attention to a
single image category and location (Sustained Attention Experiment),
participants also recognized the attended-category image at the unattended
location, and (to a lesser extent) the unattended-category image at the
attended location. After more rapidly varying their focus of attention
(Variable Attention Experiment), participants showed a similar boost in
recognition for the unattended-category image at the attended location, but
they did not recognize images at the unattended location. This suggests that
participants were able to shift the location of their covert attentional focus
more rapidly than they were able to shift their focus of covert attention to
stimulus features. We also found differences in the timecourses of these memory
effects, suggesting that the impact of location-based attention on memory
persists on the order of several seconds longer than the impact of
feature-based attention.

\section*{Materials and methods}

We ran a total of 53 participants in across two experimental conditions
(Fig.~\ref{fig:paradigm}). The two conditions differed in how often we
cued participants to change the focus of their attention. All code and
documentation pertaining to our experiments and analyses, along with the
experimental stimuli and data, may be downloaded from
\url{http://www.github.com/ContextLab/attention-memory-task}.

\textbf{JRM STOPPED HERE}

\begin{figure*}[tp]
  \centering
  \includegraphics[width=1\textwidth]{figures/paradigm_and_key.pdf}

  \caption{\textbf{Paradigm overview.} \textbf{a.} Composite face/scene image.
  \textbf{b.} A single pair of composite images and a central fixation cross.
  \textbf{c.} Timecourse of an attention cue practice trial (3 total).
  \textbf{d.} Timecourse of a practice trial for the reaction time task (3
  total). \textbf{e.} Familiarity judgement practice trial (4 total).
  \textbf{f.} Timecourse of one Sustained Attention Experiment presentation
  phase and memory phase block. \textbf{g.} Timecourse of one Variable
  Attention Experiment presentation phase and memory phase block. \textbf{h.}
  Breakdown of presented (old) and novel stimuli that matched (or did not
  match) the focus of participants' feature-based attention and/or
  location-based attention. Filled colored circles on the right denote that the
  given stimulus (matching the corresponding color; images shown on the left)
  satisfied the indicated property. Open circles denote that the given stimulus
  did \textit{not} satisfy the indicated property. Gray circles denote
  properties that are undefined for the given stimulus.}

\label{fig:paradigm}
\end{figure*}

\subsection*{Participants}
\subsubsection*{Sustained Attention Experiment}
Sixty students, enrolled in one or more undergraduate psychology courses at Dartmouth College, participated in the Sustained Attention Experiment for course credit.  The participants' ages ranged from 18--21; 42 participants were female, 17 were male, and one identified as gender non-binary.  All participants had self-reported normal or corrected-to-normal vision, memory, and attention.  Participants gave written consent to enroll in the study under a protocol approved by the Committee for the Protection of Human Subjects at Dartmouth College.

\subsubsection*{Variable Attention Experiment}
Fifty-three individuals participated in the Variable Attention Experiment for either cash ($n=13$) or course credit ($n=40$; students enrolled in one or more undergraduate psychology courses at Dartmouth College).  The participants' ages ranged from 18--23; 34 participants were female and 19 were male.  All participants had self-reported normal or corrected-to-normal vision, memory, and attention.  Participants gave written consent to enroll in the study under a protocol approved by the Committee for the Protection of Human Subjects at Dartmouth College.

\subsection*{Stimulus selection and presentation}
Participants viewed photographs of faces, scenes, and composite images each comprising an equal blend of one face image and one scene image.  The pool of 360 face images included photographs of adult human male and female faces selected from the FERET database~\citep{PhilEtal98}.  The pool of 360 scene images included photographs of indoor and outdoor scenes selected from the SUN database~\citep{XiaoEtal10}.  The images we used from both databases came from a stimulus subset that was manually curated by Megan deBettencourt (personal communication).  All images were resized to $256 \times 256$ pixels, converted to greyscale, and processed so that every image was matched for mean contrast and intensity.  We selected 20 face images and 20 scene images from the stimulus pool to use in the instructional and practice phases of the experiments (Fig.~\ref{fig:paradigm}a--e).

In addition to the face and scene images, we presented (in white) attention cues to direct the participant's focus of attention.  The attention cues comprised a stylized icon of a face or mountain peaks, directing attention to the face or scene component of the images, respectively; and a left- or right-facing angled bracket, directing attention to the left or right image, respectively (e.g., Figs.~\ref{fig:paradigm}c, d, f, and g).

 Both experiments were conducted in a sound- and light-attenuated testing room containing a chair, desk, and 27-inch iMac desktop computer (display resolution: $2048 \times 1152$).  The participant sat in the chair and rested their chin on a chin rest located 60~cm from the display.  The active portion of the display screen occupied 52.96$^\circ$ (width) and 31.28$^\circ$ (height) of the participant's field of view from the chin rest.  Stimuli were sized to occupy $6.7^\circ$ (width and height) of the participant's field of view from the chin rest.  We maintained a black background (with any text displayed in white) throughout the experiment.

\subsection*{Eyetracking}
We recorded participants' eye gaze positions using a desk-mounted video-based eyetracker with a spatial resolution of 0.1$^\circ$ visual angle root mean squared error and a sampling rate of 30~Hz (Eye Tribe, The Eye Tribe, Copenhagen, Denmark).  We calibrated the eyetracker using a 9-point gaze pattern.  As described below, we re-calibrated the eyetracker at regular intervals throughout the experiments to protect against camera drift.

\subsection*{Experimental paradigm}
Both experimental paradigms comprised a practice phase followed by a series of eight task blocks.  Each task block was in turn comprised of a presentation phase and a memory phase.  The practice and presentation phases differed across the two experiments, and the memory phases were identical across the two experiments.  Both experiments were implemented using PsychoPy~\citep{PeirEtal19}.

\subsubsection*{Practice phase}
Several participants in pilot versions of our experiments reported that they found it difficult to modulate the focus of their attention quickly on command.  We therefore designed a practice sequence to orient the participant to the process of quickly modulating the focus of their attention without moving their eyes.  The experimenter remained in the testing room throughout the practice phase and answered any questions about the experiment.  The practice sequence builds up incrementally to provide a gradual on-ramping for the participant prior to beginning the main experimental tasks that we focused on in our analyses.

\paragraph{Practice shifting the focus of feature-based attention to elements of a single composite image.}
At the start of the practice phase, we instructed the participant to look at a single composite (face-scene blend) image at the center of the screen, and to try to bring the face component of the image into greater focus by attending to it (Fig.~\ref{fig:paradigm}a).  After pressing a button on the keyboard to indicate that they had done so, we displayed a second composite image and instructed the participant to bring the scene component of the new composite image into focus.  Again, they pressed a button to indicate that they had done so.

\paragraph{Practice shifting the focus of feature-based and location-based attention while viewing two composite images.}
Next, we asked the participant to stare at a fixation cross presented in the center of the screen while two composite images were displayed on the left and right side of the screen, respectively.  We first instructed the participant to attend to the scene component of the left image without moving their eyes.  Participants practiced shifting their attention, and they pressed a button on the keyboard to indicate that they had done so. We then displayed a second pair of composite images and instructed the participant to attend to the face component of the right image. Again, the participant shifted their attention in a self-paced manner, and pressed a button to indicate when they had successfully done so (Fig.~\ref{fig:paradigm}b).

\paragraph{Practice sustaining feature-based and location-based attention over a series of composite image pairs.}
We asked participants in the Sustained Attention Experiment to practice holding their focus of feature-based and location-based attention constant (to the face component of the right image) while viewing a series of three composite image pairs presented in succession (Fig.~\ref{fig:paradigm}c).

\paragraph{Practice varying feature-based and location-based attention over a series of composite image pairs.}
We asked participants in the Variable Attention Experiment to practice varying their focus of feature-based and location-based attention while viewing a series of three composite image pairs presented in succession (Fig.~\ref{fig:paradigm}c).

\paragraph{Practice reaction time probe.}
After practicing modulating their focus of attention to a series of composite image pairs, we introduced a reaction time probe after each image presentation, whereby we presented either an $\times$ or $\circ$ on either the left or the right of the screen (Fig.~\ref{fig:paradigm}d).  We asked the participant to press the \texttt{1} key as quickly as possible when they saw an $\times$, or the \texttt{3} key as quickly as possible when they saw an $\circ$.  We did not impose a time limit on their responses, other than asking participants to respond as quickly as they were able.  Participants practiced three trials of modulating their focus of attention to a pair of composite images (3~s), and reacting as quickly as possible to the $\times$ or $\circ$ symbol presented after each composite image pair.  The reaction time probe was intended to keep participants continually engaged in modulating the focus of their attention.

\paragraph{Practice recognition memory task.}
Finally, we asked the participant to practice reporting familiarity on a recognition memory task (Fig.~\ref{fig:paradigm}e).  We presented a single face or scene image at the center of the screen, and asked them to press a button to indicate how ``familiar'' the image seemed: \texttt{1} (very confident they had not seen the image), \texttt{2} (somewhat confident they had not seen the image), \texttt{3} (somewhat confident they had seen the image), or \texttt{4} (very confident that they had seen the image).  We instructed the participant to go with their ``gut reaction'' in the event that they were unsure of how to respond.  We allowed the participant up to 2~s to provide their response.  We gave participants a total of four practice images to rate.

After completing the practice phase of the experiment, the participant read the instructions for the task blocks (described next).  The experimenter gave participants a chance to ask any remaining questions about the experiment.  After answering the participant's questions, the experimenter calibrated the eyetracker and exited the testing room.

\subsubsection*{Task blocks}
During each task block we asked the participant to modulate their attention while viewing a series of 10 composite image pairs (each followed by a reaction time probe), and then we tested the participant's memory using 40 familiarity judgements.  Each participant completed a total of eight task blocks.

\paragraph*{Sustained Attention Experiment: presentation phase.} Participants viewed an attention cue (1.5~s) instructing them to attend to either the face or scene component of either the left or right images in each to-be-viewed composite pair.  Next we displayed 10 composite images in succession (each preceded by a fixation cross and proceeded by a reaction time probe).  Complete timing information is displayed in Figure~\ref{fig:paradigm}f.  All possible attention cue pairs appeared exactly twice across the eight task blocks.

\paragraph*{Variable Attention Experiment: presentation phase.}  Participants viewed a succession of 10 attention cues (1.5~s), each followed by a fixation cross (1~s), composite image (3~s), and a reaction time probe (Fig.~\ref{fig:paradigm}g).  The attention cues were selected pseudorandomly across trials within each block, with the constraints that no single attention cue pair could appear more than three times across the 10 composite image pairs within a single task block.

\paragraph*{Memory phase.} After the presentation phase of each task block, we asked the participant to rate the familiarity (on a 1--4 scale, as during the practice phase) of a succession of face and scene images.  Each image was preceded by a 1~s fixation cross, and participants had up to 2~s to input their rating of each image.  Participants made a total of 40 familiarity judgements, about 20 face images and 20 scene images.  Of these, 20 of the images (10 faces and 10 scenes) were drawn randomly from the (attended and unattended) composite images that the participant had viewed during the presentation phase.  The remaining 20 images (10 faces and 10 scenes) were novel images that the participant had not encountered during any part of the experiment.  At the end of each memory block, the participant was given the opportunity to take a short break.  When they were ready to continue with the next task block, they indicated their readiness to the experimenter.  The experimenter then entered the testing room, re-ran the eyetracker calibration sequence, and exited the testing room prior to the next task block.

\section*{Results}
We ran two volitional covert attention experiments; in the Sustained Attention Experiment we asked participants to \textit{sustain} the focus of their attention over a succession of 10 stimulus presentations per block whereas in the Variable Attention Experiment we asked participants to \textit{vary} their focus of attention with each new stimulus (also for a total of 10 stimulus presentations per block).  Each stimulus comprised a pair of composite images (one on the left and one on the right side of the display), where each composite comprised an equal blend of a unique face and a unique scene image.  We followed the presentation phases of each experimental block with a memory phase, where participants performed a recognition memory task by rating the familiarity of previously experienced and novel face and scene images (see \textit{Materials and methods}, Fig.~\ref{fig:paradigm}).

We considered each image we probed in the memory phase with respect to whether (and how) the participant had experienced and/or attended to that image during the presentation phase (Fig.~\ref{fig:familiarity}).  For example, if a given face image had been presented as part of the composite image on the right of the screen following an \texttt{attend to the face on the right} instruction, then that face image would have been the focus of the participant's attention during one stimulus presentation.  The face image on the left (unattended side) during that trial would have been captured by feature-based attention, but not by location-based attention; and the scene image (unattended category) on the right during that trial would have been captured by location-based attention, but not by feature-based attention.  The scene image on the left during that trial remained outside of the focus of both feature-based and location-based attention.  In this way, we categorized each of the images that participants experienced during the presentation phases of each experiment in terms of whether they fell under the scope of feature-based and/or location-based attention.  We also categorized novel face and scene images that we asked participants to judge during the memory phase (i.e., images that the participant hadn't seen before) as belonging to the attention-cued or uncued category.  These novel images were intended to serve as a baseline for comparison.  For example, we sought to measure how people rated the familiarity of new images in general.  We also used differences in familiarity ratings between novel images of the attention-cued versus uncued categories to evaluate potential \textit{prospective} affects of modulating the focus of feature-based attention.

\begin{figure*}[tp]
  \centering
  \includegraphics[width=0.75\textwidth]{figures/familiarity}
  \caption{\textbf{Familiarity ratings for attended, unattended, and novel stimuli.}  Each split violin plot displays the distribution of within-participant average familiarity ratings given to faces (left, darker colors) and scenes (right, lighter colors) during the memory phases of each experiment.  As shown in the legend (bottom), the colors indicate whether each image had been viewed during the presentation phase (\texttt{old}) or not; whether the given images matched the \texttt{attended category}; and/or whether the given images matched the \texttt{attended location}.  The colored lines above each set of violin plots denote statistical differences  (\textbf{pos}itive or \textbf{neg}ative differences in mean, collapsing over image category, assessed via two-tailed $t$-tests) between the distributions centered on the endpoints of each line.  The line thicknesses denote $p$-values as indicated in the legend.  Asterisks denote differences between the face versus scene distributions (assessed via two-tailed $t$-tests).  Panel \textbf{a.} displays results from the Sustained Attention Experiment and panel \textbf{b.} displays results from the Variable Attention Experiment.  Figure~\familiarity~displays these results broken down by participant cohort.}
\label{fig:familiarity}
\end{figure*}

Participants in both experiments rated stimuli they attended as more familiar than unattended or novel stimuli (Fig.~\ref{fig:familiarity}; Sustained Attention Experiment: $t(59) = 13.42, p = 1.39 \times 10^{-19}, d = 1.73$; Variable Attention Experiment: $t(52) = 12.40, p = 3.70 \times 10^{-17}, d = 1.70$).  Participants in both experiments also rated attended scene stimuli as more familiar than attended face stimuli (Sustained Attention Experiment: $t(59) = 7.69, p = 1.85 \times 10^{-10}, d = 0.99$; Variable Attention Experiment: $t(52) = 7.08, p = 3.63 \times 10^{-9}, d = 0.97$).  These findings indicate that aspects of experience that are captured by the focus of attention are easier to recognize later, and that attention may preferentially benefit memory for some aspects of experience to a greater extent than other aspects of experience.

Participants in the Sustained Attention Experiment experiment also rated unattended images that matched the attended category as more familiar than unattended images that did not match the attended category (\textit{incidental feature-based attention}; $t(59) = 7.17, p = 1.40 \times 10^{-9}, d = 0.93$).  This pattern did not hold for participants in the Variable Attention Experiment ($t(52) = 0.44, p = 0.66, d = 0.06$).  Participants in both experiments displayed an incidental effect of location-based attention, whereby they rated unattended-category images at the attended location as more familiar than unattended-category images at the unattended location (Sustained Attention Experiment: $t(59) = 4.32, p = 6.05 \times 10^{-5}, d = 0.56$; Variable Attention Experiment: $t(52) = 2.57, p = 0.01, d = 0.35$).  This indicates that aspects of our experience that incidentally overlap with the focus of our location-based attention are easier to recognize later, even if those aspects do not fall within the intentional focus of our feature-based attention.

We defined the \textit{memory benefit of feature-based attention} as the difference in mean familiarity ratings of attended stimuli and unattended stimuli from the attended category versus the mean familiarity ratings of unattended stimuli from the unattended category.  Similarly, we defined the \textit{memory benefit of location-based attention} as the difference in mean familiarity ratings of attended stimuli and unattended stimuli from the attended location versus the mean familiarity ratings of unattended stimuli from the unattended location.  Participants in the Sustained Attention Experiment displayed a larger memory benefit of feature-based attention than location-based attention ($t(59) = 3.25, p = 1.91 \times 10^{-3}, d = 0.42$), whereas participants in the Variable Attention Experiment displayed a larger memory benefit of location-based attention ($t(52) = 1.70, p = 9.99 \times 10^{-2}, d = 0.23$).  This appeared to be driven in part by a response bias towards attended-category images.  For example, relative to the most recent attention cue, participants in the Sustained Attention Experiment rated attended-category novel images as more familiar than unattended-category novel images ($t(59) = 7.04, p = 2.35 \times 10^{-9}, d = 0.91$), whereas participants in the Variable Attention Experiment responded similarly to attended-category and unattended-category novel images ($t(52) = 0.23, p = 0.82, d = 0.03$).  The size of this attended-category response bias for novel images was reliably smaller than the memory benefits of feature-based attention in both experiments (Sustained Attention Experiment: $t(59) = 7.59, p = 2.68 \times 10^{-10}, d = 0.98$; Variable Attention Experiment: $t(52) = 6.74, p = 1.31 \times 10^{-8}, d = 0.93$).  This indicates that tuning the focus of feature-based attention with respect to how ongoing experience is encoded in memory takes longer than the duration of a single stimulus presentation (including fixation, roughly 5.5~s).  Further, once feature-based attention comes ``online,'' it affects how \textit{new} stimuli are processed.

We also compared the relative sizes of the memory benefits of feature-based attention and location-based attention across the two experiments.  Participants in the Sustained Attention Experiment displayed a larger difference between these two effects than did participants in the Variable Attention Experiment ($t(111) = 3.48, p = 7.24 \times 10^{-4}, d = 0.66$).  Further, the difference in mean familiarity ratings of attended-location images versus unattended images was greater for participants in the Variable Attention Experiment ($t(111) = 2.32, p = 0.02, d = 0.44$). The memory benefit of location-based attention reliably distinguished between attended-category versus unattended category images for participants in both experiments (Sustained Attention Experiment: $t(59) = 9.50, p = 1.68 \times 10^{-13}, d = 1.23$; Variable Attention Experiment: $t(52) = 9.72, p = 2.76 \times 10^{-13}, d = 1.33$).  This indicates that tuning the focus of location-based attention with respect to how ongoing experience is encoded into memory occurs faster than the duration of a single stimulus presentation.

We also compared reaction times to probes from the attended versus unattended side.  Participants in both experiments responded slightly faster on average to attended-side probes, although the differences did not reach significance (Sustained Attention Experiment: $t(59) = 1.03, p = 0.31, d = 0.13$; Variable Attention Experiment: $t(52) = 0.65, p = 0.52, d = 0.09$).  Participants in the Sustained Attention Experiment displayed a slightly larger (and not statistically significant) difference in attended-side versus unattended-side reaction times than participants in the Variable Attention Experiment ($t(111) = .87, p = 0.38, d = 0.20$).  Because none of these reaction time effects were statistically reliable, we are unable to draw meaningful conclusions about reaction times to the attention probes on the attended versus unattended side, nor are we able to draw meaningful conclusions about differences in those reaction times that might be due to sustained versus variable attention.

\begin{figure}[tp]
  \centering
  \includegraphics[width=\textwidth]{figures/exps1_2_xgaze.pdf}
  \caption{\textbf{Horizontal coordinates of visual fixations.}  Each violin plot displays a distribution of participant-wise average horizontal gaze positions relative to a presented image.  The coordinates have been normalized such that a value of 1.0 denotes the furthest onscreen coordinate from the central fixation point \textit{towards} the direction of the given image, and -1.0 denotes the furthest onscreen coordinate from the central fixation point \textit{away from} the direction of the given image.  The gray bars in each panel mark the boundaries of the presented images.  The violin plots are broken down by participants' familiarity ratings during the memory phases of each experiment, and by each image's relation to the attention cue while that image appeared onscreen.  Panel \textbf{a.} displays fixation data for the Sustained Attention Experiment and Panel \textbf{b.} displays fixation data for the Variable Attention Experiment.  Figure~\fixation~displays these results broken down by participant cohort.}
\label{fig:fixation}
\end{figure}

Given that participants in both experiments rated attended-location images from both the attended and unattended category as more familiar than unattended-location images, we wondered whether this was truly a consequence of covert attention, or whether it might be driven solely by where participants were looking. In other words, we sought to distinguish the memory effects of the focus of covert attention from the focus of visual gaze.  We used eyetracking to measure the horizontal positions of the participants' visual fixations while each pair of composite stimuli appeared onscreen (Fig.~\ref{fig:fixation}). For 94\% of presentation trials (Sustained Attention Task: $\frac{4531}{4800}$ trials; Variable Attention Task: $\frac{3972}{4240}$ trials), we collected viable gaze data for analysis. In the remaining trials, participant movement or other technical issues corrupted the gaze data. We found that, though they generally followed our instruction to keep their gaze fixed on the center of the screen, participants in both experiments exhibited a slight tendency to look towards the side of the screen they were attending to (Sustained Attention Task: $t(59) = 3.61, p = 6.31 \times 10^{-4}$; Variable Attention Task: $t(52) = 2.86, p = 6.06 \times 10^{-3}$). When we limited our analyses to trials with viable gaze data where participants successfully maintained fixation on the center of the screen within 4.28$^\circ$ visual angle (i.e., between the rightmost boundary of the left image and the leftmost boundary of the right image) we observed (numerical) memory benefits of feature-based attention in both experiments (Sustained Attention Experiment: $t(59) = 4.73, p = 1.96 \times 10^{-5}, d = 0.67$; Variable Attention Experiment: $t(52) = 0.64, p = 0.52, d = 0.09$) and location-based attention in the Sustained Attention Experiment, but not the Variable Attention Experiment (Sustained Attention Experiment: $t(59) = 0.67, p = 0.51, d = 0.09$; Variable Attention Experiment: $t(52) = -0.79, p = 0.43, d = 0.11$).  These analyses indicate that although the focus of covert attention can affect where people are looking, covert attention affects memory encoding beyond what may be accounted for by gaze position alone.

The preceding results indicate that volitional covert attention affects memory, and that feature-based and location-based covert attention may come online at different timescales.  We next sought to examine how long the memory effects of feature-based and location-based covert attention persist.  To gain additional insights into the timecourse of the impact of feature-based and location-based attention on memory, we used a sliding window analysis to measure how participants' familiarity ratings of attended, partially attended, unattended, and novel stimuli varied over the duration of the memory phases of both experiments.  During each block within the memory phases of each experiment, participants made familiarity judgements about a total of 40 images (20 old images and 20 novel images).  We computed average familiarity ratings for images appearing in each position of the memory stimulus sequence (positions 1--40), as a function of how (or whether) they were attended during the preceding presentation phase (old images) or whether they matched the category of the most recent attention cue (novel images), for overlapping 20-image sliding windows (Figs.~\ref{fig:familiarity_timecourse_category}, \ref{fig:familiarity_timecourse_location}, and \ref{fig:familiarity_timecourse_novel}). We first calculated these values for each participant, and then we averaged across participants.

\begin{figure*}[tp]
  \centering
  \includegraphics[width=1\textwidth]{figures/Cat_Cued_TimeSeries.pdf}
  \caption{\textbf{Familiarity ratings over time for images that matched the cued or uncued image category.}  Each curve reflects the average familiarity ratings for attended, unattended, and novel images (denoted in the legends on the right) within a succession of overlapping 20-image sliding windows.  Error ribbons denote 95\% confidence intervals, computed across participants.  Panels \textbf{a.} and \textbf{c.} display results from the Sustained Attention Experiment and Panels \textbf{b.} and \textbf{d.} display results from the Variable Attention Experiment.  The paired horizontal lines at the bottom of each panel denote timepoints when the given pair of curves was statistically distinguishable (i.e., the topmost line color was statistically greater than the bottommost line color at $\alpha = 0.05$, via a paired two-tailed $t$-test.)  The gray lines in Panels b and d reflect familiarity ratings of novel stimuli from both the most recently attended and unattended image categories.   Figures~\timecourseCuedCategory~and \timecourseUncuedCategory~display these results broken down by participant cohort.}
\label{fig:familiarity_timecourse_category}
\end{figure*}

Throughout the memory phase, participants from both experiments rated attended images as more familiar than category-matched unattended and novel images (Fig.~\ref{fig:familiarity_timecourse_category}, top row).  This indicates that the memory benefits of attending to specific stimulus features (versus category-general features) persist for at least as long as the duration of the memory phase (2~min).  Early in the memory phase, participants in the Variable Attention Experiment also rated category-matched unattended images as more familiar than novel images.  This pattern did not hold for participants in the Sustained Attention Experiment.  The short-lived boost in familiarity for attended-category images at the unattended location following variable (but not sustained) attention suggests that the timecourse of feature-based attention's impact on memory depends on how long the focus of feature-based attention has been held.

Participants in both experiments also rated unattended-category images at the attended location as more familiar than unattended-category images at the unattended location and novel unattended-category images (Fig.~\ref{fig:familiarity_timecourse_category}, bottom row).  This pattern persisted throughout the memory phases of both experiments.  This supports the notion that location-based attention enhances memory in a (partially) feature-independent way.  Participants in the Variable Attention Experiment also rated unattended-category images at the unattended location as (numerically) more familiar than novel images (though this pattern was only statistically reliable towards the middle of the memory phase).  This pattern did not hold for participants in the Sustained Attention Experiment.  Participants in the Sustained Attention Experiment rated unattended-category images (regardless of location or novelty status) as less familiar than participants in the Variable Attention Experiment (e.g., compare heights of the lines in the bottom left versus bottom right panels of Fig.~\ref{fig:familiarity_timecourse_category}).  This suggests that, after sustained feature-based attention to a particular image category, the encodings of stimuli from the unattended category are suppressed.  This suppression effect appears to persist at least as long as the memory phase of the experiment (2~min).  Further, the magnitude of this suppression effect appears to become stronger following longer-term sustained (versus shorter-term variable) feature-based attention.

\begin{figure*}[tp]
  \centering
  \includegraphics[width=\textwidth]{figures/Side_Cued_TimeSeries_2.pdf}
  \caption{\textbf{Familiarity ratings over time for images that matched the cued or uncued image location.}  This figure follows the same format and conventions as Figure~\ref{fig:familiarity_timecourse_category}.   Figures~\timecourseCuedLocation~and \timecourseUncuedLocation~display these results broken down by participant cohort.}
\label{fig:familiarity_timecourse_location}
\end{figure*}

We next examined how participants' familiarity ratings varied over the duration of the memory phases of each experiment as a function of the attended location.  Participants in the Sustained Attention Experiment rated attended-category images as more familiar, at both the attended and unattended locations (Fig.~\ref{fig:familiarity_timecourse_location}, left panels).  In contrast, participants in the Variable Attention Experiment rated attended-category images as more familiar than unattended-category images only at the attended locations (Fig.~\ref{fig:familiarity_timecourse_location}, right panels).  The primary difference in familiarity ratings between Sustained Attention Experiment versus Variable Attention Experiment participants was in how they rated unattended-category images.  Participants in the Variable Attention Task rated unattended-category images as more familiar than did participants in the Sustained Attention Task; this pattern persisted throughout the memory phase and held for images at both the attended and unattended locations (compare heights of blue lines in the left versus right panels of Fig.~\ref{fig:familiarity_timecourse_location}).  This suggests that lower familiarity ratings of unattended-category stimuli in the Sustained Attention Experiment are due to suppression of the encoding of unattended-category features (e.g., as opposed to enhancement of the encoding of attended-category features).  This suppression effect appears to build over an interval that is longer than the duration of a single stimulus presentation (5.5~s).

\begin{figure*}[tp]
  \centering
  \includegraphics[width=1\textwidth]{figures/Novel_Timecourse_Panels.pdf}
  \caption{\textbf{Familiarity ratings over time for attended-category and unattended-category novel images.}  The top panels of this figure follow the same formats and conventions as Figures~\ref{fig:familiarity_timecourse_category} and \ref{fig:familiarity_timecourse_location}.  The bottom panels display the differences between the timecourses of familiarity ratings of attended-category and unattended-category novel stimuli.  The error ribbons denote 95\% confidence intervals, computed across participants.  The dotted horizontal line in each panel denotes a difference of 0-- i.e., the value above which attended-category novel images were rated as more familiar than unattended-category novel images.  The black lines in the bottom panels display linear regression fits to the data (error ribbons denote 95\% confidence intervals).   Figures~\timecourseNovel~and \timecourseDiff~display these results broken down by participant cohort.}
\label{fig:familiarity_timecourse_novel}
\end{figure*}

Finally, we examined how participants in both experiments rated the familiarity of novel images.  These ratings provide insights into how modulating the focus of attention to \textit{prior} stimuli can affect the perception of \textit{future} stimuli.  We considered how participants rated novel stimuli that matched versus did not match the category (face or scene) of the most recent attention cue.  Participants in the Sustained Attention Experiment rated attended-category novel stimuli as more familiar than unattended-category novel stimuli throughout the entire memory phase (Fig.~\ref{fig:familiarity_timecourse_novel}a).  By contrast, participants in the Variable Attention Experiment rated attended-category and unattended-category novel images similarly throughout the memory phase (Fig.~\ref{fig:familiarity_timecourse_novel}b).  The difference in familiarity ratings between the two experiments primarily reflects that participants in the Variable Attention Experiment rated unattended-category novel images as more familiar than did participants in the Sustained Attention Experiment (e.g., compare blue lines in Fig.~\ref{fig:familiarity_timecourse_novel}a versus \ref{fig:familiarity_timecourse_novel}b).  This may indicate that the processing of unattended-category novel stimuli is suppressed following sustained attention (e.g., as opposed to enhancing the processing of attended-category novel stimuli).  The differences in familiarity between attended-category versus unattended-category novel images increased slightly but reliably throughout the memory phases of both experiments (Fig.~\ref{fig:familiarity_timecourse_novel}, bottom panels; slope of regression line fit to differences in Sustained Attention Experiment: $\beta = 2.05 \times 10^{-3}, p = 1.07 \times 10^{-14} $; slope of regression for Variable Attention Experiment: $\beta = 1.54 \times 10^{-3}, p = 5.63 \times 10^{-13} $).  This might reflect a process whereby the suppression of unattended features continues to build for a short duration even after the participant stops volitionally focusing on the attended features.

\section*{Discussion}
We ran two covert attention experiments that asked participants to sustain or vary the focus of their covert attention, respectively.  When participants held the focus of their feature-based (face versus scene) and location-based (left versus right) attention for a sustained interval, they judged stimuli they had seen as familiar when they overlapped with respect to the features and locations they had attended.  The increase in familiarity was larger for attended-feature images than attended-location images.  The increase also extended to novel stimuli from the attended image category.  By contrast, when participants varied the focus of their feature-based and location-based attention more rapidly, the boost in familiarity for feature-matched stimuli was smaller than that for location-matched stimuli, and did not extend to novel stimuli.  Our findings suggest that participants were able to more rapidly modulate their focus of location-based attention than their focus of feature-based attention.  The tuning of location-based attention appears to be mediated by enhanced encoding and faster processing at the attended location.  The tuning of feature-based attention appears to be mediated by a suppression in the encoding and processing of unattended stimulus features.  This suppression effect also affects how new stimuli are processed, and it persists for a longer duration following an interval when the focus of feature-based attention was held constant over a longer duration.  Taken together, our findings suggest that feature-based and location-based attention are mediated by different mechanisms and affect memory at different timescales (Fig.~\ref{fig:model}).

\begin{figure*}[tp]
  \centering \includegraphics[width=0.75\textwidth]{figures/discussion_schematic}
  \caption{\textbf{Timecourse of encoding and retrieval effects of feature-based and location-based attention.}  The focus of location-based attention (green) may be modulated quickly and rapidly enhances memory encoding for nearby stimuli.  The focus of feature-based attention (purple) is modulated more slowly, and serves to suppress unattended stimulus features.  The effects of location-based attention on memory persist for longer than the effects of feature-based attention.  Sustained attention (darker shading) yields more robust enhancement and suppression than shorter-term (variable) attention (light shading).  The vertical gray line on the left denotes the duration of a single stimulus presentation (the upper bound by which location-based attention begins to affect encoding, and the lower-bound by which feature-based attention begins to affect encoding).  The vertical gray line on the right separates encoding from immediate subsequent retrieval of the encoded information.}
\label{fig:model}
\end{figure*}

The notion that location-based attention operates at a faster timescale than feature-based attention is supported by prior work on the deployment of visual attention~\citep{SotoBlan04, StopEtal07}.  Our findings that location-based attention enhances the processing of attended stimuli whereas feature-based attention suppresses the processing of unattended stimuli is also consistent with prior work on location-based attention~\citep[e.g.,][]{IttiKoch01} and feature-based attention~\citep[e.g.,][]{MoheEtal14}.  Our finding that people better remember attended stimuli also follows prior work on interactions between attention and memory~\citep{PallWagn02, ChunTurk07, AlyTurk16, AlyTurk17, WittEtal18, MorrEtal14, BaleEtal19}.  Whereas much of this prior work focused on elucidating the neural basis of these interactions, our work extends these prior studies by elucidating the specific and separable behavioral impacts of feature-based attention (inhibition with a slow onset) and location-based attention (enhancement with a fast onset) on subsequent memory.  Both of these effects persisted throughout the 2~min memory phases of both experiments.  Therefore future work is needed to elucidate the longevity of these effects beyond 2 minutes.

Another important area for future study concerns how the flow of information between different brain structures is modulated according to the focus of volitional attention-- particularly with respect to pathways from primary sensory regions (e.g., V1, A1) to regions implicated in encoding ongoing experiences into memory (e.g, medial temporal lobe structures such as the hippocampus and entorhinal cortex, prefrontal cortex, etc.).  For example, several studies suggest that attention serves to modulate the \textit{gain} of specific neural circuits~\citep{TreuTruj99, ChanEtal02, EldaEtal13, SaliThie00}, effectively facilitating or inhibiting the flow of specific neural representations~\citep{VartEtal07, LaRoEtal14}.  Prior work suggests that feature-based attention may be supported by changes in connectivity with the thalamus~\citep{Schn11}, whereas location-based attention may be supported by changes in connectivity with primary visual cortex~\citep{NoudEtal10}.  That feature-based and location-based attention are mediated by different brain structures may explain why these different aspects of attention operate on different timescales and affect memory differently.  A strong test of this hypothesis would entail directly measuring neural activity patterns as people modulate their focus of attention (e.g., using functional magnetic resonance imaging or electroencephalography), and then using neural decoding approaches~\citep[e.g.,][]{HaxbEtal01, NormEtal06, MannEtal18} to follow how neural representations of attended (or unattended) stimuli are transfered from primary sensory regions, to higher order sensory regions, to memory areas.  If the effects of attention on memory are mediated by changes in network dynamics, the transmission rates of the representations of attended stimuli from primary sensory regions to memory areas should be facilitated relative to the transmission rates of unattended stimuli.  Further, variability in these neural changes (e.g., as a participant focuses their attention with more or less success) should track with behavioral measures of memorability.

Which aspects of our ongoing experiences we choose to attend affects how we process and remember those experiences later.  Different forms of attention---e.g., to specific features or spatial locations---operate and affect memory at different timescales, and are likely mediated by different brain networks.  Elucidating the behavioral and neural consequences of volitional changes in attention is central to discovering how our thoughts, feelings, goals, and situational understanding fluctuate from moment to moment.

\section*{Author Contributions}

J. R. Manning and K. Ziman developed the concept for this study. Experiment code was written by K. Ziman and A. R. Martinez, and testing and data collection were conducted by M. R. Lee and K. Ziman. K. Ziman, M. R. Lee, and A. R. Martinez analyzed the data.  All authors contributed to writing the manuscript and have approved the final version of the manuscript for submission.

\section*{Acknowledgements}

This work was supported in part by NSF EPSCoR award number 1632738.  The content of this manuscript is solely the responsibility of the authors and does not necessarily represent the official views of our supporting organizations.  We are grateful for useful discussions with the EPSCoR Attention Consortium, particularly with Marian Berryhill, Gideon Caplovitz, Patrick Cavanagh, Theresa Desrochers, and Peter Tse.  We thank Megan deBettencourt for useful discussions, pointers to our experimental stimuli, and for providing code to facilitate stimulus preparation.  We also appreciate useful discussions with Paxton Fitzpatrick, Kevin Hartstein, Talia Manning, Lucy Owen, and Michael Ziman.  Finally, we thank Christina Liu and Eowyn Pak for their help running pilot versions of the experiments reported here.

\section*{Open practices statement}
Neither of the experiments reported in this article were pre-registered. However, we replicated both experiments in the study after collecting our initial datasets. We report analysis of the combined datasets in our manuscript (Sustained Attention Experiment: n = 60; Variable Attention Experiment: n = 53), and analysis of each replication group, independently, in the \textit{Supporting Materials} (Sustained Attention Experiment, Group 1: n = 30; Sustained Attention Experiment, Group 2: n = 30; Variable Attention Experiment, Group 1: n = 30; Variable Attention Experiment, Group 2: n = 23). All of our experimental materials, data, and analysis code may be downloaded from \url{http://www.github.com/ContextLab/attention-memory-task}.

\bibliographystyle{apacite}
\bibliography{CDL-bibliography/memlab}

\end{document}

### 2023-03-24 paper/supplemental_materials.tex
copying in old draft of paper + supplement

\documentclass{article}
\usepackage{graphicx}
\usepackage[position=top]{subfig}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
% ^^ moves subfigure titles to the top
\usepackage{pxfonts}

\def\rot#1{\raisebox{-1.35in}{\rotatebox{90}{#1}}}
% ^^ moves vertical titles down to the middle of the subfigures

\def\roto#1{\raisebox{-1.17in}{\rotatebox{90}{#1}}}

\begin{document}

\title{Supporting Materials for \textit{Feature-based and location-based volitional covert attention affect memory at different timescales}}

\author{Kirsten Ziman$^1$,
Madeline R. Lee$^1$,
Alejandro R. Martinez$^1$,\\
Ethan D. Adner$^2$,
and
Jeremy R. Manning\textsuperscript{$1, \dagger$}\\[0.1in]$^1$Department of Psychological and Brain Sciences and\\
$^2$Thayer School of Engineering,\\
Dartmouth College, Hanover, NH 03755\\
\textsuperscript{$\dagger$}Address correspondence to jeremy.r.manning@dartmouth.edu}

%\begin{titlepage}
  \maketitle
%\end{titlepage}

  \renewcommand{\thefigure}{S\arabic{figure}}

%\section*{Supplement}

%Here, we separately replicate the figures in our manuscript for the initial participant cohort and the replication cohort of each experiment.

% FIGURE - violin
\begin{figure}
\captionsetup[subfigure]{labelformat=empty}
\roto{\rlap{\textbf{Sustained}}}
 \subfloat[(a) Initial cohort]{
	\begin{minipage}[c][1\width]{
	   0.4\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/Maddy_sustain1violin.pdf}
	\end{minipage}}
 \hfill
  \subfloat[(b) Replication cohort]{
	\begin{minipage}[c][1\width]{
	   0.4\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/Maddy_sustain2violin.pdf}
	\end{minipage}}
 \hfill
  \subfloat{
	\begin{minipage}[c][1\width]{
	   0.1\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/violin_key.pdf}
	\end{minipage}}

% \hfill
  %\subfloat[Combined data]{
	%\begin{minipage}[c][1\width]{
	   %0.5\textwidth}
	   %\centering
	   %\includegraphics[width=\textwidth]{example-image-a.pdf}
	%\end{minipage}}

\roto{\rlap{\textbf{Variable}}}
  \subfloat[(c) Initial cohort]{
	\begin{minipage}[c][1\width]{
	   0.4\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/Maddy_variabl1violin.pdf}
	\end{minipage}}
 \hfill
  \subfloat[(d) Replication cohort]{
	\begin{minipage}[c][1\width]{
	   0.4\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/Maddy_variabl2violin.pdf}
	\end{minipage}}
 \hfill
  \subfloat{
	\begin{minipage}[c][1\width]{
	   0.1\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/violin_key.pdf}
	\end{minipage}}

\caption{\textbf{Familiarity ratings for attended, unattended, and
    novel stimuli.}  This figure follows the same formatting as
  Figure~2 in the main text, but the panels in this figure break down
  those results by participant cohort.  Each split violin plot displays the distribution of within-participant average familiarity ratings given to faces (left, darker colors) and scenes (right, lighter colors) during the memory phases of each experiment.  As shown in the legend (bottom), the colors indicate whether each image had been viewed during the presentation phase (\texttt{old}) or not; whether the given images matched the \texttt{attended category}; and/or whether the given images matched the \texttt{attended location}.  The colored lines above each set of violin plots denote statistical differences  (\textbf{pos}itive or \textbf{neg}ative differences in mean, collapsing over image category, assessed via two-tailed $t$-tests) between the distributions centered on the endpoints of each line.  The line thicknesses denote $p$-values as indicated in the legend.  Asterisks denote differences between the face versus scene distributions (assessed via two-tailed $t$-tests).}

\end{figure}

% FIGURE - gaze

\begin{figure}[ht]
\captionsetup[subfigure]{labelformat=empty}
\rot{\rlap{\textbf{Sustained}}}
  \subfloat[(a) Initial cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/sustain_gaze_1.pdf}
	\end{minipage}}
 \hfill
  \subfloat[(b) Replication cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/sustain_gaze_2.pdf}
	\end{minipage}}
 \hfill
  \subfloat{
	\begin{minipage}[c][1\width]{
	   0.2\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/gaze_legend.pdf}
	\end{minipage}}

\raisebox{.05in}{\rot{\rlap{\textbf{Variable}}}}
  \subfloat[(c) Initial cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/variabl_gaze_1.pdf}
	\end{minipage}}
 \hfill
  \subfloat[(d) Replication cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/variabl_gaze_2.pdf}
	\end{minipage}}
 \hfill
  \subfloat{
	\begin{minipage}[c][1\width]{
	   0.2\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/gaze_legend.pdf}
	\end{minipage}}

  \caption{\textbf{Horizontal coordinates of visual fixations.}  This figure follows the same formatting as
  Figure~3 in the main text, but the panels in this figure break down
  those results by participant cohort.  Each violin plot displays a distribution of participant-wise average horizontal gaze positions relative to a presented image.  The coordinates have been normalized such that a value of 1.0 denotes the furthest onscreen coordinate from the central fixation point \textit{towards} the direction of the given image, and -1.0 denotes the furthest onscreen coordinate from the central fixation point \textit{away from} the direction of the given image.  The gray bars in each panel mark the boundaries of the presented images.  The violin plots are broken down by participants' familiarity ratings during the memory phases of each experiment, and by each image's relation to the attention cue while that image appeared onscreen. }\end{figure}

% FIGURE - cued_window

\begin{figure}[ht]
\captionsetup[subfigure]{labelformat=empty}
\rot{\rlap{\textbf{Sustained}}}
  \subfloat[(a) Initial cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/sust1_cued_window.pdf}
	\end{minipage}}
 \hfill
  \subfloat[(b) Replication cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/sust2_cued_window.pdf}
	\end{minipage}}
 \hfill
  \subfloat{
	\begin{minipage}[c][1\width]{
	   0.2\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/red_key.pdf}
	\end{minipage}}

\raisebox{.05in}{\rot{\rlap{\textbf{Variable}}}}
  \subfloat[(c) Initial cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/var1_cued_window.pdf}
	\end{minipage}}
 \hfill
  \subfloat[(d) Replication cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/var2_cued_window.pdf}
	\end{minipage}}
 \hfill
  \subfloat{
	\begin{minipage}[c][1\width]{
	   0.2\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/red_key.pdf}
	\end{minipage}}

  \caption{\textbf{Familiarity ratings over time for images that matched cued image category.}  This figure follows the same formatting as
  Figure~4 (top panels) in the main text, but the panels in this figure break down
  those results by participant cohort.  Each curve reflects the average familiarity ratings for attended, unattended, and novel images (denoted in the legends on the right) within a succession of overlapping 20-image sliding windows.  Error ribbons denote 95\% confidence intervals, computed across participants. The paired horizontal lines at the bottom of each panel denote timepoints when the given pair of curves was statistically distinguishable (i.e., the topmost line color was statistically greater than the bottommost line color at $\alpha = 0.05$, via a paired two-tailed $t$-test.)}
  \label{fig:familiarity_timecourse_category3}
\end{figure}

% FIGURE - uncued_window

\begin{figure}[ht]
\captionsetup[subfigure]{labelformat=empty}
\rot{\rlap{\textbf{Sustained}}}
  \subfloat[(a) Initial cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/sust1_uncued_window.pdf}
	\end{minipage}}
 \hfill
  \subfloat[(b) Replication cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/sust2_uncued_window.pdf}
	\end{minipage}}
 \hfill
  \subfloat{
	\begin{minipage}[c][1\width]{
	   0.2\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/blue_key.pdf}
	\end{minipage}}

\raisebox{.05in}{\rot{\rlap{\textbf{Variable}}}}
  \subfloat[(c) Initial cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/var1_uncued_window.pdf}
	\end{minipage}}
 \hfill
  \subfloat[(d) Replication cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/var2_uncued_window.pdf}
	\end{minipage}}
 \hfill
  \subfloat{
	\begin{minipage}[c][1\width]{
	   0.2\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/blue_key.pdf}
	\end{minipage}}

  \caption{\textbf{Familiarity ratings over time for images that matched uncued image category.}  This figure follows the same formatting as
  Figure~4 (bottom panels) in the main text, but the panels in this figure break down
  those results by participant cohort.  Each curve reflects the average familiarity ratings for attended, unattended, and novel images (denoted in the legends on the right) within a succession of overlapping 20-image sliding windows.  Error ribbons denote 95\% confidence intervals, computed across participants. The paired horizontal lines at the bottom of each panel denote timepoints when the given pair of curves was statistically distinguishable (i.e., the topmost line color was statistically greater than the bottommost line color at $\alpha = 0.05$, via a paired two-tailed $t$-test.)}
  \label{fig:familiarity_timecourse_category4}
\end{figure}

% FIGURE - cued_loc

\begin{figure}[ht]
\captionsetup[subfigure]{labelformat=empty}
\rot{\rlap{\textbf{Sustained}}}
  \subfloat[(a) Initial cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/sust1_cued_loc.pdf}
	\end{minipage}}
 \hfill
  \subfloat[(b) Replication cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/sust2_cued_loc.pdf}
	\end{minipage}}
 \hfill
  \subfloat{
	\begin{minipage}[c][1\width]{
	   0.2\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/red_blue_key.pdf}
	\end{minipage}}

\raisebox{.05in}{\rot{\rlap{\textbf{Variable}}}}
  \subfloat[(c) Initial cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/var1_cued_loc.pdf}
	\end{minipage}}
 \hfill
  \subfloat[(d) Replication cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/var2_cued_loc.pdf}
	\end{minipage}}
 \hfill
  \subfloat{
	\begin{minipage}[c][1\width]{
	   0.2\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/red_blue_key.pdf}
	\end{minipage}}

\caption{\textbf{Familiarity ratings over time for images that matched the cued image location.}  This figure follows the same formatting as
  Figure~5 (top panels) in the main text, but the panels in this figure break down
  those results by participant cohort.}
\label{fig:familiarity_timecourse_location5}
\end{figure}

% FIGURE - uncued_loc

\begin{figure}[ht]
\captionsetup[subfigure]{labelformat=empty}
\rot{\rlap{\textbf{Sustained}}}
  \subfloat[(a) Initial cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/sust1_uncued_loc.pdf}
	\end{minipage}}
 \hfill
  \subfloat[(b) Replication cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/sust2_uncued_loc.pdf}
	\end{minipage}}
 \hfill
  \subfloat{
	\begin{minipage}[c][1\width]{
	   0.2\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/orange_blue_key.pdf}
	\end{minipage}}

\raisebox{.05in}{\rot{\rlap{\textbf{Variable}}}}
  \subfloat[(c) Initial cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/var1_uncued_loc.pdf}
	\end{minipage}}
 \hfill
  \subfloat[(d) Replication cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/var2_uncued_loc.pdf}
	\end{minipage}}
 \hfill
  \subfloat{
	\begin{minipage}[c][1\width]{
	   0.2\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/orange_blue_key.pdf}
	\end{minipage}}

\caption{\textbf{Familiarity ratings over time for images that matched uncued image location.}  This figure follows the same formatting as
  Figure~5 (bottom panels) in the main text, but the panels in this figure break down
  those results by participant cohort.}
\label{fig:familiarity_timecourse_location6}
\end{figure}

% FIGURE - novel window

\begin{figure}[ht]
\captionsetup[subfigure]{labelformat=empty}
\rot{\rlap{\textbf{Sustained}}}
  \subfloat[(a) Initial cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/sust1_novel_window.pdf}
	\end{minipage}}
 \hfill
  \subfloat[(b) Replication cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/sust2_novel_window.pdf}
	\end{minipage}}
 \hfill
  \subfloat{
	\begin{minipage}[c][1\width]{
	   0.2\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/novel_key.pdf}
	\end{minipage}}

\raisebox{.05in}{\rot{\rlap{\textbf{Variable}}}}
  \subfloat[(c) Initial cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/var1_novel_window.pdf}
	\end{minipage}}
 \hfill
  \subfloat[(d) Replication cohort]{
	\begin{minipage}[c][1\width]{
	   0.35\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/var2_novel_window.pdf}
	\end{minipage}}
 \hfill
  \subfloat{
	\begin{minipage}[c][1\width]{
	   0.2\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/novel_key.pdf}
	\end{minipage}}

   \caption{\textbf{Familiarity ratings over time for attended-category and unattended-category novel images.}  This figure follows the same formatting as
  Figure~6 (top panels) in the main text, but the panels in this figure break down
  those results by participant cohort.}\end{figure}

% FIGURE - diff

\begin{figure}[ht]
\raisebox{-.4in}{\rot{\rlap{\textbf{Sustained}}}}
  \subfloat[Initial cohort]{
	\begin{minipage}[c][1\width]{
	   0.5\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/sust1_diff.pdf}
	\end{minipage}}
 \hfill
  \subfloat[Replication cohort]{
	\begin{minipage}[c][1\width]{
	   0.5\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/sust2_diff.pdf}
	\end{minipage}}

\raisebox{-.35in}{\rot{\rlap{\textbf{Variable}}}}
  \subfloat[Initial cohort]{
	\begin{minipage}[c][1\width]{
	   0.5\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/var1_diff.pdf}
	\end{minipage}}
 \hfill
  \subfloat[Replication cohort]{
	\begin{minipage}[c][1\width]{
	   0.5\textwidth}
	   \centering
	   \includegraphics[width=\textwidth]{supp_figures/var2_diff.pdf}
	\end{minipage}}

 \caption{\textbf{Familiarity ratings over time for attended-category and unattended-category novel images.}  This figure follows the same formatting as
  Figure~6 (bottom panels) in the main text, but the panels in this figure break down
  those results by participant cohort.}
\end{figure}

\end{document}

### 2023-03-25 code/helpers.py
complete drafts of all figures and stats

@@ -1,0 +1,444 @@
+import os
+import requests
+import pandas as pd
+import numpy as np
+import warnings
+import json
+import matplotlib as mpl
+from matplotlib import pyplot as plt
+
+from tqdm import tqdm
+from glob import glob as lsdir
+
+basedir = os.path.split(os.getcwd())[0]
+datadir = os.path.join(basedir, 'data')
+figdir = os.path.join(basedir, 'paper', 'figs', 'source')
+
+if not os.path.exists(figdir):
+    os.makedirs(figdir)
+
+if not os.path.exists(datadir):
+    os.makedirs(datadir)
+
+attention_colors = {
+    'Attended': '#BE1E2D',
+    'Attended category': '#F15A29',
+    'Attended location': '#F9ED32',
+    'Unattended': '#009444',
+    'Novel': '#27AAE1',
+    'Face': '#000000',
+    'Place': '#000000'
+}
+
+
+def download_data():
+    data_url = 'https://www.dropbox.com/s/99ty0ok8p4m5ijc/data.zip?dl=1'
+    data_fname = os.path.join(basedir, 'data.zip')
+    checkfile_fname = os.path.join(datadir, 'checkfile.txt')
+
+    if not os.path.exists(data_fname) and not os.path.exists(checkfile_fname):
+        print('Downloading data...')
+        r = requests.get(data_url, allow_redirects=True)
+        open(data_fname, 'wb').write(r.content)
+
+    if os.path.exists(data_fname) and not os.path.exists(checkfile_fname):
+        print('Unzipping data...')
+        os.system(f'unzip -q {data_fname} -d {basedir}')
+        os.system(f'rm {data_fname}')
+        os.system(f'rm -rf {basedir}/__MACOSX')
+
+        with open(checkfile_fname, 'w') as f:
+            f.write('download complete.')
+
+def parse_behavioral_data(datadir):
+    def get_pres_time(image, stim_type, log):
+        if type(image) is str:
+            image_times = log.loc[log['Info'].apply(lambda x: (image in x) and (stim_type in x) if type(x) is str else False)]
+            assert image_times.shape[0] == 4, Exception(f'Image {image} appears the wrong number of times')
+            return image_times.iloc[-2]['Time'], image_times.iloc[-1]['Time']
+        else:
+            return np.nan, np.nan
+        
+    def add_timing_info(subj_df):
+        def timing_helper(x, log):
+            image = np.nan
+            stim_type = ''
+            if image is np.nan:
+                image = x['Cued Composite']
[…]

### 2023-03-25 paper/main.tex
finished updating draft of text through end of methods section

@@
 
-\title{Category-based and location-based volitional covert attention affect memory at different timescales}
+\title{Category-based and location-based volitional covert attention affect
+memory at different timescales}
 
@@
 central point. The image pairs comprised a left and right image, each
-constructed by blending an image of a face and scene. The stimuli and
+constructed by blending an image of a face and place. The stimuli and
 presentation durations were constant across the two experiments, but the
 experiments differed in how often we asked participants to change the focus of
-their attention with respect to image category (face versus scene) and image
+their attention with respect to image category (face versus place) and image
 location (left versus right). After the participants attended to a series of
@@
 
-\textbf{JRM STOPPED HERE}
-
 \begin{figure*}[tp]
   \centering
-  \includegraphics[width=1\textwidth]{figures/paradigm_and_key.pdf}
+  \includegraphics[width=1\textwidth]{figs/paradigm}
 
-  \caption{\textbf{Paradigm overview.} \textbf{a.} Composite face/scene image.
-  \textbf{b.} A single pair of composite images and a central fixation cross.
-  \textbf{c.} Timecourse of an attention cue practice trial (3 total).
-  \textbf{d.} Timecourse of a practice trial for the reaction time task (3
-  total). \textbf{e.} Familiarity judgement practice trial (4 total).
-  \textbf{f.} Timecourse of one Sustained Attention Experiment presentation
-  phase and memory phase block. \textbf{g.} Timecourse of one Variable
-  Attention Experiment presentation phase and memory phase block. \textbf{h.}
-  Breakdown of presented (old) and novel stimuli that matched (or did not
-  match) the focus of participants' feature-based attention and/or
-  location-based attention. Filled colored circles on the right denote that the
-  given stimulus (matching the corresponding color; images shown on the left)
-  satisfied the indicated property. Open circles denote that the given stimulus
-  did \textit{not} satisfy the indicated property. Gray circles denote
-  properties that are undefined for the given stimulus.}
+  \caption{\textbf{Experimental paradigm.} \textbf{A.--D. Practice phase.}
+  \textbf{A.} Composite face/place image. \textbf{B.} A single pair of
+  composite images and a central fixation cross. \textbf{C.} One attention cue
+  practice trial. \textbf{D.} Familiarity judgement practice trial. \textbf{E.
+  Sustained attention condition.} Participants receive an attention cue,
+  followed by a sequence of 10 composite image pairs (Panel E), and then they
+  make of familiarity judgements on each of 40 face and place images, presented
+  in sequence (Panel F).  \textbf{G.  Variable attention condition.}  Participants
+  study a succession of 10 composite image pairs, each preceded by an attention cue.
+  After studying the images, they make a series of 40 familiarity judgements about
+  face and place images, as in the sustained attention condition (Panel F).}
 
@@
 \subsection*{Participants}
-\subsubsection*{Sustained Attention Experiment}
-Sixty students, enrolled in one or more undergraduate psychology courses at Dartmouth College, participated in the Sustained Attention Experiment for course credit.
-The participants' ages ranged from 18--21; 42 participants were female, 17 were male, and one identified as gender non-binary.
-All participants had self-reported normal or corrected-to-normal vision, memory, and attention.
-Participants gave written consent to enroll in the study under a protocol approved by the Committee for the Protection of Human Subjects at Dartmouth College.
 
-\subsubsection*{Variable Attention Experiment}
-Fifty-three individuals participated in the Variable Attention Experiment for either cash ($n=13$) or course credit ($n=40$; students enrolled in one or more undergraduate psychology courses at Dartmouth College).
-The participants' ages ranged from 18--23; 34 participants were female and 19 were male.
-All participants had self-reported normal or corrected-to-normal vision, memory, and attention.
-Participants gave written consent to enroll in the study under a protocol approved by the Committee for the Protection of Human Subjects at Dartmouth College.
+A total of 53 Dartmouth College undergraduate students enrolled in our study
+(30 in the sustained attention condition and 23 in the variable attention
+condition). Following a pilot study using a similar experimental design, we
+aimed to enroll 30 participants in each condition. However, we fell short of
+our enrollment target in the variable attention condition when in-person
+testing was discontinued at our institution due to the COVID-19 pandemic. All
+participants had self-reported normal or corrected-to-normal vision, memory,
+and attention. Participants gave written consent to enroll in the study under a
+protocol approved by the Committee for the Protection of Human Subjects at
+Dartmouth College.
+
+We used a voluntary pre-experimental survey to collect self-reported
+demographic information about each partipant. All 53 participants elected to
+fill out the survey. Participants ranged in age from 18--21 years old (mean:
+18.7 years; standard deviation: 0.8 years). Participants reported their genders
+as female (34 particiapnts), male (18 participants), and gender non-binary (1
+participant). Participants reported their ethnicities as Not Hispanic or Latino
+(44 particiapnts), Hispanic or Latino (7 participants), or declined to respond
+(2 participant). Participants reported their race as White (37 participants),
+Asian (13 participants), American Indian or Alaska Native (4 participants),
+Black or African American (2 participants), and Other (1 participant). Note
+that each participant could report one or more racial categories, as they
+deemed appropriate.
+
+Fourty-nine participants reported having no reading impairments, and 4
+participants reported having reading impairments such as dyslexia. Fifty
+participants reported having normal color vision and 3 reported having abnormal
+color vision such as colorblindness. Fifty participants reported taking no
+medications and having no recent injuries. One participant reported that they
+had recently ``hit [their] head very hard.'' Another reported having taken
+concerta in the past, but mentioned they had not taken it recently. One
+participant reported using amphetamines regularly, but also clarified that they
+were not currently on amphetamines at the time of testing.
+
+We also asked participants to self-report on their sleep, alertness, and coffee
+consumption. Participants reported having gotten between 4 and 9 hours of sleep
+on the night prior to testing (mean: 6.9 hours; standard deviation: 1.3 hours).
+Participants reported their alertness at the time of testing, and we converted
+their responses to point values as follows: ``Very alert'' (5 points), ``A
+little alert'' (4 points), ``Neutral'' (3 points), ``A little sluggish'' (2
+points), and ``Very sluggish'' (1 point). Across all participants, the full
+range of alertness values were used (maximum: 5; minimum: 1; mean: 3.44;
+standard deviation: 1.0). Participants reported having consumed between 0 and 2
+cups of coffee so far on their testing day (mean: 0.3 cups; standard deviation:
+0.5 cups).
 
 \subsection*{Stimulus selection and presentation}
-Participants viewed photographs of faces, scenes, and composite images each comprising an equal blend of one face image and one scene image.
-The pool of 360 face images included photographs of adult human male and female faces selected from the FERET database~\citep{PhilEtal98}.
-The pool of 360 scene images included photographs of indoor and outdoor scenes selected from the SUN database~\citep{XiaoEtal10}.
-The images we used from both databases came from a stimulus subset that was manually curated by Megan deBettencourt (personal communication).
-All images were resized to $256 \times 256$ pixels, converted to greyscale, and processed so that every image was matched for mean contrast and intensity.
-We selected 20 face images and 20 scene images from the stimulus pool to use in the instructional and practice phases of the experiments (Fig.~\ref{fig:paradigm}a--e).
 
-In addition to the face and scene images, we presented (in white) attention cues to direct the participant's focus of attention.
-The attention cues comprised a stylized icon of a face or mountain peaks, directing attention to the face or scene component of the images, respectively; and a left- or right-facing angled bracket, directing attention to the left or right image, respectively (e.g., Figs.~\ref{fig:paradigm}c, d, f, and g).
+Participants viewed photographs of faces, places, and composite images each
+comprising an equal blend of one face image and one place image. The pool of
+360 face images included photographs of adult human male and female faces
+selected from the FERET database~\citep{PhilEtal98}. The pool of 360 place
+images included photographs of indoor and outdoor places selected from the SUN
+database~\citep{XiaoEtal10}. The images we used from both databases came from a
+stimulus subset that was manually curated by Megan deBettencourt (personal
+communication). All images were resized to $256 \times 256$ pixels, converted
+to greyscale, and processed so that every image was matched for mean contrast
+and intensity. We selected 20 face images and 20 place images from the stimulus
+pool to use in the instructional and practice phases of the experiments
+(Fig.~\ref{fig:paradigm}A--D).
 
- Both experiments were conducted in a sound- and light-attenuated testing room containing a chair, desk, and 27-inch iMac desktop computer (display resolution: $2048 \times 1152$).
-The participant sat in the chair and rested their chin on a chin rest located 60~cm from the display.
-The active portion of the display screen occupied 52.96$^\circ$ (width) and 31.28$^\circ$ (height) of the participant's field of view from the chin rest.
-Stimuli were sized to occupy $6.7^\circ$ (width and height) of the participant's field of view from the chin rest.
-We maintained a black background (with any text displayed in white) throughout the experiment.
+In addition to the face and place images, we presented (in white) attention
+cues to direct the participant's focus of attention. The attention cues
+comprised a stylized icon of a face or mountain peaks, directing attention to
+the face or place component of the images, respectively; and a left- or
+right-facing angled bracket, directing attention to the left or right image,
+respectively (e.g., Figs.~\ref{fig:paradigm}C, E, and G).
+
+ Our experiment was conducted in a sound- and light-attenuated testing room
+ containing a chair, desk, and 27-inch iMac desktop computer (display
+ resolution: $2048 \times 1152$). The participant sat in the chair and rested
+ their chin on a chin rest located 60~cm from the display. The active portion
+ of the display screen occupied 52.96$^\circ$ (width) and 31.28$^\circ$
+ (height) of the participant's field of view from the chin rest. Stimuli were
+ sized to occupy $6.7^\circ$ (width and height) of the participant's field of
+ view from the chin rest. We maintained a black background (with any text
+ displayed in white) throughout the experiment.
 
 \subsection*{Eyetracking}
-We recorded participants' eye gaze positions using a desk-mounted video-based eyetracker with a spatial resolution of 0.1$^\circ$ visual angle root mean squared error and a sampling rate of 30~Hz (Eye Tribe, The Eye Tribe, Copenhagen, Denmark).
-We calibrated the eyetracker using a 9-point gaze pattern.
-As described below, we re-calibrated the eyetracker at regular intervals throughout the experiments to protect against camera drift.
+
+We recorded participants' eye gaze positions using a desk-mounted video-based
+eyetracker with a spatial resolution of 0.1$^\circ$ visual angle root mean
+squared error and a sampling rate of 30~Hz (Eye Tribe, The Eye Tribe,
+Copenhagen, Denmark). We calibrated the eyetracker using a 9-point gaze
+pattern. As described below, we re-calibrated the eyetracker at regular
+intervals throughout the experiment to protect against camera drift.
 
 \subsection*{Experimental paradigm}
-Both experimental paradigms comprised a practice phase followed by a series of eight task blocks.
-Each task block was in turn comprised of a presentation phase and a memory phase.
-The practice and presentation phases differed across the two experiments, and the memory phases were identical across the two experiments.
+
+Our experiment comprised two testing conditions: a \textit{sustained} attention
+condition and a \textit{variable} attention condition. Both experimental
+conditions comprised a practice phase followed by a series of eight task
+blocks. Each task block was in turn comprised of a presentation phase and a
+memory phase. The practice and presentation phases differed across the two
+experiments, and the memory phases were identical across the two experiments.
 Both experiments were implemented using PsychoPy~\citep{PeirEtal19}.
@@
 \subsubsection*{Practice phase}
-Several participants in pilot versions of our experiments reported that they found it difficult to modulate the focus of their attention quickly on command.
-We therefore designed a practice sequence to orient the participant to the process of quickly modulating the focus of their attention without moving their eyes.
-The experimenter remained in the testing room throughout the practice phase and answered any questions about the experiment.
-The practice sequence builds up incrementally to provide a gradual on-ramping for the participant prior to beginning the main experimental tasks that we focused on in our analyses.
 
-\paragraph{Practice shifting the focus of feature-based attention to elements of a single composite image.}
-At the start of the practice phase, we instructed the participant to look at a single composite (face-scene blend) image at the center of the screen, and to try to bring the face component of the image into greater focus by attending to it (Fig.~\ref{fig:paradigm}a).
-After pressing a button on the keyboard to indicate that they had done so, we displayed a second composite image and instructed the participant to bring the scene component of the new composite image into focus.
-Again, they pressed a button to indicate that they had done so.
+Several participants in pilot versions of our experiments reported that they
+found it difficult to modulate the focus of their attention quickly on command.
+We therefore designed a practice sequence to orient the participant to the
+process of quickly modulating the focus of their attention without moving their
+eyes. The experimenter remained in the testing room throughout the practice
+phase and answered any questions about the experiment. The practice sequence
+builds up incrementally to provide a gradual on-ramping for the participant
+prior to beginning the main experimental tasks that we focused on in our
+analyses.
 
-\paragraph{Practice shifting the focus of feature-based and location-based attention while viewing two composite images.}
-Next, we asked the participant to stare at a fixation cross presented in the center of the screen while two composite images were displayed on the left and right side of the screen, respectively.
-We first instructed the participant to attend to the scene component of the left image without moving their eyes.
-Participants practiced shifting their attention, and they pressed a button on the keyboard to indicate that they had done so.
-We then displayed a second pair of composite images and instructed the participant to attend to the face component of the right image.
-Again, the participant shifted their attention in a self-paced manner, and pressed a button to indicate when they had successfully done so (Fig.~\ref{fig:paradigm}b).
+\paragraph{Practice shifting the focus of category-based attention to elements
+of a single composite image.}
 
-\paragraph{Practice sustaining feature-based and location-based attention over a series of composite image pairs.}
-We asked participants in the Sustained Attention Experiment to practice holding their focus of feature-based and location-based attention constant (to the face component of the right image) while viewing a series of three composite image pairs presented in succession (Fig.~\ref{fig:paradigm}c).
+At the start of the practice phase, we instructed the participant to look at a
+single composite (face-place blend) image at the center of the screen, and to
+try to bring the face component of the image into greater focus by attending to
+it (Fig.~\ref{fig:paradigm}A). After pressing a button on the keyboard to
+indicate that they had done so, we displayed a second composite image and
+instructed the participant to bring the place component of the new composite
+image into focus. Again, they pressed a button to indicate that they had done
+so.
 
-\paragraph{Practice varying feature-based and location-based attention over a series of composite image pairs.}
-We asked participants in the Variable Attention Experiment to practice varying their focus of feature-based and location-based attention while viewing a series of three composite image pairs presented in succession (Fig.~\ref{fig:paradigm}c).
+\paragraph{Practice shifting the focus of category-based and location-based
+attention while viewing two composite images.}
+
+Next, we asked the participant to stare at a fixation cross presented in the
+center of the screen while two composite images were displayed on the left and
+right side of the screen, respectively (Fig.~\ref{fig:paradigm}B). We first
+instructed the participant to attend to the place component of the left image
+without moving their eyes. Participants practiced shifting their attention, and
+they pressed a button on the keyboard to indicate that they had done so. We
+then displayed a second pair of composite images and instructed the participant
+to attend to the face component of the right image. Again, the participant
+shifted their attention in a self-paced manner, and pressed a button to
+indicate when they had successfully done so.
+
+\paragraph{Practice \textit{sustaining} category-based and location-based attention over
+a series of composite image pairs.}
+
+We asked participants in the sustained attention condition to practice holding
+their focus of category-based and location-based attention constant (to the
+face component of the right image) while viewing a series of three composite
+image pairs presented in succession (Fig.~\ref{fig:paradigm}C).
+
+\paragraph{Practice \textit{varying} category-based and location-based
+attention over a series of composite image pairs.}
+
+We asked participants in the variable attention condition to practice varying
+their focus of category-based and location-based attention while viewing a
+series of three composite image pairs, each presented after a different
+attention cue (Fig.~\ref{fig:paradigm}C).
 
 \paragraph{Practice reaction time probe.}
-After practicing modulating their focus of attention to a series of composite image pairs, we introduced a reaction time probe after each image presentation, whereby we presented either an $\times$ or $\circ$ on either the left or the right of the screen (Fig.~\ref{fig:paradigm}d).
-We asked the participant to press the \texttt{1} key as quickly as possible when they saw an $\times$, or the \texttt{3} key as quickly as possible when they saw an $\circ$.
-We did not impose a time limit on their responses, other than asking participants to respond as quickly as they were able.
-Participants practiced three trials of modulating their focus of attention to a pair of composite images (3~s), and reacting as quickly as possible to the $\times$ or $\circ$ symbol presented after each composite image pair.
-The reaction time probe was intended to keep participants continually engaged in modulating the focus of their attention.
+
+After practicing modulating their focus of attention to a series of composite
+image pairs, we introduced a reaction time probe after each image presentation,
+whereby we presented either an $\times$ or $\circ$ on either the left or the
+right of the screen (not shown). We asked the participant to press the
+\texttt{1} key as quickly as possible when they saw an $\times$, or the
+\texttt{3} key as quickly as possible when they saw an $\circ$. We did not
+impose a time limit on their responses, other than asking participants to
+respond as quickly as they were able. Participants practiced three trials of
+modulating their focus of attention to a pair of composite images (3~s), and
+reacting as quickly as possible to the $\times$ or $\circ$ symbol presented
+after each composite image pair. The reaction time probe was intended to keep
+participants continually engaged in modulating the focus of their attention.
 
 \paragraph{Practice recognition memory task.}
-Finally, we asked the participant to practice reporting familiarity on a recognition memory task (Fig.~\ref{fig:paradigm}e).
-We presented a single face or scene image at the center of the screen, and asked them to press a button to indicate how ``familiar'' the image seemed: \texttt{1} (very confident they had not seen the image), \texttt{2} (somewhat confident they had not seen the image), \texttt{3} (somewhat confident they had seen the image), or \texttt{4} (very confident that they had seen the image).
-We instructed the participant to go with their ``gut reaction'' in the event that they were unsure of how to respond.
-We allowed the participant up to 2~s to provide their response.
-We gave participants a total of four practice images to rate.
 
-After completing the practice phase of the experiment, the participant read the instructions for the task blocks (described next).
-The experimenter gave participants a chance to ask any remaining questions about the experiment.
-After answering the participant's questions, the experimenter calibrated the eyetracker and exited the testing room.
+Finally, we asked the participant to practice reporting familiarity on a
+recognition memory task (Fig.~\ref{fig:paradigm}D). We presented a single face
+or place image at the center of the screen, and asked them to press a button to
+indicate how ``familiar'' the image seemed: \texttt{1} (very confident they had
+not seen the image), \texttt{2} (somewhat confident they had not seen the
+image), \texttt{3} (somewhat confident they had seen the image), or \texttt{4}
+(very confident that they had seen the image). We instructed the participant to
+go with their ``gut reaction'' in the event that they were unsure of how to
+respond. We allowed the participant up to 2~s to provide their response. We
+gave participants a total of four practice images to rate.
+
+After completing the practice phase of the experiment, the participant read the
+instructions for the task blocks (described next). The experimenter gave
+participants a chance to ask any remaining questions about the experiment.
+After answering the participant's questions, the experimenter calibrated the
+eyetracker and exited the testing room.
 
 \subsubsection*{Task blocks}
-During each task block we asked the participant to modulate their attention while viewing a series of 10 composite image pairs (each followed by a reaction time probe), and then we tested the participant's memory using 40 familiarity judgements.
-Each participant completed a total of eight task blocks.
 
-\paragraph*{Sustained Attention Experiment: presentation phase.} Participants viewed an attention cue (1.5~s) instructing them to attend to either the face or scene component of either the left or right images in each to-be-viewed composite pair.
-Next we displayed 10 composite images in succession (each preceded by a fixation cross and proceeded by a reaction time probe).
-Complete timing information is displayed in Figure~\ref{fig:paradigm}f.
-All possible attention cue pairs appeared exactly twice across the eight task blocks.
+During each task block we asked the participant to modulate their attention
+while viewing a series of 10 composite image pairs (each followed by a reaction
+time probe), and then we tested the participant's memory using 40 familiarity
+judgements. Each participant completed a total of eight task blocks.
 
-\paragraph*{Variable Attention Experiment: presentation phase.}  Participants viewed a succession of 10 attention cues (1.5~s), each followed by a fixation cross (1~s), composite image (3~s), and a reaction time probe (Fig.~\ref{fig:paradigm}g).
-The attention cues were selected pseudorandomly across trials within each block, with the constraints that no single attention cue pair could appear more than three times across the 10 composite image pairs within a single task block.
+\paragraph*{Sustained attention condition: presentation phase
+(Fig.~\ref{fig:paradigm}E).}
 
-\paragraph*{Memory phase.} After the presentation phase of each task block, we asked the participant to rate the familiarity (on a 1--4 scale, as during the practice phase) of a succession of face and scene images.
-Each image was preceded by a 1~s fixation cross, and participants had up to 2~s to input their rating of each image.
-Participants made a total of 40 familiarity judgements, about 20 face images and 20 scene images.
-Of these, 20 of the images (10 faces and 10 scenes) were drawn randomly from the (attended and unattended) composite images that the participant had viewed during the presentation phase.
-The remaining 20 images (10 faces and 10 scenes) were novel images that the participant had not encountered during any part of the experiment.
-At the end of each memory block, the participant was given the opportunity to take a short break.
-When they were ready to continue with the next task block, they indicated their readiness to the experimenter.
-The experimenter then entered the testing room, re-ran the eyetracker calibration sequence, and exited the testing room prior to the next task block.
+Participants viewed an attention cue (1.5~s) instructing them to attend to
+either the face or place component of either the left or right images in each
+to-be-viewed composite pair. Next we displayed 10 composite images in
+succession (each preceded by a fixation cross and proceeded by a reaction time
+probe). All possible attention cue pairs appeared exactly twice across the
+eight task blocks.
+
+\paragraph*{Variable attention condition: presentation phase
+(Fig.~\ref{fig:paradigm}G).}
+
+Participants viewed a succession of 10 attention cues (1.5~s), each followed by
+a fixation cross (1~s), composite image (3~s), and a reaction time probe. The
+attention cues were selected pseudorandomly across trials within each block,
+with the constraints that no single attention cue pair could appear more than
+three times across the 10 composite image pairs within a single task block.
+
+\paragraph*{Memory phase (Fig.~\ref{fig:paradigm}F).}
+
+After the presentation phase of each task block, we asked the participant to
+rate the familiarity (on a 1--4 scale, as during the practice phase) of a
+succession of face and place images. Each image was preceded by a 1~s fixation
+cross, and participants had up to 2~s to input their rating of each image.
+Participants made a total of 40 familiarity judgements, about 20 face images
+and 20 place images. Of these, 20 of the images (10 faces and 10 places) were
+drawn randomly from the (attended and unattended) composite images that the
+participant had viewed during the presentation phase. The remaining 20 images
+(10 faces and 10 places) were novel images that the participant had not
+encountered during any part of the experiment. At the end of each memory block,
+the participant was given the opportunity to take a short break. When they were
+ready to continue with the next task block, they indicated their readiness to
+the experimenter. The experimenter then entered the testing room, re-ran the
+eyetracker calibration sequence, and exited the testing room prior to the next
+task block.
+
+\textbf{JRM STOPPED HERE}
 
 \section*{Results}
-We ran two volitional covert attention experiments; in the Sustained Attention Experiment we asked participants to \textit{sustain} the focus of their attention over a succession of 10 stimulus presentations per block whereas in the Variable Attention Experiment we asked participants to \textit{vary} their focus of attention with each new stimulus (also for a total of 10 stimulus presentations per block).
-Each stimulus comprised a pair of composite images (one on the left and one on the right side of the display), where each composite comprised an equal blend of a unique face and a unique scene image.
-We followed the presentation phases of each experimental block with a memory phase, where participants performed a recognition memory task by rating the familiarity of previously experienced and novel face and scene images (see \textit{Materials and methods}, Fig.~\ref{fig:paradigm}).
 
-We considered each image we probed in the memory phase with respect to whether (and how) the participant had experienced and/or attended to that image during the presentation phase (Fig.~\ref{fig:familiarity}).
-For example, if a given face image had been presented as part of the composite image on the right of the screen following an \texttt{attend to the face on the right} instruction, then that face image would have been the focus of the participant's attention during one stimulus presentation.
-The face image on the left (unattended side) during that trial would have been captured by feature-based attention, but not by location-based attention; and the scene image (unattended category) on the right during that trial would have been captured by location-based attention, but not by feature-based attention.
-The scene image on the left during that trial remained outside of the focus of both feature-based and location-based attention.
-In this way, we categorized each of the images that participants experienced during the presentation phases of each experiment in terms of whether they fell under the scope of feature-based and/or location-based attention.
-We also categorized novel face and scene images that we asked participants to judge during the memory phase (i.e., images that the participant hadn't seen before) as belonging to the attention-cued or uncued category.
-These novel images were intended to serve as a baseline for comparison.
-For example, we sought to measure how people rated the familiarity of new images in general.
-We also used differences in familiarity ratings between novel images of the attention-cued versus uncued categories to evaluate potential \textit{prospective} affects of modulating the focus of feature-based attention.
+We ran two volitional covert attention experiments; in the Sustained Attention
+Experiment we asked participants to \textit{sustain} the focus of their
+attention over a succession of 10 stimulus presentations per block whereas in
+the Variable Attention Experiment we asked participants to \textit{vary} their
+focus of attention with each new stimulus (also for a total of 10 stimulus
+presentations per block). Each stimulus comprised a pair of composite images
+(one on the left and one on the right side of the display), where each
+composite comprised an equal blend of a unique face and a unique place image.
+We followed the presentation phases of each experimental block with a memory
+phase, where participants performed a recognition memory task by rating the
+familiarity of previously experienced and novel face and place images (see
+\textit{Materials and methods}, Fig.~\ref{fig:paradigm}).
+
+We considered each image we probed in the memory phase with respect to whether
+(and how) the participant had experienced and/or attended to that image during
+the presentation phase (Fig.~\ref{fig:familiarity}). For example, if a given
+face image had been presented as part of the composite image on the right of
+the screen following an \texttt{attend to the face on the right} instruction,
+then that face image would have been the focus of the participant's attention
+during one stimulus presentation. The face image on the left (unattended side)
+during that trial would have been captured by feature-based attention, but not
+by location-based attention; and the place image (unattended category) on the
+right during that trial would have been captured by location-based attention,
+but not by feature-based attention. The place image on the left during that
+trial remained outside of the focus of both feature-based and location-based
+attention. In this way, we categorized each of the images that participants
+experienced during the presentation phases of each experiment in terms of
+whether they fell under the scope of feature-based and/or location-based
+attention. We also categorized novel face and place images that we asked
+participants to judge during the memory phase (i.e., images that the
+participant hadn't seen before) as belonging to the attention-cued or uncued
+category. These novel images were intended to serve as a baseline for
+comparison. For example, we sought to measure how people rated the familiarity
+of new images in general. We also used differences in familiarity ratings
+between novel images of the attention-cued versus uncued categories to evaluate
+potential \textit{prospective} affects of modulating the focus of feature-based
+attention.
 
@@
   \includegraphics[width=0.75\textwidth]{figures/familiarity}
-  \caption{\textbf{Familiarity ratings for attended, unattended, and novel stimuli.}  Each split violin plot displays the distribution of within-participant average familiarity ratings given to faces (left, darker colors) and scenes (right, lighter colors) during the memory phases of each experiment.
-As shown in the legend (bottom), the colors indicate whether each image had been viewed during the presentation phase (\texttt{old}) or not; whether the given images matched the \texttt{attended category}; and/or whether the given images matched the \texttt{attended location}.
-The colored lines above each set of violin plots denote statistical differences  (\textbf{pos}itive or \textbf{neg}ative differences in mean, collapsing over image category, assessed via two-tailed $t$-tests) between the distributions centered on the endpoints of each line.
-The line thicknesses denote $p$-values as indicated in the legend.
-Asterisks denote differences between the face versus scene distributions (assessed via two-tailed $t$-tests).
-Panel \textbf{a.} displays results from the Sustained Attention Experiment and panel \textbf{b.} displays results from the Variable Attention Experiment.
-Figure~\familiarity~displays these results broken down by participant cohort.}
+
+  \caption{\textbf{Familiarity ratings for attended, unattended, and novel
+  stimuli.} Each split violin plot displays the distribution of
+  within-participant average familiarity ratings given to faces (left, darker
+  colors) and scenes (right, lighter colors) during the memory phases of each
+  experiment. As shown in the legend (bottom), the colors indicate whether each
+  image had been viewed during the presentation phase (\texttt{old}) or not;
+  whether the given images matched the \texttt{attended category}; and/or
+  whether the given images matched the \texttt{attended location}. The colored
+  lines above each set of violin plots denote statistical differences
+  (\textbf{pos}itive or \textbf{neg}ative differences in mean, collapsing over
+  image category, assessed via two-tailed $t$-tests) between the distributions
+  centered on the endpoints of each line. The line thicknesses denote
+  $p$-values as indicated in the legend. Asterisks denote differences between
+  the face versus scene distributions (assessed via two-tailed $t$-tests).
+  Panel \textbf{a.} displays results from the Sustained Attention Experiment
+  and panel \textbf{b.} displays results from the Variable Attention
+  Experiment. Figure~\familiarity~displays these results broken down by
+  participant cohort.}
+
 \label{fig:familiarity}
@@
 
-Participants in both experiments rated stimuli they attended as more familiar than unattended or novel stimuli (Fig.~\ref{fig:familiarity}; Sustained Attention Experiment: $t(59) = 13.42, p = 1.39 \times 10^{-19}, d = 1.73$; Variable Attention Experiment: $t(52) = 12.40, p = 3.70 \times 10^{-17}, d = 1.70$).
-Participants in both experiments also rated attended scene stimuli as more familiar than attended face stimuli (Sustained Attention Experiment: $t(59) = 7.69, p = 1.85 \times 10^{-10}, d = 0.99$; Variable Attention Experiment: $t(52) = 7.08, p = 3.63 \times 10^{-9}, d = 0.97$).
-These findings indicate that aspects of experience that are captured by the focus of attention are easier to recognize later, and that attention may preferentially benefit memory for some aspects of experience to a greater extent than other aspects of experience.
+Participants in both experiments rated stimuli they attended as more familiar
+than unattended or novel stimuli (Fig.~\ref{fig:familiarity}; Sustained
+Attention Experiment: $t(59) = 13.42, p = 1.39 \times 10^{-19}, d = 1.73$;
+Variable Attention Experiment: $t(52) = 12.40, p = 3.70 \times 10^{-17}, d =
+1.70$). Participants in both experiments also rated attended scene stimuli as
+more familiar than attended face stimuli (Sustained Attention Experiment:
+$t(59) = 7.69, p = 1.85 \times 10^{-10}, d = 0.99$; Variable Attention
+Experiment: $t(52) = 7.08, p = 3.63 \times 10^{-9}, d = 0.97$). These findings
+indicate that aspects of experience that are captured by the focus of attention
+are easier to recognize later, and that attention may preferentially benefit
+memory for some aspects of experience to a greater extent than other aspects of
+experience.
 
-Participants in the Sustained Attention Experiment experiment also rated unattended images that matched the attended category as more familiar than unattended images that did not match the attended category (\textit{incidental feature-based attention}; $t(59) = 7.17, p = 1.40 \times 10^{-9}, d = 0.93$).
-This pattern did not hold for participants in the Variable Attention Experiment ($t(52) = 0.44, p = 0.66, d = 0.06$).
-Participants in both experiments displayed an incidental effect of location-based attention, whereby they rated unattended-category images at the attended location as more familiar than unattended-category images at the unattended location (Sustained Attention Experiment: $t(59) = 4.32, p = 6.05 \times 10^{-5}, d = 0.56$; Variable Attention Experiment: $t(52) = 2.57, p = 0.01, d = 0.35$).
-This indicates that aspects of our experience that incidentally overlap with the focus of our location-based attention are easier to recognize later, even if those aspects do not fall within the intentional focus of our feature-based attention.
+Participants in the Sustained Attention Experiment experiment also rated
+unattended images that matched the attended category as more familiar than
+unattended images that did not match the attended category (\textit{incidental
+feature-based attention}; $t(59) = 7.17, p = 1.40 \times 10^{-9}, d = 0.93$).
+This pattern did not hold for participants in the Variable Attention Experiment
+($t(52) = 0.44, p = 0.66, d = 0.06$). Participants in both experiments
+displayed an incidental effect of location-based attention, whereby they rated
+unattended-category images at the attended location as more familiar than
+unattended-category images at the unattended location (Sustained Attention
+Experiment: $t(59) = 4.32, p = 6.05 \times 10^{-5}, d = 0.56$; Variable
+Attention Experiment: $t(52) = 2.57, p = 0.01, d = 0.35$). This indicates that
+aspects of our experience that incidentally overlap with the focus of our
+location-based attention are easier to recognize later, even if those aspects
+do not fall within the intentional focus of our feature-based attention.
 
-We defined the \textit{memory benefit of feature-based attention} as the difference in mean familiarity ratings of attended stimuli and unattended stimuli from the attended category versus the mean familiarity ratings of unattended stimuli from the unattended category.
-Similarly, we defined the \textit{memory benefit of location-based attention} as the difference in mean familiarity ratings of attended stimuli and unattended stimuli from the attended location versus the mean familiarity ratings of unattended stimuli from the unattended location.
-Participants in the Sustained Attention Experiment displayed a larger memory benefit of feature-based attention than location-based attention ($t(59) = 3.25, p = 1.91 \times 10^{-3}, d = 0.42$), whereas participants in the Variable Attention Experiment displayed a larger memory benefit of location-based attention ($t(52) = 1.70, p = 9.99 \times 10^{-2}, d = 0.23$).
-This appeared to be driven in part by a response bias towards attended-category images.
-For example, relative to the most recent attention cue, participants in the Sustained Attention Experiment rated attended-category novel images as more familiar than unattended-category novel images ($t(59) = 7.04, p = 2.35 \times 10^{-9}, d = 0.91$), whereas participants in the Variable Attention Experiment responded similarly to attended-category and unattended-category novel images ($t(52) = 0.23, p = 0.82, d = 0.03$).
-The size of this attended-category response bias for novel images was reliably smaller than the memory benefits of feature-based attention in both experiments (Sustained Attention Experiment: $t(59) = 7.59, p = 2.68 \times 10^{-10}, d = 0.98$; Variable Attention Experiment: $t(52) = 6.74, p = 1.31 \times 10^{-8}, d = 0.93$).
-This indicates that tuning the focus of feature-based attention with respect to how ongoing experience is encoded in memory takes longer than the duration of a single stimulus presentation (including fixation, roughly 5.5~s).
-Further, once feature-based attention comes ``online,'' it affects how \textit{new} stimuli are processed.
+We defined the \textit{memory benefit of feature-based attention} as the
+difference in mean familiarity ratings of attended stimuli and unattended
+stimuli from the attended category versus the mean familiarity ratings of
+unattended stimuli from the unattended category. Similarly, we defined the
+\textit{memory benefit of location-based attention} as the difference in mean
+familiarity ratings of attended stimuli and unattended stimuli from the
+attended location versus the mean familiarity ratings of unattended stimuli
+from the unattended location. Participants in the Sustained Attention
+Experiment displayed a larger memory benefit of feature-based attention than
+location-based attention ($t(59) = 3.25, p = 1.91 \times 10^{-3}, d = 0.42$),
+whereas participants in the Variable Attention Experiment displayed a larger
+memory benefit of location-based attention ($t(52) = 1.70, p = 9.99 \times
+10^{-2}, d = 0.23$). This appeared to be driven in part by a response bias
+towards attended-category images. For example, relative to the most recent
+attention cue, participants in the Sustained Attention Experiment rated
+attended-category novel images as more familiar than unattended-category novel
+images ($t(59) = 7.04, p = 2.35 \times 10^{-9}, d = 0.91$), whereas
+participants in the Variable Attention Experiment responded similarly to
+attended-category and unattended-category novel images ($t(52) = 0.23, p =
+0.82, d = 0.03$). The size of this attended-category response bias for novel
+images was reliably smaller than the memory benefits of feature-based attention
+in both experiments (Sustained Attention Experiment: $t(59) = 7.59, p = 2.68
+\times 10^{-10}, d = 0.98$; Variable Attention Experiment: $t(52) = 6.74, p =
+1.31 \times 10^{-8}, d = 0.93$). This indicates that tuning the focus of
+feature-based attention with respect to how ongoing experience is encoded in
+memory takes longer than the duration of a single stimulus presentation
+(including fixation, roughly 5.5~s). Further, once feature-based attention
+comes ``online,'' it affects how \textit{new} stimuli are processed.
 
-We also compared the relative sizes of the memory benefits of feature-based attention and location-based attention across the two experiments.
-Participants in the Sustained Attention Experiment displayed a larger difference between these two effects than did participants in the Variable Attention Experiment ($t(111) = 3.48, p = 7.24 \times 10^{-4}, d = 0.66$).
-Further, the difference in mean familiarity ratings of attended-location images versus unattended images was greater for participants in the Variable Attention Experiment ($t(111) = 2.32, p = 0.02, d = 0.44$).
-The memory benefit of location-based attention reliably distinguished between attended-category versus unattended category images for participants in both experiments (Sustained Attention Experiment: $t(59) = 9.50, p = 1.68 \times 10^{-13}, d = 1.23$; Variable Attention Experiment: $t(52) = 9.72, p = 2.76 \times 10^{-13}, d = 1.33$).
-This indicates that tuning the focus of location-based attention with respect to how ongoing experience is encoded into memory occurs faster than the duration of a single stimulus presentation.
+We also compared the relative sizes of the memory benefits of feature-based
+attention and location-based attention across the two experiments. Participants
+in the Sustained Attention Experiment displayed a larger difference between
+these two effects than did participants in the Variable Attention Experiment
+($t(111) = 3.48, p = 7.24 \times 10^{-4}, d = 0.66$). Further, the difference
+in mean familiarity ratings of attended-location images versus unattended
+images was greater for participants in the Variable Attention Experiment
+($t(111) = 2.32, p = 0.02, d = 0.44$). The memory benefit of location-based
+attention reliably distinguished between attended-category versus unattended
+category images for participants in both experiments (Sustained Attention
+Experiment: $t(59) = 9.50, p = 1.68 \times 10^{-13}, d = 1.23$; Variable
+Attention Experiment: $t(52) = 9.72, p = 2.76 \times 10^{-13}, d = 1.33$). This
+indicates that tuning the focus of location-based attention with respect to how
+ongoing experience is encoded into memory occurs faster than the duration of a
+single stimulus presentation.
 
-We also compared reaction times to probes from the attended versus unattended side.
-Participants in both experiments responded slightly faster on average to attended-side probes, although the differences did not reach significance (Sustained Attention Experiment: $t(59) = 1.03, p = 0.31, d = 0.13$; Variable Attention Experiment: $t(52) = 0.65, p = 0.52, d = 0.09$).
-Participants in the Sustained Attention Experiment displayed a slightly larger (and not statistically significant) difference in attended-side versus unattended-side reaction times than participants in the Variable Attention Experiment ($t(111) = .87, p = 0.38, d = 0.20$).
-Because none of these reaction time effects were statistically reliable, we are unable to draw meaningful conclusions about reaction times to the attention probes on the attended versus unattended side, nor are we able to draw meaningful conclusions about differences in those reaction times that might be due to sustained versus variable attention.
+We also compared reaction times to probes from the attended versus unattended
+side. Participants in both experiments responded slightly faster on average to
+attended-side probes, although the differences did not reach significance
+(Sustained Attention Experiment: $t(59) = 1.03, p = 0.31, d = 0.13$; Variable
+Attention Experiment: $t(52) = 0.65, p = 0.52, d = 0.09$). Participants in the
+Sustained Attention Experiment displayed a slightly larger (and not
+statistically significant) difference in attended-side versus unattended-side
+reaction times than participants in the Variable Attention Experiment ($t(111)
+= .87, p = 0.38, d = 0.20$). Because none of these reaction time effects were
+statistically reliable, we are unable to draw meaningful conclusions about
+reaction times to the attention probes on the attended versus unattended side,
+nor are we able to draw meaningful conclusions about differences in those
+reaction times that might be due to sustained versus variable attention.
 
@@
   \includegraphics[width=\textwidth]{figures/exps1_2_xgaze.pdf}
-  \caption{\textbf{Horizontal coordinates of visual fixations.}  Each violin plot displays a distribution of participant-wise average horizontal gaze positions relative to a presented image.
-The coordinates have been normalized such that a value of 1.0 denotes the furthest onscreen coordinate from the central fixation point \textit{towards} the direction of the given image, and -1.0 denotes the furthest onscreen coordinate from the central fixation point \textit{away from} the direction of the given image.
-The gray bars in each panel mark the boundaries of the presented images.
-The violin plots are broken down by participants' familiarity ratings during the memory phases of each experiment, and by each image's relation to the attention cue while that image appeared onscreen.
-Panel \textbf{a.} displays fixation data for the Sustained Attention Experiment and Panel \textbf{b.} displays fixation data for the Variable Attention Experiment.
-Figure~\fixation~displays these results broken down by participant cohort.}
+
+  \caption{\textbf{Horizontal coordinates of visual fixations.} Each violin
+  plot displays a distribution of participant-wise average horizontal gaze
+  positions relative to a presented image. The coordinates have been normalized
+  such that a value of 1.0 denotes the furthest onscreen coordinate from the
+  central fixation point \textit{towards} the direction of the given image, and
+  -1.0 denotes the furthest onscreen coordinate from the central fixation point
+  \textit{away from} the direction of the given image. The gray bars in each
+  panel mark the boundaries of the presented images. The violin plots are
+  broken down by participants' familiarity ratings during the memory phases of
+  each experiment, and by each image's relation to the attention cue while that
+  image appeared onscreen. Panel \textbf{a.} displays fixation data for the
+  Sustained Attention Experiment and Panel \textbf{b.} displays fixation data
+  for the Variable Attention Experiment. Figure~\fixation~displays these
+  results broken down by participant cohort.}
+
 \label{fig:fixation}
@@
 
-Given that participants in both experiments rated attended-location images from both the attended and unattended category as more familiar than unattended-location images, we wondered whether this was truly a consequence of covert attention, or whether it might be driven solely by where participants were looking.
-In other words, we sought to distinguish the memory effects of the focus of covert attention from the focus of visual gaze.
-We used eyetracking to measure the horizontal positions of the participants' visual fixations while each pair of composite stimuli appeared onscreen (Fig.~\ref{fig:fixation}).
-For 94\% of presentation trials (Sustained Attention Task: $\frac{4531}{4800}$ trials; Variable Attention Task: $\frac{3972}{4240}$ trials), we collected viable gaze data for analysis.
-In the remaining trials, participant movement or other technical issues corrupted the gaze data.
-We found that, though they generally followed our instruction to keep their gaze fixed on the center of the screen, participants in both experiments exhibited a slight tendency to look towards the side of the screen they were attending to (Sustained Attention Task: $t(59) = 3.61, p = 6.31 \times 10^{-4}$; Variable Attention Task: $t(52) = 2.86, p = 6.06 \times 10^{-3}$).
-When we limited our analyses to trials with viable gaze data where participants successfully maintained fixation on the center of the screen within 4.28$^\circ$ visual angle (i.e., between the rightmost boundary of the left image and the leftmost boundary of the right image) we observed (numerical) memory benefits of feature-based attention in both experiments (Sustained Attention Experiment: $t(59) = 4.73, p = 1.96 \times 10^{-5}, d = 0.67$; Variable Attention Experiment: $t(52) = 0.64, p = 0.52, d = 0.09$) and location-based attention in the Sustained Attention Experiment, but not the Variable Attention Experiment (Sustained Attention Experiment: $t(59) = 0.67, p = 0.51, d = 0.09$; Variable Attention Experiment: $t(52) = -0.79, p = 0.43, d = 0.11$).
-These analyses indicate that although the focus of covert attention can affect where people are looking, covert attention affects memory encoding beyond what may be accounted for by gaze position alone.
+Given that participants in both experiments rated attended-location images from
+both the attended and unattended category as more familiar than
+unattended-location images, we wondered whether this was truly a consequence of
+covert attention, or whether it might be driven solely by where participants
+were looking. In other words, we sought to distinguish the memory effects of
+the focus of covert attention from the focus of visual gaze. We used
+eyetracking to measure the horizontal positions of the participants' visual
+fixations while each pair of composite stimuli appeared onscreen
+(Fig.~\ref{fig:fixation}). For 94\% of presentation trials (Sustained Attention
+Task: $\frac{4531}{4800}$ trials; Variable Attention Task: $\frac{3972}{4240}$
+trials), we collected viable gaze data for analysis. In the remaining trials,
+participant movement or other technical issues corrupted the gaze data. We
+found that, though they generally followed our instruction to keep their gaze
+fixed on the center of the screen, participants in both experiments exhibited a
+slight tendency to look towards the side of the screen they were attending to
+(Sustained Attention Task: $t(59) = 3.61, p = 6.31 \times 10^{-4}$; Variable
+Attention Task: $t(52) = 2.86, p = 6.06 \times 10^{-3}$). When we limited our
+analyses to trials with viable gaze data where participants successfully
+maintained fixation on the center of the screen within 4.28$^\circ$ visual
+angle (i.e., between the rightmost boundary of the left image and the leftmost
+boundary of the right image) we observed (numerical) memory benefits of
+feature-based attention in both experiments (Sustained Attention Experiment:
+$t(59) = 4.73, p = 1.96 \times 10^{-5}, d = 0.67$; Variable Attention
+Experiment: $t(52) = 0.64, p = 0.52, d = 0.09$) and location-based attention in
+the Sustained Attention Experiment, but not the Variable Attention Experiment
+(Sustained Attention Experiment: $t(59) = 0.67, p = 0.51, d = 0.09$; Variable
+Attention Experiment: $t(52) = -0.79, p = 0.43, d = 0.11$). These analyses
+indicate that although the focus of covert attention can affect where people
+are looking, covert attention affects memory encoding beyond what may be
+accounted for by gaze position alone.
 
-The preceding results indicate that volitional covert attention affects memory, and that feature-based and location-based covert attention may come online at different timescales.
-We next sought to examine how long the memory effects of feature-based and location-based covert attention persist.
-To gain additional insights into the timecourse of the impact of feature-based and location-based attention on memory, we used a sliding window analysis to measure how participants' familiarity ratings of attended, partially attended, unattended, and novel stimuli varied over the duration of the memory phases of both experiments.
-During each block within the memory phases of each experiment, participants made familiarity judgements about a total of 40 images (20 old images and 20 novel images).
-We computed average familiarity ratings for images appearing in each position of the memory stimulus sequence (positions 1--40), as a function of how (or whether) they were attended during the preceding presentation phase (old images) or whether they matched the category of the most recent attention cue (novel images), for overlapping 20-image sliding windows (Figs.~\ref{fig:familiarity_timecourse_category}, \ref{fig:familiarity_timecourse_location}, and \ref{fig:familiarity_timecourse_novel}).
-We first calculated these values for each participant, and then we averaged across participants.
+The preceding results indicate that volitional covert attention affects memory,
+and that feature-based and location-based covert attention may come online at
+different timescales. We next sought to examine how long the memory effects of
+feature-based and location-based covert attention persist. To gain additional
+insights into the timecourse of the impact of feature-based and location-based
+attention on memory, we used a sliding window analysis to measure how
+participants' familiarity ratings of attended, partially attended, unattended,
+and novel stimuli varied over the duration of the memory phases of both
+experiments. During each block within the memory phases of each experiment,
+participants made familiarity judgements about a total of 40 images (20 old
+images and 20 novel images). We computed average familiarity ratings for images
+appearing in each position of the memory stimulus sequence (positions 1--40),
+as a function of how (or whether) they were attended during the preceding
+presentation phase (old images) or whether they matched the category of the
+most recent attention cue (novel images), for overlapping 20-image sliding
+windows (Figs.~\ref{fig:familiarity_timecourse_category},
+\ref{fig:familiarity_timecourse_location}, and
+\ref{fig:familiarity_timecourse_novel}). We first calculated these values for
+each participant, and then we averaged across participants.
 
@@
   \includegraphics[width=1\textwidth]{figures/Cat_Cued_TimeSeries.pdf}
-  \caption{\textbf{Familiarity ratings over time for images that matched the cued or uncued image category.}  Each curve reflects the average familiarity ratings for attended, unattended, and novel images (denoted in the legends on the right) within a succession of overlapping 20-image sliding windows.
-Error ribbons denote 95\% confidence intervals, computed across participants.
-Panels \textbf{a.} and \textbf{c.} display results from the Sustained Attention Experiment and Panels \textbf{b.} and \textbf{d.} display results from the Variable Attention Experiment.
-The paired horizontal lines at the bottom of each panel denote timepoints when the given pair of curves was statistically distinguishable (i.e., the topmost line color was statistically greater than the bottommost line color at $\alpha = 0.05$, via a paired two-tailed $t$-test.)  The gray lines in Panels b and d reflect familiarity ratings of novel stimuli from both the most recently attended and unattended image categories.
-Figures~\timecourseCuedCategory~and \timecourseUncuedCategory~display these results broken down by participant cohort.}
+
+  \caption{\textbf{Familiarity ratings over time for images that matched the
+  cued or uncued image category.} Each curve reflects the average familiarity
+  ratings for attended, unattended, and novel images (denoted in the legends on
+  the right) within a succession of overlapping 20-image sliding windows. Error
+  ribbons denote 95\% confidence intervals, computed across participants.
+  Panels \textbf{a.} and \textbf{c.} display results from the Sustained
+  Attention Experiment and Panels \textbf{b.} and \textbf{d.} display results
+  from the Variable Attention Experiment. The paired horizontal lines at the
+  bottom of each panel denote timepoints when the given pair of curves was
+  statistically distinguishable (i.e., the topmost line color was statistically
+  greater than the bottommost line color at $\alpha = 0.05$, via a paired
+  two-tailed $t$-test.) The gray lines in Panels b and d reflect familiarity
+  ratings of novel stimuli from both the most recently attended and unattended
+  image categories. Figures~\timecourseCuedCategory~and
+  \timecourseUncuedCategory~display these results broken down by participant
+  cohort.}
+
 \label{fig:familiarity_timecourse_category}
@@
 
-Throughout the memory phase, participants from both experiments rated attended images as more familiar than category-matched unattended and novel images (Fig.~\ref{fig:familiarity_timecourse_category}, top row).
-This indicates that the memory benefits of attending to specific stimulus features (versus category-general features) persist for at least as long as the duration of the memory phase (2~min).
-Early in the memory phase, participants in the Variable Attention Experiment also rated category-matched unattended images as more familiar than novel images.
-This pattern did not hold for participants in the Sustained Attention Experiment.
-The short-lived boost in familiarity for attended-category images at the unattended location following variable (but not sustained) attention suggests that the timecourse of feature-based attention's impact on memory depends on how long the focus of feature-based attention has been held.
+Throughout the memory phase, participants from both experiments rated attended
+images as more familiar than category-matched unattended and novel images
+(Fig.~\ref{fig:familiarity_timecourse_category}, top row). This indicates that
+the memory benefits of attending to specific stimulus features (versus
+category-general features) persist for at least as long as the duration of the
+memory phase (2~min). Early in the memory phase, participants in the Variable
+Attention Experiment also rated category-matched unattended images as more
+familiar than novel images. This pattern did not hold for participants in the
+Sustained Attention Experiment. The short-lived boost in familiarity for
+attended-category images at the unattended location following variable (but not
+sustained) attention suggests that the timecourse of feature-based attention's
+impact on memory depends on how long the focus of feature-based attention has
+been held.
 
-Participants in both experiments also rated unattended-category images at the attended location as more familiar than unattended-category images at the unattended location and novel unattended-category images (Fig.~\ref{fig:familiarity_timecourse_category}, bottom row).
-This pattern persisted throughout the memory phases of both experiments.
-This supports the notion that location-based attention enhances memory in a (partially) feature-independent way.
-Participants in the Variable Attention Experiment also rated unattended-category images at the unattended location as (numerically) more familiar than novel images (though this pattern was only statistically reliable towards the middle of the memory phase).
-This pattern did not hold for participants in the Sustained Attention Experiment.
-Participants in the Sustained Attention Experiment rated unattended-category images (regardless of location or novelty status) as less familiar than participants in the Variable Attention Experiment (e.g., compare heights of the lines in the bottom left versus bottom right panels of Fig.~\ref{fig:familiarity_timecourse_category}).
-This suggests that, after sustained feature-based attention to a particular image category, the encodings of stimuli from the unattended category are suppressed.
-This suppression effect appears to persist at least as long as the memory phase of the experiment (2~min).
-Further, the magnitude of this suppression effect appears to become stronger following longer-term sustained (versus shorter-term variable) feature-based attention.
+Participants in both experiments also rated unattended-category images at the
+attended location as more familiar than unattended-category images at the
+unattended location and novel unattended-category images
+(Fig.~\ref{fig:familiarity_timecourse_category}, bottom row). This pattern
+persisted throughout the memory phases of both experiments. This supports the
+notion that location-based attention enhances memory in a (partially)
+feature-independent way. Participants in the Variable Attention Experiment also
+rated unattended-category images at the unattended location as (numerically)
+more familiar than novel images (though this pattern was only statistically
+reliable towards the middle of the memory phase). This pattern did not hold for
+participants in the Sustained Attention Experiment. Participants in the
+Sustained Attention Experiment rated unattended-category images (regardless of
+location or novelty status) as less familiar than participants in the Variable
+Attention Experiment (e.g., compare heights of the lines in the bottom left
+versus bottom right panels of Fig.~\ref{fig:familiarity_timecourse_category}).
+This suggests that, after sustained feature-based attention to a particular
+image category, the encodings of stimuli from the unattended category are
+suppressed. This suppression effect appears to persist at least as long as the
+memory phase of the experiment (2~min). Further, the magnitude of this
+suppression effect appears to become stronger following longer-term sustained
+(versus shorter-term variable) feature-based attention.
 
@@
   \includegraphics[width=\textwidth]{figures/Side_Cued_TimeSeries_2.pdf}
-  \caption{\textbf{Familiarity ratings over time for images that matched the cued or uncued image location.}  This figure follows the same format and conventions as Figure~\ref{fig:familiarity_timecourse_category}.
-Figures~\timecourseCuedLocation~and \timecourseUncuedLocation~display these results broken down by participant cohort.}
+
+  \caption{\textbf{Familiarity ratings over time for images that matched the
+  cued or uncued image location.} This figure follows the same format and
+  conventions as Figure~\ref{fig:familiarity_timecourse_category}.
+  Figures~\timecourseCuedLocation~and \timecourseUncuedLocation~display these
+  results broken down by participant cohort.}
+
 \label{fig:familiarity_timecourse_location}
@@
 
-We next examined how participants' familiarity ratings varied over the duration of the memory phases of each experiment as a function of the attended location.
-Participants in the Sustained Attention Experiment rated attended-category images as more familiar, at both the attended and unattended locations (Fig.~\ref{fig:familiarity_timecourse_location}, left panels).
-In contrast, participants in the Variable Attention Experiment rated attended-category images as more familiar than unattended-category images only at the attended locations (Fig.~\ref{fig:familiarity_timecourse_location}, right panels).
-The primary difference in familiarity ratings between Sustained Attention Experiment versus Variable Attention Experiment participants was in how they rated unattended-category images.
-Participants in the Variable Attention Task rated unattended-category images as more familiar than did participants in the Sustained Attention Task; this pattern persisted throughout the memory phase and held for images at both the attended and unattended locations (compare heights of blue lines in the left versus right panels of Fig.~\ref{fig:familiarity_timecourse_location}).
-This suggests that lower familiarity ratings of unattended-category stimuli in the Sustained Attention Experiment are due to suppression of the encoding of unattended-category features (e.g., as opposed to enhancement of the encoding of attended-category features).
-This suppression effect appears to build over an interval that is longer than the duration of a single stimulus presentation (5.5~s).
+We next examined how participants' familiarity ratings varied over the duration
+of the memory phases of each experiment as a function of the attended location.
+Participants in the Sustained Attention Experiment rated attended-category
+images as more familiar, at both the attended and unattended locations
+(Fig.~\ref{fig:familiarity_timecourse_location}, left panels). In contrast,
+participants in the Variable Attention Experiment rated attended-category
+images as more familiar than unattended-category images only at the attended
+locations (Fig.~\ref{fig:familiarity_timecourse_location}, right panels). The
+primary difference in familiarity ratings between Sustained Attention
+Experiment versus Variable Attention Experiment participants was in how they
+rated unattended-category images. Participants in the Variable Attention Task
+rated unattended-category images as more familiar than did participants in the
+Sustained Attention Task; this pattern persisted throughout the memory phase
+and held for images at both the attended and unattended locations (compare
+heights of blue lines in the left versus right panels of
+Fig.~\ref{fig:familiarity_timecourse_location}). This suggests that lower
+familiarity ratings of unattended-category stimuli in the Sustained Attention
+Experiment are due to suppression of the encoding of unattended-category
+features (e.g., as opposed to enhancement of the encoding of attended-category
+features). This suppression effect appears to build over an interval that is
+longer than the duration of a single stimulus presentation (5.5~s).
 
@@
   \includegraphics[width=1\textwidth]{figures/Novel_Timecourse_Panels.pdf}
-  \caption{\textbf{Familiarity ratings over time for attended-category and unattended-category novel images.}  The top panels of this figure follow the same formats and conventions as Figures~\ref{fig:familiarity_timecourse_category} and \ref{fig:familiarity_timecourse_location}.
-The bottom panels display the differences between the timecourses of familiarity ratings of attended-category and unattended-category novel stimuli.
-The error ribbons denote 95\% confidence intervals, computed across participants.
-The dotted horizontal line in each panel denotes a difference of 0-- i.e., the value above which attended-category novel images were rated as more familiar than unattended-category novel images.
-The black lines in the bottom panels display linear regression fits to the data (error ribbons denote 95\% confidence intervals).
-Figures~\timecourseNovel~and \timecourseDiff~display these results broken down by participant cohort.}
+
+  \caption{\textbf{Familiarity ratings over time for attended-category and
+  unattended-category novel images.} The top panels of this figure follow the
+  same formats and conventions as
+  Figures~\ref{fig:familiarity_timecourse_category} and
+  \ref{fig:familiarity_timecourse_location}. The bottom panels display the
+  differences between the timecourses of familiarity ratings of
+  attended-category and unattended-category novel stimuli. The error ribbons
+  denote 95\% confidence intervals, computed across participants. The dotted
+  horizontal line in each panel denotes a difference of 0-- i.e., the value
+  above which attended-category novel images were rated as more familiar than
+  unattended-category novel images. The black lines in the bottom panels
+  display linear regression fits to the data (error ribbons denote 95\%
+  confidence intervals). Figures~\timecourseNovel~and \timecourseDiff~display
+  these results broken down by participant cohort.}
+
 \label{fig:familiarity_timecourse_novel}
@@
 
-Finally, we examined how participants in both experiments rated the familiarity of novel images.
-These ratings provide insights into how modulating the focus of attention to \textit{prior} stimuli can affect the perception of \textit{future} stimuli.
-We considered how participants rated novel stimuli that matched versus did not match the category (face or scene) of the most recent attention cue.
-Participants in the Sustained Attention Experiment rated attended-category novel stimuli as more familiar than unattended-category novel stimuli throughout the entire memory phase (Fig.~\ref{fig:familiarity_timecourse_novel}a).
-By contrast, participants in the Variable Attention Experiment rated attended-category and unattended-category novel images similarly throughout the memory phase (Fig.~\ref{fig:familiarity_timecourse_novel}b).
-The difference in familiarity ratings between the two experiments primarily reflects that participants in the Variable Attention Experiment rated unattended-category novel images as more familiar than did participants in the Sustained Attention Experiment (e.g., compare blue lines in Fig.~\ref{fig:familiarity_timecourse_novel}a versus \ref{fig:familiarity_timecourse_novel}b).
-This may indicate that the processing of unattended-category novel stimuli is suppressed following sustained attention (e.g., as opposed to enhancing the processing of attended-category novel stimuli).
-The differences in familiarity between attended-category versus unattended-category novel images increased slightly but reliably throughout the memory phases of both experiments (Fig.~\ref{fig:familiarity_timecourse_novel}, bottom panels; slope of regression line fit to differences in Sustained Attention Experiment: $\beta = 2.05 \times 10^{-3}, p = 1.07 \times 10^{-14} $; slope of regression for Variable Attention Experiment: $\beta = 1.54 \times 10^{-3}, p = 5.63 \times 10^{-13} $).
-This might reflect a process whereby the suppression of unattended features continues to build for a short duration even after the participant stops volitionally focusing on the attended features.
+Finally, we examined how participants in both experiments rated the familiarity
+of novel images. These ratings provide insights into how modulating the focus
+of attention to \textit{prior} stimuli can affect the perception of
+\textit{future} stimuli. We considered how participants rated novel stimuli
+that matched versus did not match the category (face or scene) of the most
+recent attention cue. Participants in the Sustained Attention Experiment rated
+attended-category novel stimuli as more familiar than unattended-category novel
+stimuli throughout the entire memory phase
+(Fig.~\ref{fig:familiarity_timecourse_novel}a). By contrast, participants in
+the Variable Attention Experiment rated attended-category and
+unattended-category novel images similarly throughout the memory phase
+(Fig.~\ref{fig:familiarity_timecourse_novel}b). The difference in familiarity
+ratings between the two experiments primarily reflects that participants in the
+Variable Attention Experiment rated unattended-category novel images as more
+familiar than did participants in the Sustained Attention Experiment (e.g.,
+compare blue lines in Fig.~\ref{fig:familiarity_timecourse_novel}a versus
+\ref{fig:familiarity_timecourse_novel}b). This may indicate that the processing
+of unattended-category novel stimuli is suppressed following sustained
+attention (e.g., as opposed to enhancing the processing of attended-category
+novel stimuli). The differences in familiarity between attended-category versus
+unattended-category novel images increased slightly but reliably throughout the
+memory phases of both experiments (Fig.~\ref{fig:familiarity_timecourse_novel},
+bottom panels; slope of regression line fit to differences in Sustained
+Attention Experiment: $\beta = 2.05 \times 10^{-3}, p = 1.07 \times 10^{-14} $;
+slope of regression for Variable Attention Experiment: $\beta = 1.54 \times
+10^{-3}, p = 5.63 \times 10^{-13} $). This might reflect a process whereby the
+suppression of unattended features continues to build for a short duration even
+after the participant stops volitionally focusing on the attended features.
 
 \section*{Discussion}
-We ran two covert attention experiments that asked participants to sustain or vary the focus of their covert attention, respectively.
-When participants held the focus of their feature-based (face versus scene) and location-based (left versus right) attention for a sustained interval, they judged stimuli they had seen as familiar when they overlapped with respect to the features and locations they had attended.
-The increase in familiarity was larger for attended-feature images than attended-location images.
-The increase also extended to novel stimuli from the attended image category.
-By contrast, when participants varied the focus of their feature-based and location-based attention more rapidly, the boost in familiarity for feature-matched stimuli was smaller than that for location-matched stimuli, and did not extend to novel stimuli.
-Our findings suggest that participants were able to more rapidly modulate their focus of location-based attention than their focus of feature-based attention.
-The tuning of location-based attention appears to be mediated by enhanced encoding and faster processing at the attended location.
-The tuning of feature-based attention appears to be mediated by a suppression in the encoding and processing of unattended stimulus features.
-This suppression effect also affects how new stimuli are processed, and it persists for a longer duration following an interval when the focus of feature-based attention was held constant over a longer duration.
-Taken together, our findings suggest that feature-based and location-based attention are mediated by different mechanisms and affect memory at different timescales (Fig.~\ref{fig:model}).
+
+We ran two covert attention experiments that asked participants to sustain or
+vary the focus of their covert attention, respectively. When participants held
+the focus of their feature-based (face versus scene) and location-based (left
+versus right) attention for a sustained interval, they judged stimuli they had
+seen as familiar when they overlapped with respect to the features and
+locations they had attended. The increase in familiarity was larger for
+attended-feature images than attended-location images. The increase also
+extended to novel stimuli from the attended image category. By contrast, when
+participants varied the focus of their feature-based and location-based
+attention more rapidly, the boost in familiarity for feature-matched stimuli
+was smaller than that for location-matched stimuli, and did not extend to novel
+stimuli. Our findings suggest that participants were able to more rapidly
+modulate their focus of location-based attention than their focus of
+feature-based attention. The tuning of location-based attention appears to be
+mediated by enhanced encoding and faster processing at the attended location.
+The tuning of feature-based attention appears to be mediated by a suppression
+in the encoding and processing of unattended stimulus features. This
+suppression effect also affects how new stimuli are processed, and it persists
+for a longer duration following an interval when the focus of feature-based
+attention was held constant over a longer duration. Taken together, our
+findings suggest that feature-based and location-based attention are mediated
+by different mechanisms and affect memory at different timescales
+(Fig.~\ref{fig:model}).
 
@@
   \centering \includegraphics[width=0.75\textwidth]{figures/discussion_schematic}
-  \caption{\textbf{Timecourse of encoding and retrieval effects of feature-based and location-based attention.}  The focus of location-based attention (green) may be modulated quickly and rapidly enhances memory encoding for nearby stimuli.
-The focus of feature-based attention (purple) is modulated more slowly, and serves to suppress unattended stimulus features.
-The effects of location-based attention on memory persist for longer than the effects of feature-based attention.
-Sustained attention (darker shading) yields more robust enhancement and suppression than shorter-term (variable) attention (light shading).
-The vertical gray line on the left denotes the duration of a single stimulus presentation (the upper bound by which location-based attention begins to affect encoding, and the lower-bound by which feature-based attention begins to affect encoding).
-The vertical gray line on the right separates encoding from immediate subsequent retrieval of the encoded information.}
+
+  \caption{\textbf{Timecourse of encoding and retrieval effects of
+  feature-based and location-based attention.} The focus of location-based
+  attention (green) may be modulated quickly and rapidly enhances memory
+  encoding for nearby stimuli. The focus of feature-based attention (purple) is
+  modulated more slowly, and serves to suppress unattended stimulus features.
+  The effects of location-based attention on memory persist for longer than the
+  effects of feature-based attention. Sustained attention (darker shading)
+  yields more robust enhancement and suppression than shorter-term (variable)
+  attention (light shading). The vertical gray line on the left denotes the
+  duration of a single stimulus presentation (the upper bound by which
+  location-based attention begins to affect encoding, and the lower-bound by
+  which feature-based attention begins to affect encoding). The vertical gray
+  line on the right separates encoding from immediate subsequent retrieval of
+  the encoded information.}
+
 \label{fig:model}
@@
 
-The notion that location-based attention operates at a faster timescale than feature-based attention is supported by prior work on the deployment of visual attention~\citep{SotoBlan04, StopEtal07}.
-Our findings that location-based attention enhances the processing of attended stimuli whereas feature-based attention suppresses the processing of unattended stimuli is also consistent with prior work on location-based attention~\citep[e.g.,][]{IttiKoch01} and feature-based attention~\citep[e.g.,][]{MoheEtal14}.
-Our finding that people better remember attended stimuli also follows prior work on interactions between attention and memory~\citep{PallWagn02, ChunTurk07, AlyTurk16, AlyTurk17, WittEtal18, MorrEtal14, BaleEtal19}.
-Whereas much of this prior work focused on elucidating the neural basis of these interactions, our work extends these prior studies by elucidating the specific and separable behavioral impacts of feature-based attention (inhibition with a slow onset) and location-based attention (enhancement with a fast onset) on subsequent memory.
-Both of these effects persisted throughout the 2~min memory phases of both experiments.
-Therefore future work is needed to elucidate the longevity of these effects beyond 2 minutes.
+The notion that location-based attention operates at a faster timescale than
+feature-based attention is supported by prior work on the deployment of visual
+attention~\citep{SotoBlan04, StopEtal07}. Our findings that location-based
+attention enhances the processing of attended stimuli whereas feature-based
+attention suppresses the processing of unattended stimuli is also consistent
+with prior work on location-based attention~\citep[e.g.,][]{IttiKoch01} and
+feature-based attention~\citep[e.g.,][]{MoheEtal14}. Our finding that people
+better remember attended stimuli also follows prior work on interactions
+between attention and memory~\citep{PallWagn02, ChunTurk07, AlyTurk16,
+AlyTurk17, WittEtal18, MorrEtal14, BaleEtal19}. Whereas much of this prior work
+focused on elucidating the neural basis of these interactions, our work extends
+these prior studies by elucidating the specific and separable behavioral
+impacts of feature-based attention (inhibition with a slow onset) and
+location-based attention (enhancement with a fast onset) on subsequent memory.
+Both of these effects persisted throughout the 2~min memory phases of both
+experiments. Therefore future work is needed to elucidate the longevity of
+these effects beyond 2 minutes.
 
-Another important area for future study concerns how the flow of information between different brain structures is modulated according to the focus of volitional attention-- particularly with respect to pathways from primary sensory regions (e.g., V1, A1) to regions implicated in encoding ongoing experiences into memory (e.g, medial temporal lobe structures such as the hippocampus and entorhinal cortex, prefrontal cortex, etc.).
-For example, several studies suggest that attention serves to modulate the \textit{gain} of specific neural circuits~\citep{TreuTruj99, ChanEtal02, EldaEtal13, SaliThie00}, effectively facilitating or inhibiting the flow of specific neural representations~\citep{VartEtal07, LaRoEtal14}.
-Prior work suggests that feature-based attention may be supported by changes in connectivity with the thalamus~\citep{Schn11}, whereas location-based attention may be supported by changes in connectivity with primary visual cortex~\citep{NoudEtal10}.
-That feature-based and location-based attention are mediated by different brain structures may explain why these different aspects of attention operate on different timescales and affect memory differently.
-A strong test of this hypothesis would entail directly measuring neural activity patterns as people modulate their focus of attention (e.g., using functional magnetic resonance imaging or electroencephalography), and then using neural decoding approaches~\citep[e.g.,][]{HaxbEtal01, NormEtal06, MannEtal18} to follow how neural representations of attended (or unattended) stimuli are transfered from primary sensory regions, to higher order sensory regions, to memory areas.
-If the effects of attention on memory are mediated by changes in network dynamics, the transmission rates of the representations of attended stimuli from primary sensory regions to memory areas should be facilitated relative to the transmission rates of unattended stimuli.
-Further, variability in these neural changes (e.g., as a participant focuses their attention with more or less success) should track with behavioral measures of memorability.
+Another important area for future study concerns how the flow of information
+between different brain structures is modulated according to the focus of
+volitional attention-- particularly with respect to pathways from primary
+sensory regions (e.g., V1, A1) to regions implicated in encoding ongoing
+experiences into memory (e.g, medial temporal lobe structures such as the
+hippocampus and entorhinal cortex, prefrontal cortex, etc.). For example,
+several studies suggest that attention serves to modulate the \textit{gain} of
+specific neural circuits~\citep{TreuTruj99, ChanEtal02, EldaEtal13,
+SaliThie00}, effectively facilitating or inhibiting the flow of specific neural
+representations~\citep{VartEtal07, LaRoEtal14}. Prior work suggests that
+feature-based attention may be supported by changes in connectivity with the
+thalamus~\citep{Schn11}, whereas location-based attention may be supported by
+changes in connectivity with primary visual cortex~\citep{NoudEtal10}. That
+feature-based and location-based attention are mediated by different brain
+structures may explain why these different aspects of attention operate on
+different timescales and affect memory differently. A strong test of this
+hypothesis would entail directly measuring neural activity patterns as people
+modulate their focus of attention (e.g., using functional magnetic resonance
+imaging or electroencephalography), and then using neural decoding
+approaches~\citep[e.g.,][]{HaxbEtal01, NormEtal06, MannEtal18} to follow how
+neural representations of attended (or unattended) stimuli are transfered from
+primary sensory regions, to higher order sensory regions, to memory areas. If
+the effects of attention on memory are mediated by changes in network dynamics,
+the transmission rates of the representations of attended stimuli from primary
+sensory regions to memory areas should be facilitated relative to the
+transmission rates of unattended stimuli. Further, variability in these neural
+changes (e.g., as a participant focuses their attention with more or less
+success) should track with behavioral measures of memorability.
 
-Which aspects of our ongoing experiences we choose to attend affects how we process and remember those experiences later.
-Different forms of attention---e.g., to specific features or spatial locations---operate and affect memory at different timescales, and are likely mediated by different brain networks.
-Elucidating the behavioral and neural consequences of volitional changes in attention is central to discovering how our thoughts, feelings, goals, and situational understanding fluctuate from moment to moment.
+Which aspects of our ongoing experiences we choose to attend affects how we
+process and remember those experiences later. Different forms of
+attention---e.g., to specific features or spatial locations---operate and
+affect memory at different timescales, and are likely mediated by different
+brain networks. Elucidating the behavioral and neural consequences of
+volitional changes in attention is central to discovering how our thoughts,
+feelings, goals, and situational understanding fluctuate from moment to moment.
 
@@
 
-J.
-R.
-Manning and K.
-Ziman developed the concept for this study.
-Experiment code was written by K.
-Ziman and A.
-R.
-Martinez, and testing and data collection were conducted by M.
-R.
-Lee and K.
-Ziman.
-K.
-Ziman, M.
-R.
-Lee, and A.
-R.
-Martinez analyzed the data.
-All authors contributed to writing the manuscript and have approved the final version of the manuscript for submission.
+JRM and KZ developed the concept for this study. Experiment code was written by
+KZ and ARM, and testing and data collection were conducted by MRL and KZ. KZ,
+MRL, ARM, and JRM analyzed the data. JRM supervised the project. All authors
+contributed to writing and editing the manuscript.
+
+\section*{Data and code availability}
+
+All of the data analyzed in this manuscript, along with all of the code for
+running our experiment and carying out the analyses may be found at
+\url{http://www.github.com/ContextLab/attention-memory-task}.
 
@@
 
-This work was supported in part by NSF EPSCoR award number 1632738.
-The content of this manuscript is solely the responsibility of the authors and does not necessarily represent the official views of our supporting organizations.
-We are grateful for useful discussions with the EPSCoR Attention Consortium, particularly with Marian Berryhill, Gideon Caplovitz, Patrick Cavanagh, Theresa Desrochers, and Peter Tse.
-We thank Megan deBettencourt for useful discussions, pointers to our experimental stimuli, and for providing code to facilitate stimulus preparation.
-We also appreciate useful discussions with Paxton Fitzpatrick, Kevin Hartstein, Talia Manning, Lucy Owen, and Michael Ziman.
-Finally, we thank Christina Liu and Eowyn Pak for their help running pilot versions of the experiments reported here.
-
-\section*{Open practices statement}
-Neither of the experiments reported in this article were pre-registered.
-However, we replicated both experiments in the study after collecting our initial datasets.
-We report analysis of the combined datasets in our manuscript (Sustained Attention Experiment: n = 60; Variable Attention Experiment: n = 53), and analysis of each replication group, independently, in the \textit{Supporting Materials} (Sustained Attention Experiment, Group 1: n = 30; Sustained Attention Experiment, Group 2: n = 30; Variable Attention Experiment, Group 1: n = 30; Variable Attention Experiment, Group 2: n = 23).
-All of our experimental materials, data, and analysis code may be downloaded from \url{http://www.github.com/ContextLab/attention-memory-task}.
+This work was supported in part by NSF EPSCoR Award Number 1632738 to JRM and
+by by NSF CAREER Award Number 2145172 to JRM. The content of this manuscript is
+solely the responsibility of the authors and does not necessarily represent the
+official views of our supporting organizations. We are grateful for useful
+discussions with the EPSCoR Attention Consortium, particularly with Marian
+Berryhill, Gideon Caplovitz, Patrick Cavanagh, Theresa Desrochers, and Peter
+Tse. We thank Megan deBettencourt for useful discussions, pointers to our
+experimental stimuli, and for providing code to facilitate stimulus
+preparation. We also appreciate useful discussions with Paxton Fitzpatrick,
+Kevin Hartstein, Talia Manning, Lucy Owen, and Michael Ziman. Finally, we thank
+Christina Liu and Eowyn Pak for their help running pilot versions of the
+experiments reported here.
 
 \bibliographystyle{apacite}
-\bibliography{CDL-bibliography/memlab}
+\bibliography{./CDL-bibliography/memlab}
 

### 2023-03-25 paper/main.tex
working on results section

@@
 
-\newcommand{\familiarity}{S1}
-\newcommand{\fixation}{S2}
-\newcommand{\timecourseCuedCategory}{S3}
-\newcommand{\timecourseUncuedCategory}{S4}
-\newcommand{\timecourseCuedLocation}{S5}
-\newcommand{\timecourseUncuedLocation}{S6}
-\newcommand{\timecourseNovel}{S7}
-\newcommand{\timecourseDiff}{S8}
+\newcommand{\gazeLocations}{S1}
+\newcommand{\excludedTrials}{S2}
+\newcommand{\ratingsByCategory}{S3}
 
@@
 
+We used the eyetracking data to home in specifically on behavioral effects
+related to \textit{covert} attention, as opposed to overt looking effects.
+Specifically, we excluded from further analysis any images from trials where
+participants shifted their gaze (for any non-zero amount of time) to any part
+of the attended composite image during a presentation trial
+(see Figs.~\gazeLocations,~and \excludedTrials).
+
 \subsection*{Experimental paradigm}
@@
 
-\textbf{JRM STOPPED HERE}
-
 \section*{Results}
 
-We ran two volitional covert attention experiments; in the Sustained Attention
-Experiment we asked participants to \textit{sustain} the focus of their
-attention over a succession of 10 stimulus presentations per block whereas in
-the Variable Attention Experiment we asked participants to \textit{vary} their
-focus of attention with each new stimulus (also for a total of 10 stimulus
-presentations per block). Each stimulus comprised a pair of composite images
-(one on the left and one on the right side of the display), where each
-composite comprised an equal blend of a unique face and a unique place image.
-We followed the presentation phases of each experimental block with a memory
-phase, where participants performed a recognition memory task by rating the
-familiarity of previously experienced and novel face and place images (see
-\textit{Materials and methods}, Fig.~\ref{fig:paradigm}).
+We ran a volitional covert attention experiment with two conditions; in the
+sustained attention condition we asked participants to \textit{sustain} the
+focus of their attention over a succession of 10 stimulus presentations per
+block whereas in the variable attention condition we asked participants to
+\textit{vary} their focus of attention with each new stimulus (also for a total
+of 10 stimulus presentations per block). Each stimulus comprised a pair of
+composite images (one on the left and one on the right side of the display),
+where each composite comprised an equal blend of a unique face and a unique
+place image. We followed the presentation phases of each experimental block
+with a memory phase, where participants performed a recognition memory task by
+rating the familiarity of previously experienced and novel face and place
+images (see \textit{Experimental paradigm}, Fig.~\ref{fig:paradigm}).
 
-We considered each image we probed in the memory phase with respect to whether
-(and how) the participant had experienced and/or attended to that image during
-the presentation phase (Fig.~\ref{fig:familiarity}). For example, if a given
-face image had been presented as part of the composite image on the right of
-the screen following an \texttt{attend to the face on the right} instruction,
-then that face image would have been the focus of the participant's attention
-during one stimulus presentation. The face image on the left (unattended side)
-during that trial would have been captured by feature-based attention, but not
-by location-based attention; and the place image (unattended category) on the
-right during that trial would have been captured by location-based attention,
-but not by feature-based attention. The place image on the left during that
-trial remained outside of the focus of both feature-based and location-based
-attention. In this way, we categorized each of the images that participants
-experienced during the presentation phases of each experiment in terms of
-whether they fell under the scope of feature-based and/or location-based
-attention. We also categorized novel face and place images that we asked
-participants to judge during the memory phase (i.e., images that the
-participant hadn't seen before) as belonging to the attention-cued or uncued
-category. These novel images were intended to serve as a baseline for
-comparison. For example, we sought to measure how people rated the familiarity
-of new images in general. We also used differences in familiarity ratings
-between novel images of the attention-cued versus uncued categories to evaluate
-potential \textit{prospective} affects of modulating the focus of feature-based
-attention.
+We first wondered whether (and how) shifts in covert attention might affect
+participants' ratings during the recognition memory task
+(Fig.~\ref{fig:familiarity}). To ensure that our findings were not conflated
+with where people were physically looking, we excluded from further analysis
+any images presented during trials where the participant's gaze touched on any
+part of the attended composite image (see \textit{Eyetraciking},
+Figs.~\gazeLocations~and \excludedTrials). For the remaining trials, the
+participants kept their gaze focused on a fixation cross at the center of the
+screen while \textit{covertly} shifting the focus of their attention to the
+cued category component of the composite image on the cued location. In other
+words, during these remaining trials, participants' physical (external)
+experiences of the face and place components of every presented composite image
+remained relatively constant across trials (up to our ability to accurately
+measure where participants were looking using the eyetracker).
+
+Simply by encoding their prior experiences into memory, we reasoned that
+participants should rate \textit{any} presented images as more familiar than
+novel images, regardless of whether they were following the attention cues. We
+confirmed that this prediction held in both the sustained ($t(29) = 8.856, p <
+0.001$) and variable ($t(22) = 5.144, p < 0.001$) conditions. In addition, to
+the extent that participants were following the attention cues, there
+\textit{internal} experiences of each image should depend on their internal
+focus of attention during each image presentation. For example, we expected
+that the attended-category component of the composite image at the attended
+location might be better recognized than the other composite image components.
+Indeed, participants in both experimental conditions rated these ``fully
+attended'' images as more familiar than category-matched image components from
+unattended locations (sustained: $t(29) = 6.893, p < 0.001$; variable: $t(22) =
+6.938, p < 0.001$), location-matched images from the unattended category
+(sustained: $t(29) = 6.710, p < 0.001$; variable: $t(22) = 7.633, p < 0.001$),
+unattended images that were neither from the attended category nor the attended
+location (sustained: $t(29) = 8.470, p < 0.001$; variable: $t(22) = 7.256, p <
+0.001$), or novel images they had never seen before (sustained: $t(29) =
+10.259, p < 0.001$; variable: $t(22) = 7.874, p < 0.001$). We also observed a
+``boost'' in familiarity over novel images for attended \textit{or} unattended
+images from the cued category (sustained: $t(29) = 10.578, p < 0.001$;
+variable: $t(22) = 7.354, p < 0.001$) and location (sustained: $t(29) = 8.917,
+p < 0.001$; variable: $t(22) = 5.726, p < 0.001$).
+
+We also wondered whether the ways participants attended to or remembered the
+images might depend on image-specific properties like the images' categories.
+We repeated the analyis displayed in Figure~\ref{fig:familiarity} separately
+for face and place images (Fig.~\ratingsByCategory). The same general patterns
+held for each category, as when we combined across the two stimulus categories
+as reported above. For example, fully attended face and place images were both
+rated as more familiar than the category-matched images from the unattended
+location (sustained: $t$s$(29) \geq 3.36, p$s$ \leq 0.002$; variable: $t$s$(22)
+\geq 6.205, p$s$ \leq 0.001$), attended-location images from the unattended
+category (sustained: $t$s$(29) \geq 5.886, p$s$ \leq 0.001$; variable:
+$t$s$(29) \geq 4.277, p$s$ \leq 0.001$), images from the unattended category
+and location (sustained: $t$s$(29) \geq 6.628, p$s$ \leq 0.001$; variable:
+$t$s$(29) \geq 5.624, p$s$ \leq 0.001$), and novel images (sustained: $t$s$(29)
+\geq 5.987, p$s$ \leq 0.001$; variable: $t$s$(29) \geq 5.132, p$s$ \leq
+0.001$). Taken together, the above results suggest that what we remember is
+guided in part by what we attended to, even after accounting for where we look
+or what specifically we are looking at.
+
+Splitting participants' responses to face versus place images also revealted
+that participants often rated attended (and partially attended) place images as
+more familiar than attention-matched face images (compare dark versus light
+bars in Fig.~\ratingsByCategory). We hypothesized that this might be
+explainable by some property of the relevant cognitive processes or by
+properties of the stimuli themselves. To help elucidate this distinction, we
+examined individual exemplars of the face and place images used in our paradigm
+(Fig.~\ref{fig:stimuli}A). By design, the face images had consistent head
+sizes, viewing angles, expressions, and so on. In contrast, the place images
+varied more substantially across images. For example, some place images
+depicted human-made structures; others depicted natural scenes; some depicted
+indoor views; others depicted outdoor views; etc. This can also be seen by
+averaging the pixel intensity values across images, separately for the face and
+place stimuli (Fig.~\ref{fig:stimuli}B). Whereas the average face image retains
+many of the landmarks characteristic of most faces (e.g., clearly defined hair,
+eyes, nose, mouth, head shape, etc.), the average place image does not show
+place-specific features as clearly, aside from a general tendancy for the tops
+of place images to be lighter than the bottoms of place images. We also
+computed the pairwise similarities across images from each stimulus category
+(Fig.~\ref{fig:stimuli}C) and found that face images tended to be much more
+similar to each other than place images (Fig.~\ref{fig:stimuli}D; $t(115258) =
+254.764, p < 0.001$). This analysis indicated to us that our experimental
+paradigm was not well-suited to identifying cognitively meaningful stimulus
+category differences, since participants' category-specific judgements may be
+confounded with within-category image similarity differences.
 
@@
 	\centering
-  \includegraphics[width=0.75\textwidth]{figures/familiarity}
+	\includegraphics[width=\textwidth]{figs/stimuli}
 
-  \caption{\textbf{Familiarity ratings for attended, unattended, and novel
-  stimuli.} Each split violin plot displays the distribution of
-  within-participant average familiarity ratings given to faces (left, darker
-  colors) and scenes (right, lighter colors) during the memory phases of each
-  experiment. As shown in the legend (bottom), the colors indicate whether each
-  image had been viewed during the presentation phase (\texttt{old}) or not;
-  whether the given images matched the \texttt{attended category}; and/or
-  whether the given images matched the \texttt{attended location}. The colored
-  lines above each set of violin plots denote statistical differences
-  (\textbf{pos}itive or \textbf{neg}ative differences in mean, collapsing over
-  image category, assessed via two-tailed $t$-tests) between the distributions
-  centered on the endpoints of each line. The line thicknesses denote
-  $p$-values as indicated in the legend. Asterisks denote differences between
-  the face versus scene distributions (assessed via two-tailed $t$-tests).
-  Panel \textbf{a.} displays results from the Sustained Attention Experiment
-  and panel \textbf{b.} displays results from the Variable Attention
-  Experiment. Figure~\familiarity~displays these results broken down by
-  participant cohort.}
+  \caption{\textbf{Stimulus examples and properties.} \textbf{A. Example images
+  from each stimulus category.} Randomly chosen subsets of 20 face images
+  (left) and 20 place images (right) are displayed. \textbf{B. Across-image
+  averages.} Each panel displays the average image, taken across all 360 face
+  images (left) and 360 place images (right). \textbf{C. Pairwise
+  correlations.} Each row and column of the matrices displays the correlation
+  (across pixels) in intensity values for one pair of face images (left) or
+  place images (right). \textbf{D. Average pairwise correlations.} The bar
+  heights denote the average pairwise correlations between face and place
+  images. Error bars denote across-pair bootstrap-estimated 95\%
+  confidence intervals.}
 
-\label{fig:familiarity}
+  \label{fig:stimuli}
   \end{figure*}
 
-Participants in both experiments rated stimuli they attended as more familiar
-than unattended or novel stimuli (Fig.~\ref{fig:familiarity}; Sustained
-Attention Experiment: $t(59) = 13.42, p = 1.39 \times 10^{-19}, d = 1.73$;
-Variable Attention Experiment: $t(52) = 12.40, p = 3.70 \times 10^{-17}, d =
-1.70$). Participants in both experiments also rated attended scene stimuli as
-more familiar than attended face stimuli (Sustained Attention Experiment:
-$t(59) = 7.69, p = 1.85 \times 10^{-10}, d = 0.99$; Variable Attention
-Experiment: $t(52) = 7.08, p = 3.63 \times 10^{-9}, d = 0.97$). These findings
-indicate that aspects of experience that are captured by the focus of attention
-are easier to recognize later, and that attention may preferentially benefit
-memory for some aspects of experience to a greater extent than other aspects of
-experience.
+Next, we turned to identifying potential differences in participants' behaviors
+across the two experimental conditions. The main difference between the
+conditions' procedures was in how long participants were asked to maintain the
+same focus of category-based and location-based attention, across successive
+image presentations. Therefore, differences in participants' behaviors across
+the two conditions might reflect differences in the timescales of the relevant
+cognitive processes. We compared participants' familiarity ratings for images
+at each attention level across the two conditions. We saw no evidence that
+people rated fully attended images ($t(51) = -0.649, p = 0.519$),
+attended-category (but not location) images ($t(51) = 1.163, p = 0.250$),
+unattended category and location images ($t(51) = -1.600, p = 0.116$), or novel
+images ($t(51) = -0.435, p = 0.665$) differently across the two conditions.
+However, participants in the variable attention condition rated
+attended-location (but unattended category) images as more familiar than
+participants in the sustained attention condition ($t(51) = 2.174, p = 0.034$).
+This suggests that the timescales over which location-based versus
+category-based attention tend to operate may differ.
 
-Participants in the Sustained Attention Experiment experiment also rated
-unattended images that matched the attended category as more familiar than
-unattended images that did not match the attended category (\textit{incidental
-feature-based attention}; $t(59) = 7.17, p = 1.40 \times 10^{-9}, d = 0.93$).
-This pattern did not hold for participants in the Variable Attention Experiment
-($t(52) = 0.44, p = 0.66, d = 0.06$). Participants in both experiments
-displayed an incidental effect of location-based attention, whereby they rated
-unattended-category images at the attended location as more familiar than
-unattended-category images at the unattended location (Sustained Attention
-Experiment: $t(59) = 4.32, p = 6.05 \times 10^{-5}, d = 0.56$; Variable
-Attention Experiment: $t(52) = 2.57, p = 0.01, d = 0.35$). This indicates that
-aspects of our experience that incidentally overlap with the focus of our
-location-based attention are easier to recognize later, even if those aspects
-do not fall within the intentional focus of our feature-based attention.
+\textbf{JRM STOPPED HERE}
 
-We defined the \textit{memory benefit of feature-based attention} as the
-difference in mean familiarity ratings of attended stimuli and unattended
-stimuli from the attended category versus the mean familiarity ratings of
-unattended stimuli from the unattended category. Similarly, we defined the
-\textit{memory benefit of location-based attention} as the difference in mean
-familiarity ratings of attended stimuli and unattended stimuli from the
-attended location versus the mean familiarity ratings of unattended stimuli
-from the unattended location. Participants in the Sustained Attention
-Experiment displayed a larger memory benefit of feature-based attention than
-location-based attention ($t(59) = 3.25, p = 1.91 \times 10^{-3}, d = 0.42$),
-whereas participants in the Variable Attention Experiment displayed a larger
-memory benefit of location-based attention ($t(52) = 1.70, p = 9.99 \times
-10^{-2}, d = 0.23$). This appeared to be driven in part by a response bias
-towards attended-category images. For example, relative to the most recent
-attention cue, participants in the Sustained Attention Experiment rated
-attended-category novel images as more familiar than unattended-category novel
-images ($t(59) = 7.04, p = 2.35 \times 10^{-9}, d = 0.91$), whereas
-participants in the Variable Attention Experiment responded similarly to
-attended-category and unattended-category novel images ($t(52) = 0.23, p =
-0.82, d = 0.03$). The size of this attended-category response bias for novel
-images was reliably smaller than the memory benefits of feature-based attention
-in both experiments (Sustained Attention Experiment: $t(59) = 7.59, p = 2.68
-\times 10^{-10}, d = 0.98$; Variable Attention Experiment: $t(52) = 6.74, p =
-1.31 \times 10^{-8}, d = 0.93$). This indicates that tuning the focus of
-feature-based attention with respect to how ongoing experience is encoded in
-memory takes longer than the duration of a single stimulus presentation
-(including fixation, roughly 5.5~s). Further, once feature-based attention
-comes ``online,'' it affects how \textit{new} stimuli are processed.
+% We considered each image we probed in the memory phase with respect to whether
+% (and how) the participant had experienced and/or attended to that image during
+% the presentation phase (Fig.~\ref{fig:familiarity}). For example, if a given
+% face image had been presented as part of the composite image on the right of
+% the screen following an \texttt{attend to the face on the right} instruction,
+% then that face image would have been the focus of the participant's attention
+% during one stimulus presentation. The face image on the left (unattended side)
+% during that trial would have been captured by feature-based attention, but not
+% by location-based attention; and the place image (unattended category) on the
+% right during that trial would have been captured by location-based attention,
+% but not by feature-based attention. The place image on the left during that
+% trial remained outside of the focus of both feature-based and location-based
+% attention. In this way, we categorized each of the images that participants
+% experienced during the presentation phases of each experiment in terms of
+% whether they fell under the scope of feature-based and/or location-based
+% attention. We also categorized novel face and place images that we asked
+% participants to judge during the memory phase (i.e., images that the
+% participant hadn't seen before) as belonging to the attention-cued or uncued
+% category. These novel images were intended to serve as a baseline for
+% comparison. For example, we sought to measure how people rated the familiarity
+% of new images in general. We also used differences in familiarity ratings
+% between novel images of the attention-cued versus uncued categories to evaluate
+% potential \textit{prospective} affects of modulating the focus of feature-based
+% attention.
 
-We also compared the relative sizes of the memory benefits of feature-based
-attention and location-based attention across the two experiments. Participants
-in the Sustained Attention Experiment displayed a larger difference between
-these two effects than did participants in the Variable Attention Experiment
-($t(111) = 3.48, p = 7.24 \times 10^{-4}, d = 0.66$). Further, the difference
-in mean familiarity ratings of attended-location images versus unattended
-images was greater for participants in the Variable Attention Experiment
-($t(111) = 2.32, p = 0.02, d = 0.44$). The memory benefit of location-based
-attention reliably distinguished between attended-category versus unattended
-category images for participants in both experiments (Sustained Attention
-Experiment: $t(59) = 9.50, p = 1.68 \times 10^{-13}, d = 1.23$; Variable
-Attention Experiment: $t(52) = 9.72, p = 2.76 \times 10^{-13}, d = 1.33$). This
-indicates that tuning the focus of location-based attention with respect to how
-ongoing experience is encoded into memory occurs faster than the duration of a
-single stimulus presentation.
+% \begin{figure*}[tp]
+%   \centering
+%   \includegraphics[width=0.75\textwidth]{figs/familiarity_by_attention_level}
 
-We also compared reaction times to probes from the attended versus unattended
-side. Participants in both experiments responded slightly faster on average to
-attended-side probes, although the differences did not reach significance
-(Sustained Attention Experiment: $t(59) = 1.03, p = 0.31, d = 0.13$; Variable
-Attention Experiment: $t(52) = 0.65, p = 0.52, d = 0.09$). Participants in the
-Sustained Attention Experiment displayed a slightly larger (and not
-statistically significant) difference in attended-side versus unattended-side
-reaction times than participants in the Variable Attention Experiment ($t(111)
-= .87, p = 0.38, d = 0.20$). Because none of these reaction time effects were
-statistically reliable, we are unable to draw meaningful conclusions about
-reaction times to the attention probes on the attended versus unattended side,
-nor are we able to draw meaningful conclusions about differences in those
-reaction times that might be due to sustained versus variable attention.
+%   \caption{\textbf{Familiarity ratings for attended, unattended, and novel
+%   stimuli.} The bars display the average familiarity ratings participants gave
+%   to images from the same category and location as the attention cue (full
+%   attention), the same category (but opposite location) as the attention cue
+%   (attended category), the same location (but opposite category) as the
+%   attention cue (attended location), the opposite category and location as the
+%   attention cue (unattended), or novel images. The left panel displays
+%   familiarity ratings from the sustained attention condition and the right
+%   panel displays familiarity ratings from the variable attention condition. All
+%   error bars denote across-participant bootstrap-estimated 95\% confidence
+%   intervals. See Figure~\ratingsByCategory~for analogous results broken down by
+%   stimulus category.}
 
-\begin{figure}[tp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/exps1_2_xgaze.pdf}
+% \label{fig:familiarity}
+% \end{figure*}
 
-  \caption{\textbf{Horizontal coordinates of visual fixations.} Each violin
-  plot displays a distribution of participant-wise average horizontal gaze
-  positions relative to a presented image. The coordinates have been normalized
-  such that a value of 1.0 denotes the furthest onscreen coordinate from the
-  central fixation point \textit{towards} the direction of the given image, and
-  -1.0 denotes the furthest onscreen coordinate from the central fixation point
-  \textit{away from} the direction of the given image. The gray bars in each
-  panel mark the boundaries of the presented images. The violin plots are
-  broken down by participants' familiarity ratings during the memory phases of
-  each experiment, and by each image's relation to the attention cue while that
-  image appeared onscreen. Panel \textbf{a.} displays fixation data for the
-  Sustained Attention Experiment and Panel \textbf{b.} displays fixation data
-  for the Variable Attention Experiment. Figure~\fixation~displays these
-  results broken down by participant cohort.}
+% Participants in both experiments rated stimuli they attended as more familiar
+% than unattended or novel stimuli (Fig.~\ref{fig:familiarity}; Sustained
+% Attention Experiment: $t(59) = 13.42, p = 1.39 \times 10^{-19}, d = 1.73$;
+% Variable Attention Experiment: $t(52) = 12.40, p = 3.70 \times 10^{-17}, d =
+% 1.70$). Participants in both experiments also rated attended scene stimuli as
+% more familiar than attended face stimuli (Sustained Attention Experiment:
+% $t(59) = 7.69, p = 1.85 \times 10^{-10}, d = 0.99$; Variable Attention
+% Experiment: $t(52) = 7.08, p = 3.63 \times 10^{-9}, d = 0.97$). These findings
+% indicate that aspects of experience that are captured by the focus of attention
+% are easier to recognize later, and that attention may preferentially benefit
+% memory for some aspects of experience to a greater extent than other aspects of
+% experience.
 
-\label{fig:fixation}
-\end{figure}
+% Participants in the Sustained Attention Experiment experiment also rated
+% unattended images that matched the attended category as more familiar than
+% unattended images that did not match the attended category (\textit{incidental
+% feature-based attention}; $t(59) = 7.17, p = 1.40 \times 10^{-9}, d = 0.93$).
+% This pattern did not hold for participants in the Variable Attention Experiment
+% ($t(52) = 0.44, p = 0.66, d = 0.06$). Participants in both experiments
+% displayed an incidental effect of location-based attention, whereby they rated
+% unattended-category images at the attended location as more familiar than
+% unattended-category images at the unattended location (Sustained Attention
+% Experiment: $t(59) = 4.32, p = 6.05 \times 10^{-5}, d = 0.56$; Variable
+% Attention Experiment: $t(52) = 2.57, p = 0.01, d = 0.35$). This indicates that
+% aspects of our experience that incidentally overlap with the focus of our
+% location-based attention are easier to recognize later, even if those aspects
+% do not fall within the intentional focus of our feature-based attention.
 
-Given that participants in both experiments rated attended-location images from
-both the attended and unattended category as more familiar than
-unattended-location images, we wondered whether this was truly a consequence of
-covert attention, or whether it might be driven solely by where participants
-were looking. In other words, we sought to distinguish the memory effects of
-the focus of covert attention from the focus of visual gaze. We used
-eyetracking to measure the horizontal positions of the participants' visual
-fixations while each pair of composite stimuli appeared onscreen
-(Fig.~\ref{fig:fixation}). For 94\% of presentation trials (Sustained Attention
-Task: $\frac{4531}{4800}$ trials; Variable Attention Task: $\frac{3972}{4240}$
-trials), we collected viable gaze data for analysis. In the remaining trials,
-participant movement or other technical issues corrupted the gaze data. We
-found that, though they generally followed our instruction to keep their gaze
-fixed on the center of the screen, participants in both experiments exhibited a
-slight tendency to look towards the side of the screen they were attending to
-(Sustained Attention Task: $t(59) = 3.61, p = 6.31 \times 10^{-4}$; Variable
-Attention Task: $t(52) = 2.86, p = 6.06 \times 10^{-3}$). When we limited our
-analyses to trials with viable gaze data where participants successfully
-maintained fixation on the center of the screen within 4.28$^\circ$ visual
-angle (i.e., between the rightmost boundary of the left image and the leftmost
-boundary of the right image) we observed (numerical) memory benefits of
-feature-based attention in both experiments (Sustained Attention Experiment:
-$t(59) = 4.73, p = 1.96 \times 10^{-5}, d = 0.67$; Variable Attention
-Experiment: $t(52) = 0.64, p = 0.52, d = 0.09$) and location-based attention in
-the Sustained Attention Experiment, but not the Variable Attention Experiment
-(Sustained Attention Experiment: $t(59) = 0.67, p = 0.51, d = 0.09$; Variable
-Attention Experiment: $t(52) = -0.79, p = 0.43, d = 0.11$). These analyses
-indicate that although the focus of covert attention can affect where people
-are looking, covert attention affects memory encoding beyond what may be
-accounted for by gaze position alone.
+% We defined the \textit{memory benefit of feature-based attention} as the
+% difference in mean familiarity ratings of attended stimuli and unattended
+% stimuli from the attended category versus the mean familiarity ratings of
+% unattended stimuli from the unattended category. Similarly, we defined the
+% \textit{memory benefit of location-based attention} as the difference in mean
+% familiarity ratings of attended stimuli and unattended stimuli from the
+% attended location versus the mean familiarity ratings of unattended stimuli
+% from the unattended location. Participants in the Sustained Attention
+% Experiment displayed a larger memory benefit of feature-based attention than
+% location-based attention ($t(59) = 3.25, p = 1.91 \times 10^{-3}, d = 0.42$),
+% whereas participants in the Variable Attention Experiment displayed a larger
+% memory benefit of location-based attention ($t(52) = 1.70, p = 9.99 \times
+% 10^{-2}, d = 0.23$). This appeared to be driven in part by a response bias
+% towards attended-category images. For example, relative to the most recent
+% attention cue, participants in the Sustained Attention Experiment rated
+% attended-category novel images as more familiar than unattended-category novel
+% images ($t(59) = 7.04, p = 2.35 \times 10^{-9}, d = 0.91$), whereas
+% participants in the Variable Attention Experiment responded similarly to
+% attended-category and unattended-category novel images ($t(52) = 0.23, p =
+% 0.82, d = 0.03$). The size of this attended-category response bias for novel
+% images was reliably smaller than the memory benefits of feature-based attention
+% in both experiments (Sustained Attention Experiment: $t(59) = 7.59, p = 2.68
+% \times 10^{-10}, d = 0.98$; Variable Attention Experiment: $t(52) = 6.74, p =
+% 1.31 \times 10^{-8}, d = 0.93$). This indicates that tuning the focus of
+% feature-based attention with respect to how ongoing experience is encoded in
+% memory takes longer than the duration of a single stimulus presentation
+% (including fixation, roughly 5.5~s). Further, once feature-based attention
+% comes ``online,'' it affects how \textit{new} stimuli are processed.
 
-The preceding results indicate that volitional covert attention affects memory,
-and that feature-based and location-based covert attention may come online at
-different timescales. We next sought to examine how long the memory effects of
-feature-based and location-based covert attention persist. To gain additional
-insights into the timecourse of the impact of feature-based and location-based
-attention on memory, we used a sliding window analysis to measure how
-participants' familiarity ratings of attended, partially attended, unattended,
-and novel stimuli varied over the duration of the memory phases of both
-experiments. During each block within the memory phases of each experiment,
-participants made familiarity judgements about a total of 40 images (20 old
-images and 20 novel images). We computed average familiarity ratings for images
-appearing in each position of the memory stimulus sequence (positions 1--40),
-as a function of how (or whether) they were attended during the preceding
-presentation phase (old images) or whether they matched the category of the
-most recent attention cue (novel images), for overlapping 20-image sliding
-windows (Figs.~\ref{fig:familiarity_timecourse_category},
-\ref{fig:familiarity_timecourse_location}, and
-\ref{fig:familiarity_timecourse_novel}). We first calculated these values for
-each participant, and then we averaged across participants.
+% We also compared the relative sizes of the memory benefits of feature-based
+% attention and location-based attention across the two experiments. Participants
+% in the Sustained Attention Experiment displayed a larger difference between
+% these two effects than did participants in the Variable Attention Experiment
+% ($t(111) = 3.48, p = 7.24 \times 10^{-4}, d = 0.66$). Further, the difference
+% in mean familiarity ratings of attended-location images versus unattended
+% images was greater for participants in the Variable Attention Experiment
+% ($t(111) = 2.32, p = 0.02, d = 0.44$). The memory benefit of location-based
+% attention reliably distinguished between attended-category versus unattended
+% category images for participants in both experiments (Sustained Attention
+% Experiment: $t(59) = 9.50, p = 1.68 \times 10^{-13}, d = 1.23$; Variable
+% Attention Experiment: $t(52) = 9.72, p = 2.76 \times 10^{-13}, d = 1.33$). This
+% indicates that tuning the focus of location-based attention with respect to how
+% ongoing experience is encoded into memory occurs faster than the duration of a
+% single stimulus presentation.
 
-\begin{figure*}[tp]
-  \centering
-  \includegraphics[width=1\textwidth]{figures/Cat_Cued_TimeSeries.pdf}
+% We also compared reaction times to probes from the attended versus unattended
+% side. Participants in both experiments responded slightly faster on average to
+% attended-side probes, although the differences did not reach significance
+% (Sustained Attention Experiment: $t(59) = 1.03, p = 0.31, d = 0.13$; Variable
+% Attention Experiment: $t(52) = 0.65, p = 0.52, d = 0.09$). Participants in the
+% Sustained Attention Experiment displayed a slightly larger (and not
+% statistically significant) difference in attended-side versus unattended-side
+% reaction times than participants in the Variable Attention Experiment ($t(111)
+% = .87, p = 0.38, d = 0.20$). Because none of these reaction time effects were
+% statistically reliable, we are unable to draw meaningful conclusions about
+% reaction times to the attention probes on the attended versus unattended side,
+% nor are we able to draw meaningful conclusions about differences in those
+% reaction times that might be due to sustained versus variable attention.
 
-  \caption{\textbf{Familiarity ratings over time for images that matched the
-  cued or uncued image category.} Each curve reflects the average familiarity
-  ratings for attended, unattended, and novel images (denoted in the legends on
-  the right) within a succession of overlapping 20-image sliding windows. Error
-  ribbons denote 95\% confidence intervals, computed across participants.
-  Panels \textbf{a.} and \textbf{c.} display results from the Sustained
-  Attention Experiment and Panels \textbf{b.} and \textbf{d.} display results
-  from the Variable Attention Experiment. The paired horizontal lines at the
-  bottom of each panel denote timepoints when the given pair of curves was
-  statistically distinguishable (i.e., the topmost line color was statistically
-  greater than the bottommost line color at $\alpha = 0.05$, via a paired
-  two-tailed $t$-test.) The gray lines in Panels b and d reflect familiarity
-  ratings of novel stimuli from both the most recently attended and unattended
-  image categories. Figures~\timecourseCuedCategory~and
-  \timecourseUncuedCategory~display these results broken down by participant
-  cohort.}
+% \begin{figure}[tp]
+%   \centering
+%   \includegraphics[width=\textwidth]{figures/exps1_2_xgaze.pdf}
 
-\label{fig:familiarity_timecourse_category}
-\end{figure*}
+%   \caption{\textbf{Horizontal coordinates of visual fixations.} Each violin
+%   plot displays a distribution of participant-wise average horizontal gaze
+%   positions relative to a presented image. The coordinates have been normalized
+%   such that a value of 1.0 denotes the furthest onscreen coordinate from the
+%   central fixation point \textit{towards} the direction of the given image, and
+%   -1.0 denotes the furthest onscreen coordinate from the central fixation point
+%   \textit{away from} the direction of the given image. The gray bars in each
+%   panel mark the boundaries of the presented images. The violin plots are
+%   broken down by participants' familiarity ratings during the memory phases of
+%   each experiment, and by each image's relation to the attention cue while that
+%   image appeared onscreen. Panel \textbf{a.} displays fixation data for the
+%   Sustained Attention Experiment and Panel \textbf{b.} displays fixation data
+%   for the Variable Attention Experiment. Figure~\fixation~displays these
+%   results broken down by participant cohort.}
 
-Throughout the memory phase, participants from both experiments rated attended
-images as more familiar than category-matched unattended and novel images
-(Fig.~\ref{fig:familiarity_timecourse_category}, top row). This indicates that
-the memory benefits of attending to specific stimulus features (versus
-category-general features) persist for at least as long as the duration of the
-memory phase (2~min). Early in the memory phase, participants in the Variable
-Attention Experiment also rated category-matched unattended images as more
-familiar than novel images. This pattern did not hold for participants in the
-Sustained Attention Experiment. The short-lived boost in familiarity for
-attended-category images at the unattended location following variable (but not
-sustained) attention suggests that the timecourse of feature-based attention's
-impact on memory depends on how long the focus of feature-based attention has
-been held.
+% \label{fig:fixation}
+% \end{figure}
 
-Participants in both experiments also rated unattended-category images at the
-attended location as more familiar than unattended-category images at the
-unattended location and novel unattended-category images
-(Fig.~\ref{fig:familiarity_timecourse_category}, bottom row). This pattern
-persisted throughout the memory phases of both experiments. This supports the
-notion that location-based attention enhances memory in a (partially)
-feature-independent way. Participants in the Variable Attention Experiment also
-rated unattended-category images at the unattended location as (numerically)
-more familiar than novel images (though this pattern was only statistically
-reliable towards the middle of the memory phase). This pattern did not hold for
-participants in the Sustained Attention Experiment. Participants in the
-Sustained Attention Experiment rated unattended-category images (regardless of
-location or novelty status) as less familiar than participants in the Variable
-Attention Experiment (e.g., compare heights of the lines in the bottom left
-versus bottom right panels of Fig.~\ref{fig:familiarity_timecourse_category}).
-This suggests that, after sustained feature-based attention to a particular
-image category, the encodings of stimuli from the unattended category are
-suppressed. This suppression effect appears to persist at least as long as the
-memory phase of the experiment (2~min). Further, the magnitude of this
-suppression effect appears to become stronger following longer-term sustained
-(versus shorter-term variable) feature-based attention.
+% Given that participants in both experiments rated attended-location images from
+% both the attended and unattended category as more familiar than
+% unattended-location images, we wondered whether this was truly a consequence of
+% covert attention, or whether it might be driven solely by where participants
+% were looking. In other words, we sought to distinguish the memory effects of
+% the focus of covert attention from the focus of visual gaze. We used
+% eyetracking to measure the horizontal positions of the participants' visual
+% fixations while each pair of composite stimuli appeared onscreen
+% (Fig.~\ref{fig:fixation}). For 94\% of presentation trials (Sustained Attention
+% Task: $\frac{4531}{4800}$ trials; Variable Attention Task: $\frac{3972}{4240}$
+% trials), we collected viable gaze data for analysis. In the remaining trials,
+% participant movement or other technical issues corrupted the gaze data. We
+% found that, though they generally followed our instruction to keep their gaze
+% fixed on the center of the screen, participants in both experiments exhibited a
+% slight tendency to look towards the side of the screen they were attending to
+% (Sustained Attention Task: $t(59) = 3.61, p = 6.31 \times 10^{-4}$; Variable
+% Attention Task: $t(52) = 2.86, p = 6.06 \times 10^{-3}$). When we limited our
+% analyses to trials with viable gaze data where participants successfully
+% maintained fixation on the center of the screen within 4.28$^\circ$ visual
+% angle (i.e., between the rightmost boundary of the left image and the leftmost
+% boundary of the right image) we observed (numerical) memory benefits of
+% feature-based attention in both experiments (Sustained Attention Experiment:
+% $t(59) = 4.73, p = 1.96 \times 10^{-5}, d = 0.67$; Variable Attention
+% Experiment: $t(52) = 0.64, p = 0.52, d = 0.09$) and location-based attention in
+% the Sustained Attention Experiment, but not the Variable Attention Experiment
+% (Sustained Attention Experiment: $t(59) = 0.67, p = 0.51, d = 0.09$; Variable
+% Attention Experiment: $t(52) = -0.79, p = 0.43, d = 0.11$). These analyses
+% indicate that although the focus of covert attention can affect where people
+% are looking, covert attention affects memory encoding beyond what may be
+% accounted for by gaze position alone.
 
-\begin{figure*}[tp]
-  \centering
-  \includegraphics[width=\textwidth]{figures/Side_Cued_TimeSeries_2.pdf}
+% The preceding results indicate that volitional covert attention affects memory,
+% and that feature-based and location-based covert attention may come online at
+% different timescales. We next sought to examine how long the memory effects of
+% feature-based and location-based covert attention persist. To gain additional
+% insights into the timecourse of the impact of feature-based and location-based
+% attention on memory, we used a sliding window analysis to measure how
+% participants' familiarity ratings of attended, partially attended, unattended,
+% and novel stimuli varied over the duration of the memory phases of both
+% experiments. During each block within the memory phases of each experiment,
+% participants made familiarity judgements about a total of 40 images (20 old
+% images and 20 novel images). We computed average familiarity ratings for images
+% appearing in each position of the memory stimulus sequence (positions 1--40),
+% as a function of how (or whether) they were attended during the preceding
+% presentation phase (old images) or whether they matched the category of the
+% most recent attention cue (novel images), for overlapping 20-image sliding
+% windows (Figs.~\ref{fig:familiarity_timecourse_category},
+% \ref{fig:familiarity_timecourse_location}, and
+% \ref{fig:familiarity_timecourse_novel}). We first calculated these values for
+% each participant, and then we averaged across participants.
 
-  \caption{\textbf{Familiarity ratings over time for images that matched the
-  cued or uncued image location.} This figure follows the same format and
-  conventions as Figure~\ref{fig:familiarity_timecourse_category}.
-  Figures~\timecourseCuedLocation~and \timecourseUncuedLocation~display these
-  results broken down by participant cohort.}
+% \begin{figure*}[tp]
+%   \centering
+%   \includegraphics[width=1\textwidth]{figures/Cat_Cued_TimeSeries.pdf}
 
-\label{fig:familiarity_timecourse_location}
-\end{figure*}
+%   \caption{\textbf{Familiarity ratings over time for images that matched the
+%   cued or uncued image category.} Each curve reflects the average familiarity
+%   ratings for attended, unattended, and novel images (denoted in the legends on
+%   the right) within a succession of overlapping 20-image sliding windows. Error
+%   ribbons denote 95\% confidence intervals, computed across participants.
+%   Panels \textbf{a.} and \textbf{c.} display results from the Sustained
+%   Attention Experiment and Panels \textbf{b.} and \textbf{d.} display results
+%   from the Variable Attention Experiment. The paired horizontal lines at the
+%   bottom of each panel denote timepoints when the given pair of curves was
+%   statistically distinguishable (i.e., the topmost line color was statistically
+%   greater than the bottommost line color at $\alpha = 0.05$, via a paired
+%   two-tailed $t$-test.) The gray lines in Panels b and d reflect familiarity
+%   ratings of novel stimuli from both the most recently attended and unattended
+%   image categories. Figures~\timecourseCuedCategory~and
+%   \timecourseUncuedCategory~display these results broken down by participant
+%   cohort.}
 
-We next examined how participants' familiarity ratings varied over the duration
-of the memory phases of each experiment as a function of the attended location.
-Participants in the Sustained Attention Experiment rated attended-category
-images as more familiar, at both the attended and unattended locations
-(Fig.~\ref{fig:familiarity_timecourse_location}, left panels). In contrast,
-participants in the Variable Attention Experiment rated attended-category
-images as more familiar than unattended-category images only at the attended
-locations (Fig.~\ref{fig:familiarity_timecourse_location}, right panels). The
-primary difference in familiarity ratings between Sustained Attention
-Experiment versus Variable Attention Experiment participants was in how they
-rated unattended-category images. Participants in the Variable Attention Task
-rated unattended-category images as more familiar than did participants in the
-Sustained Attention Task; this pattern persisted throughout the memory phase
-and held for images at both the attended and unattended locations (compare
-heights of blue lines in the left versus right panels of
-Fig.~\ref{fig:familiarity_timecourse_location}). This suggests that lower
-familiarity ratings of unattended-category stimuli in the Sustained Attention
-Experiment are due to suppression of the encoding of unattended-category
-features (e.g., as opposed to enhancement of the encoding of attended-category
-features). This suppression effect appears to build over an interval that is
-longer than the duration of a single stimulus presentation (5.5~s).
+% \label{fig:familiarity_timecourse_category}
+% \end{figure*}
 
-\begin{figure*}[tp]
-  \centering
-  \includegraphics[width=1\textwidth]{figures/Novel_Timecourse_Panels.pdf}
+% Throughout the memory phase, participants from both experiments rated attended
+% images as more familiar than category-matched unattended and novel images
+% (Fig.~\ref{fig:familiarity_timecourse_category}, top row). This indicates that
+% the memory benefits of attending to specific stimulus features (versus
+% category-general features) persist for at least as long as the duration of the
+% memory phase (2~min). Early in the memory phase, participants in the Variable
+% Attention Experiment also rated category-matched unattended images as more
+% familiar than novel images. This pattern did not hold for participants in the
+% Sustained Attention Experiment. The short-lived boost in familiarity for
+% attended-category images at the unattended location following variable (but not
+% sustained) attention suggests that the timecourse of feature-based attention's
+% impact on memory depends on how long the focus of feature-based attention has
+% been held.
 
-  \caption{\textbf{Familiarity ratings over time for attended-category and
-  unattended-category novel images.} The top panels of this figure follow the
-  same formats and conventions as
-  Figures~\ref{fig:familiarity_timecourse_category} and
-  \ref{fig:familiarity_timecourse_location}. The bottom panels display the
-  differences between the timecourses of familiarity ratings of
-  attended-category and unattended-category novel stimuli. The error ribbons
-  denote 95\% confidence intervals, computed across participants. The dotted
-  horizontal line in each panel denotes a difference of 0-- i.e., the value
-  above which attended-category novel images were rated as more familiar than
-  unattended-category novel images. The black lines in the bottom panels
-  display linear regression fits to the data (error ribbons denote 95\%
-  confidence intervals). Figures~\timecourseNovel~and \timecourseDiff~display
-  these results broken down by participant cohort.}
+% Participants in both experiments also rated unattended-category images at the
+% attended location as more familiar than unattended-category images at the
+% unattended location and novel unattended-category images
+% (Fig.~\ref{fig:familiarity_timecourse_category}, bottom row). This pattern
+% persisted throughout the memory phases of both experiments. This supports the
+% notion that location-based attention enhances memory in a (partially)
+% feature-independent way. Participants in the Variable Attention Experiment also
+% rated unattended-category images at the unattended location as (numerically)
+% more familiar than novel images (though this pattern was only statistically
+% reliable towards the middle of the memory phase). This pattern did not hold for
+% participants in the Sustained Attention Experiment. Participants in the
+% Sustained Attention Experiment rated unattended-category images (regardless of
+% location or novelty status) as less familiar than participants in the Variable
+% Attention Experiment (e.g., compare heights of the lines in the bottom left
+% versus bottom right panels of Fig.~\ref{fig:familiarity_timecourse_category}).
+% This suggests that, after sustained feature-based attention to a particular
+% image category, the encodings of stimuli from the unattended category are
+% suppressed. This suppression effect appears to persist at least as long as the
+% memory phase of the experiment (2~min). Further, the magnitude of this
+% suppression effect appears to become stronger following longer-term sustained
+% (versus shorter-term variable) feature-based attention.
 
-\label{fig:familiarity_timecourse_novel}
-\end{figure*}
+% \begin{figure*}[tp]
+%   \centering
+%   \includegraphics[width=\textwidth]{figures/Side_Cued_TimeSeries_2.pdf}
 
-Finally, we examined how participants in both experiments rated the familiarity
-of novel images. These ratings provide insights into how modulating the focus
-of attention to \textit{prior} stimuli can affect the perception of
-\textit{future} stimuli. We considered how participants rated novel stimuli
-that matched versus did not match the category (face or scene) of the most
-recent attention cue. Participants in the Sustained Attention Experiment rated
-attended-category novel stimuli as more familiar than unattended-category novel
-stimuli throughout the entire memory phase
-(Fig.~\ref{fig:familiarity_timecourse_novel}a). By contrast, participants in
-the Variable Attention Experiment rated attended-category and
-unattended-category novel images similarly throughout the memory phase
-(Fig.~\ref{fig:familiarity_timecourse_novel}b). The difference in familiarity
-ratings between the two experiments primarily reflects that participants in the
-Variable Attention Experiment rated unattended-category novel images as more
-familiar than did participants in the Sustained Attention Experiment (e.g.,
-compare blue lines in Fig.~\ref{fig:familiarity_timecourse_novel}a versus
-\ref{fig:familiarity_timecourse_novel}b). This may indicate that the processing
-of unattended-category novel stimuli is suppressed following sustained
-attention (e.g., as opposed to enhancing the processing of attended-category
-novel stimuli). The differences in familiarity between attended-category versus
-unattended-category novel images increased slightly but reliably throughout the
-memory phases of both experiments (Fig.~\ref{fig:familiarity_timecourse_novel},
-bottom panels; slope of regression line fit to differences in Sustained
-Attention Experiment: $\beta = 2.05 \times 10^{-3}, p = 1.07 \times 10^{-14} $;
-slope of regression for Variable Attention Experiment: $\beta = 1.54 \times
-10^{-3}, p = 5.63 \times 10^{-13} $). This might reflect a process whereby the
-suppression of unattended features continues to build for a short duration even
-after the participant stops volitionally focusing on the attended features.
+%   \caption{\textbf{Familiarity ratings over time for images that matched the
+%   cued or uncued image location.} This figure follows the same format and
+%   conventions as Figure~\ref{fig:familiarity_timecourse_category}.
+%   Figures~\timecourseCuedLocation~and \timecourseUncuedLocation~display these
+%   results broken down by participant cohort.}
+
+% \label{fig:familiarity_timecourse_location}
+% \end{figure*}
+
+% We next examined how participants' familiarity ratings varied over the duration
+% of the memory phases of each experiment as a function of the attended location.
+% Participants in the Sustained Attention Experiment rated attended-category
+% images as more familiar, at both the attended and unattended locations
+% (Fig.~\ref{fig:familiarity_timecourse_location}, left panels). In contrast,
+% participants in the Variable Attention Experiment rated attended-category
+% images as more familiar than unattended-category images only at the attended
+% locations (Fig.~\ref{fig:familiarity_timecourse_location}, right panels). The
+% primary difference in familiarity ratings between Sustained Attention
+% Experiment versus Variable Attention Experiment participants was in how they
+% rated unattended-category images. Participants in the Variable Attention Task
+% rated unattended-category images as more familiar than did participants in the
+% Sustained Attention Task; this pattern persisted throughout the memory phase
+% and held for images at both the attended and unattended locations (compare
+% heights of blue lines in the left versus right panels of
+% Fig.~\ref{fig:familiarity_timecourse_location}). This suggests that lower
+% familiarity ratings of unattended-category stimuli in the Sustained Attention
+% Experiment are due to suppression of the encoding of unattended-category
+% features (e.g., as opposed to enhancement of the encoding of attended-category
+% features). This suppression effect appears to build over an interval that is
+% longer than the duration of a single stimulus presentation (5.5~s).
+
+% \begin{figure*}[tp]
+%   \centering
+%   \includegraphics[width=1\textwidth]{figures/Novel_Timecourse_Panels.pdf}
+
+%   \caption{\textbf{Familiarity ratings over time for attended-category and
+%   unattended-category novel images.} The top panels of this figure follow the
+%   same formats and conventions as
+%   Figures~\ref{fig:familiarity_timecourse_category} and
+%   \ref{fig:familiarity_timecourse_location}. The bottom panels display the
+%   differences between the timecourses of familiarity ratings of
+%   attended-category and unattended-category novel stimuli. The error ribbons
+%   denote 95\% confidence intervals, computed across participants. The dotted
+%   horizontal line in each panel denotes a difference of 0-- i.e., the value
+%   above which attended-category novel images were rated as more familiar than
+%   unattended-category novel images. The black lines in the bottom panels
+%   display linear regression fits to the data (error ribbons denote 95\%
+%   confidence intervals). Figures~\timecourseNovel~and \timecourseDiff~display
+%   these results broken down by participant cohort.}
+
+% \label{fig:familiarity_timecourse_novel}
+% \end{figure*}
+
+% Finally, we examined how participants in both experiments rated the familiarity
+% of novel images. These ratings provide insights into how modulating the focus
+% of attention to \textit{prior} stimuli can affect the perception of
+% \textit{future} stimuli. We considered how participants rated novel stimuli
+% that matched versus did not match the category (face or scene) of the most
+% recent attention cue. Participants in the Sustained Attention Experiment rated
+% attended-category novel stimuli as more familiar than unattended-category novel
+% stimuli throughout the entire memory phase
+% (Fig.~\ref{fig:familiarity_timecourse_novel}a). By contrast, participants in
+% the Variable Attention Experiment rated attended-category and
+% unattended-category novel images similarly throughout the memory phase
+% (Fig.~\ref{fig:familiarity_timecourse_novel}b). The difference in familiarity
+% ratings between the two experiments primarily reflects that participants in the
+% Variable Attention Experiment rated unattended-category novel images as more
+% familiar than did participants in the Sustained Attention Experiment (e.g.,
+% compare blue lines in Fig.~\ref{fig:familiarity_timecourse_novel}a versus
+% \ref{fig:familiarity_timecourse_novel}b). This may indicate that the processing
+% of unattended-category novel stimuli is suppressed following sustained
+% attention (e.g., as opposed to enhancing the processing of attended-category
+% novel stimuli). The differences in familiarity between attended-category versus
+% unattended-category novel images increased slightly but reliably throughout the
+% memory phases of both experiments (Fig.~\ref{fig:familiarity_timecourse_novel},
+% bottom panels; slope of regression line fit to differences in Sustained
+% Attention Experiment: $\beta = 2.05 \times 10^{-3}, p = 1.07 \times 10^{-14} $;
+% slope of regression for Variable Attention Experiment: $\beta = 1.54 \times
+% 10^{-3}, p = 5.63 \times 10^{-13} $). This might reflect a process whereby the
+% suppression of unattended features continues to build for a short duration even
+% after the participant stops volitionally focusing on the attended features.
 

### 2023-03-25 paper/supplemental_materials.tex
working on results section

@@
 \usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
-% ^^ moves subfigure titles to the top
  \usepackage{pxfonts}
 
-\def\rot#1{\raisebox{-1.35in}{\rotatebox{90}{#1}}}
-% ^^ moves vertical titles down to the middle of the subfigures
-
-\def\roto#1{\raisebox{-1.17in}{\rotatebox{90}{#1}}}
+ \newcommand{\familiarity}{2}
 
@@
 
-\title{Supporting Materials for \textit{Feature-based and location-based volitional covert attention affect memory at different timescales}}
+\title{Supporting Materials for \textit{Category-based and location-based volitional covert attention affect
+memory at different timescales}}
 
-\author{Kirsten Ziman$^1$,
+\author{Kirsten Ziman$^1, 2$,
 Madeline R. Lee$^1$,
 Alejandro R. Martinez$^1$,\\
-Ethan D. Adner$^2$,
+Ethan D. Adner$^1$,
 and
-Jeremy R. Manning\textsuperscript{$1, \dagger$}\\[0.1in]$^1$Department of Psychological and Brain Sciences and\\
-$^2$Thayer School of Engineering,\\
-Dartmouth College, Hanover, NH 03755\\
+Jeremy R. Manning\textsuperscript{$1, \dagger$}\\[0.1in]$^1$Dartmouth College\\
+$^2$Princeton University\\
 \textsuperscript{$\dagger$}Address correspondence to jeremy.r.manning@dartmouth.edu}
@@
 
-%\section*{Supplement}
+  \begin{figure*}[tp]
+	\centering
+	\includegraphics[width=1\textwidth]{figs/gaze_locations}
 
-%Here, we separately replicate the figures in our manuscript for the initial participant cohort and the replication cohort of each experiment.
+ \caption{\textbf{Gaze location histograms.} We divided the experimental
+ display into 120 horizontal bins and 78 vertical bins, each comprising a
+ roughly 0.5~cm square. The panels display the average proportions of time
+ (throughout the duration of the experiment) participants spend looking at each
+ location. The left panel displays data from participants in the sustained
+ attention condition and the right panel displays data from participants in the
+ variable attention condition. In both panels, the locations of the central
+ fixation cross (red $+$) and composite images (red-outlined squares) are
+ indicated.}
 
-% FIGURE - violin
-\begin{figure}
-\captionsetup[subfigure]{labelformat=empty}
-\roto{\rlap{\textbf{Sustained}}}
- \subfloat[(a) Initial cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.4\textwidth}
+  \label{fig:gaze-histograms}
+  \end{figure*}
+
+  \begin{figure*}[tp]
 	\centering
-	   \includegraphics[width=\textwidth]{supp_figures/Maddy_sustain1violin.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat[(b) Replication cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.4\textwidth}
+	\includegraphics[width=1\textwidth]{figs/gaze_intersections}
+
+\caption{\textbf{Proportions of excluded trials.} We excluded from our analyses
+any images from trials where the participant's gaze touched on any part of the
+attended composite image (attended-side red squares in
+Fig.~\ref{fig:gaze-histograms}). \textbf{A--B. Proportions of excluded trials,
+by run.} Across both experimental conditions (left: sustained attention; right:
+variable attention), the bars display the average proportions of presentations
+from each run where participants looked at any part of the attended composite
+image, for any non-zero duration. Error bars denote across-participant
+bootstrap-estimated 95\% confidence intervals. \textbf{C--D. Proportions of
+excluded trials, by participant.} Across both experimental conditions (left:
+sustained attention; right: variable attention), the bars display the average
+proportions of presentations across different runs where the given
+pariticapants looked at any part of the attended composite image, for any
+non-zero duration. Error bars denote across-run bootstrap-estimated 95\%
+confidence intervals.}
+
+  \label{fig:intersections}
+  \end{figure*}
+
+  \label{fig:gaze-histograms}
+\end{figure*}
+
+\begin{figure*}[tp]
   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/Maddy_sustain2violin.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat{
-	\begin{minipage}[c][1\width]{
-	   0.1\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/violin_key.pdf}
-	\end{minipage}}
+  \includegraphics[width=1\textwidth]{figs/familiarity_by_attention_level and_category}
 
-% \hfill
-  %\subfloat[Combined data]{
-	%\begin{minipage}[c][1\width]{
-	   %0.5\textwidth}
-	   %\centering
-	   %\includegraphics[width=\textwidth]{example-image-a.pdf}
-	%\end{minipage}}
+\caption{\textbf{Familiarity by attention level and stimulus category.} The
+bars display the average familiarity ratings participants gave to images from
+the same category and location as the attention cue (fully attended), the same
+category (but opposite location) as the attention cue (attended category), the
+same location (but opposite category) as the attention cue (attended location),
+the opposite category and location as the attention cue (unattended), or novel
+images. Each family of bars is further sub-divided according to whether the
+rated stimulus was a face (darker shading) or a place (lighter shading) image.
+The left panel displays familiarity ratings from the sustained attention
+condition and the right panel displays familiarity ratings from the variable
+attention condition. All error bars denote across-participant
+bootstrap-estimated 95\% confidence intervals. Also see Figure~\familiarity~in
+the main text.}
 
-\roto{\rlap{\textbf{Variable}}}
-  \subfloat[(c) Initial cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.4\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/Maddy_variabl1violin.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat[(d) Replication cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.4\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/Maddy_variabl2violin.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat{
-	\begin{minipage}[c][1\width]{
-	   0.1\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/violin_key.pdf}
-	\end{minipage}}
-
-\caption{\textbf{Familiarity ratings for attended, unattended, and
-    novel stimuli.}  This figure follows the same formatting as
-  Figure~2 in the main text, but the panels in this figure break down
-  those results by participant cohort.
-Each split violin plot displays the distribution of within-participant average familiarity ratings given to faces (left, darker colors) and scenes (right, lighter colors) during the memory phases of each experiment.
-As shown in the legend (bottom), the colors indicate whether each image had been viewed during the presentation phase (\texttt{old}) or not; whether the given images matched the \texttt{attended category}; and/or whether the given images matched the \texttt{attended location}.
-The colored lines above each set of violin plots denote statistical differences  (\textbf{pos}itive or \textbf{neg}ative differences in mean, collapsing over image category, assessed via two-tailed $t$-tests) between the distributions centered on the endpoints of each line.
-The line thicknesses denote $p$-values as indicated in the legend.
-Asterisks denote differences between the face versus scene distributions (assessed via two-tailed $t$-tests).}
-
-\end{figure}
-
-% FIGURE - gaze
-
-\begin{figure}[ht]
-\captionsetup[subfigure]{labelformat=empty}
-\rot{\rlap{\textbf{Sustained}}}
-  \subfloat[(a) Initial cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/sustain_gaze_1.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat[(b) Replication cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/sustain_gaze_2.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat{
-	\begin{minipage}[c][1\width]{
-	   0.2\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/gaze_legend.pdf}
-	\end{minipage}}
-
-\raisebox{.05in}{\rot{\rlap{\textbf{Variable}}}}
-  \subfloat[(c) Initial cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/variabl_gaze_1.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat[(d) Replication cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/variabl_gaze_2.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat{
-	\begin{minipage}[c][1\width]{
-	   0.2\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/gaze_legend.pdf}
-	\end{minipage}}
-
-  \caption{\textbf{Horizontal coordinates of visual fixations.}  This figure follows the same formatting as
-  Figure~3 in the main text, but the panels in this figure break down
-  those results by participant cohort.
-Each violin plot displays a distribution of participant-wise average horizontal gaze positions relative to a presented image.
-The coordinates have been normalized such that a value of 1.0 denotes the furthest onscreen coordinate from the central fixation point \textit{towards} the direction of the given image, and -1.0 denotes the furthest onscreen coordinate from the central fixation point \textit{away from} the direction of the given image.
-The gray bars in each panel mark the boundaries of the presented images.
-The violin plots are broken down by participants' familiarity ratings during the memory phases of each experiment, and by each image's relation to the attention cue while that image appeared onscreen.
-}\end{figure}
-
-% FIGURE - cued_window
-
-\begin{figure}[ht]
-\captionsetup[subfigure]{labelformat=empty}
-\rot{\rlap{\textbf{Sustained}}}
-  \subfloat[(a) Initial cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/sust1_cued_window.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat[(b) Replication cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/sust2_cued_window.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat{
-	\begin{minipage}[c][1\width]{
-	   0.2\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/red_key.pdf}
-	\end{minipage}}
-
-\raisebox{.05in}{\rot{\rlap{\textbf{Variable}}}}
-  \subfloat[(c) Initial cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/var1_cued_window.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat[(d) Replication cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/var2_cued_window.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat{
-	\begin{minipage}[c][1\width]{
-	   0.2\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/red_key.pdf}
-	\end{minipage}}
-
-  \caption{\textbf{Familiarity ratings over time for images that matched cued image category.}  This figure follows the same formatting as
-  Figure~4 (top panels) in the main text, but the panels in this figure break down
-  those results by participant cohort.
-Each curve reflects the average familiarity ratings for attended, unattended, and novel images (denoted in the legends on the right) within a succession of overlapping 20-image sliding windows.
-Error ribbons denote 95\% confidence intervals, computed across participants.
-The paired horizontal lines at the bottom of each panel denote timepoints when the given pair of curves was statistically distinguishable (i.e., the topmost line color was statistically greater than the bottommost line color at $\alpha = 0.05$, via a paired two-tailed $t$-test.)}
-  \label{fig:familiarity_timecourse_category3}
-\end{figure}
-
-% FIGURE - uncued_window
-
-\begin{figure}[ht]
-\captionsetup[subfigure]{labelformat=empty}
-\rot{\rlap{\textbf{Sustained}}}
-  \subfloat[(a) Initial cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/sust1_uncued_window.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat[(b) Replication cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/sust2_uncued_window.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat{
-	\begin{minipage}[c][1\width]{
-	   0.2\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/blue_key.pdf}
-	\end{minipage}}
-
-\raisebox{.05in}{\rot{\rlap{\textbf{Variable}}}}
-  \subfloat[(c) Initial cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/var1_uncued_window.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat[(d) Replication cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/var2_uncued_window.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat{
-	\begin{minipage}[c][1\width]{
-	   0.2\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/blue_key.pdf}
-	\end{minipage}}
-
-  \caption{\textbf{Familiarity ratings over time for images that matched uncued image category.}  This figure follows the same formatting as
-  Figure~4 (bottom panels) in the main text, but the panels in this figure break down
-  those results by participant cohort.
-Each curve reflects the average familiarity ratings for attended, unattended, and novel images (denoted in the legends on the right) within a succession of overlapping 20-image sliding windows.
-Error ribbons denote 95\% confidence intervals, computed across participants.
-The paired horizontal lines at the bottom of each panel denote timepoints when the given pair of curves was statistically distinguishable (i.e., the topmost line color was statistically greater than the bottommost line color at $\alpha = 0.05$, via a paired two-tailed $t$-test.)}
-  \label{fig:familiarity_timecourse_category4}
-\end{figure}
-
-% FIGURE - cued_loc
-
-\begin{figure}[ht]
-\captionsetup[subfigure]{labelformat=empty}
-\rot{\rlap{\textbf{Sustained}}}
-  \subfloat[(a) Initial cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/sust1_cued_loc.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat[(b) Replication cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/sust2_cued_loc.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat{
-	\begin{minipage}[c][1\width]{
-	   0.2\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/red_blue_key.pdf}
-	\end{minipage}}
-
-\raisebox{.05in}{\rot{\rlap{\textbf{Variable}}}}
-  \subfloat[(c) Initial cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/var1_cued_loc.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat[(d) Replication cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/var2_cued_loc.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat{
-	\begin{minipage}[c][1\width]{
-	   0.2\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/red_blue_key.pdf}
-	\end{minipage}}
-
-\caption{\textbf{Familiarity ratings over time for images that matched the cued image location.}  This figure follows the same formatting as
-  Figure~5 (top panels) in the main text, but the panels in this figure break down
-  those results by participant cohort.}
-\label{fig:familiarity_timecourse_location5}
-\end{figure}
-
-% FIGURE - uncued_loc
-
-\begin{figure}[ht]
-\captionsetup[subfigure]{labelformat=empty}
-\rot{\rlap{\textbf{Sustained}}}
-  \subfloat[(a) Initial cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/sust1_uncued_loc.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat[(b) Replication cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/sust2_uncued_loc.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat{
-	\begin{minipage}[c][1\width]{
-	   0.2\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/orange_blue_key.pdf}
-	\end{minipage}}
-
-\raisebox{.05in}{\rot{\rlap{\textbf{Variable}}}}
-  \subfloat[(c) Initial cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/var1_uncued_loc.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat[(d) Replication cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/var2_uncued_loc.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat{
-	\begin{minipage}[c][1\width]{
-	   0.2\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/orange_blue_key.pdf}
-	\end{minipage}}
-
-\caption{\textbf{Familiarity ratings over time for images that matched uncued image location.}  This figure follows the same formatting as
-  Figure~5 (bottom panels) in the main text, but the panels in this figure break down
-  those results by participant cohort.}
-\label{fig:familiarity_timecourse_location6}
-\end{figure}
-
-% FIGURE - novel window
-
-\begin{figure}[ht]
-\captionsetup[subfigure]{labelformat=empty}
-\rot{\rlap{\textbf{Sustained}}}
-  \subfloat[(a) Initial cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/sust1_novel_window.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat[(b) Replication cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/sust2_novel_window.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat{
-	\begin{minipage}[c][1\width]{
-	   0.2\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/novel_key.pdf}
-	\end{minipage}}
-
-\raisebox{.05in}{\rot{\rlap{\textbf{Variable}}}}
-  \subfloat[(c) Initial cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/var1_novel_window.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat[(d) Replication cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.35\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/var2_novel_window.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat{
-	\begin{minipage}[c][1\width]{
-	   0.2\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/novel_key.pdf}
-	\end{minipage}}
-
-   \caption{\textbf{Familiarity ratings over time for attended-category and unattended-category novel images.}  This figure follows the same formatting as
-  Figure~6 (top panels) in the main text, but the panels in this figure break down
-  those results by participant cohort.}\end{figure}
-
-% FIGURE - diff
-
-\begin{figure}[ht]
-\raisebox{-.4in}{\rot{\rlap{\textbf{Sustained}}}}
-  \subfloat[Initial cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.5\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/sust1_diff.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat[Replication cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.5\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/sust2_diff.pdf}
-	\end{minipage}}
-
-\raisebox{-.35in}{\rot{\rlap{\textbf{Variable}}}}
-  \subfloat[Initial cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.5\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/var1_diff.pdf}
-	\end{minipage}}
- \hfill
-  \subfloat[Replication cohort]{
-	\begin{minipage}[c][1\width]{
-	   0.5\textwidth}
-	   \centering
-	   \includegraphics[width=\textwidth]{supp_figures/var2_diff.pdf}
-	\end{minipage}}
-
- \caption{\textbf{Familiarity ratings over time for attended-category and unattended-category novel images.}  This figure follows the same formatting as
-  Figure~6 (bottom panels) in the main text, but the panels in this figure break down
-  those results by participant cohort.}
-\end{figure}
+\label{fig:ratings-by-category}
+\end{figure*}
 

### 2023-03-25 paper/main.tex
minor wording fix
added order effect analyses to results section

@@
 
+\begin{figure*}[tp]
+	\centering
+	\includegraphics[width=0.7\textwidth]{figs/familiarity_by_attention_level}
+
+  \caption{\textbf{Familiarity by attention level.} The bars display the
+  average familiarity ratings participants gave to images from the same
+  category and location as the attention cue (fully attended), the same
+  category (but opposite location) as the attention cue (attended category),
+  the same location (but opposite category) as the attention cue (attended
+  location), the opposite category and location as the attention cue
+  (unattended), or novel images. The left panel displays familiarity ratings
+  from the sustained attention condition and the right panel displays
+  familiarity ratings from the variable attention condition. All error bars
+  denote across-participant bootstrap-estimated 95\% confidence intervals. For results
+  sub-divided by stimulus category, see Figure~\ratingsByCategory.}
+
+  \label{fig:familiarity}
+  \end{figure*}
+
 We first wondered whether (and how) shifts in covert attention might affect
@@
 participants in the sustained attention condition ($t(51) = 2.174, p = 0.034$).
-This suggests that the timescales over which location-based versus
-category-based attention tend to operate may differ.
+This suggests that category-based versus location-based attention may operate
+over different timescales.
+
+\begin{figure*}[tp]
+	\centering
+	\includegraphics[width=0.7\textwidth]{figs/encoding_and_retrieval_timecourses}
+
+  \caption{\textbf{Familiarity ratings by serial positions and attention
+  level.} \textbf{A. Subsequent familiarity ratings by presentation position
+  (sustained attention condition).} The curves' colors denote the attention
+  levels of each presented image. The $x$-axis denotes the presentation
+  positions of each image within the sequence of 10 composite image pairs
+  during the run when it was presented. The $y$-axis denotes the average
+  familiarity ratings later given to the corresponding items. \textbf{B.
+  Subsequent familiarity ratings by presentation position (variable attention
+  condition).} This panel is in the same format as Panel A, but displays
+  ratings for the variable attention condition. \textbf{C. Familiarity ratings
+  by memory probe position (sustained attention condition).} The curve's colors
+  denote the attention levels (or novelty) of each probe image. The $x$-axis
+  denotes the position of each probed image within the sequence of 40 images
+  that participants judged during the memory phase of the experiemnt. The
+  $y$-axis denotes the average familiarity ratings given to the corresponding
+  probes. \textbf{D. Familiarity ratings by memory probe position (variable
+  attention condition).} This panel is in the same format as Panel C, but
+  displays ratings for the variable attention condition. All panels: error
+  ribbons denote across-participant bootstrap-estimated 95\% confidence
+  intervals.}
+
+  \label{fig:timecourses}
+  \end{figure*}
+
+Given the above results suggesting potential differences in the timescales of
+category-based and location-based attention, we carried out two additional
+exploratory analyses aimed at identifying other timing effects. First, we
+wondered whether participants' familiarity ratings might show serial position
+effects analogous to those reported in classic recognition memory
+studies~\citep[e.g.,][]{Neat93b, McElDosh89, WickNorm66}. For each participant,
+for each composite image pair (presented in each trial during the study phase
+of the experiment), we labeled each composite's face and place image component
+according to whether it matched the cued category and/or location. We discarded
+any face or place images that did not appear in the participants' memory phase.
+We tagged the remaining (probed) images with the familiarity ratings that
+participants would later give the images during the memory phase and plotted
+these ratings against the images' presentation positions
+(Figs.~\ref{fig:timecourses}A and B). Across both experimental conditions and
+across all serial positions, we generally found that the average ordering of
+familiarity ratings by attention level (Fig.~\ref{fig:familiarity}) were
+preserved. This suggests that the encoding-related affects of attention on
+subsequent recognition memory are relatively stable over time (e.g., we did not
+observe clear primacy or recency effects during the study phase of the
+experiment). Second, we carried out an analogous analysis to identify potential
+serial position effects of recall order. For each probed item a participant
+rated during the memory phase, we assigned the image a label according to
+whether the participant's attention cue (at the time the image was presented as
+part of its composite pair) matched the image's category and/or location, or
+whether the image was novel (i.e., not presented during the study phase).
+Again, we found that (across both experimental conditions and all probe
+positions) in general the average ordering of familiarity ratings by attention
+level (Fig.~\ref{fig:familiarity}) were preserved. This suggests that the
+retrieval-related affects of attention on subsequent recognition memory are
+relatively stable over time (e.g., we did not observe clear primacy or recency
+effects during the memory phase of the experiment).
 
 \textbf{JRM STOPPED HERE}
+%note: discuss response bias analyses next (also add to supplement)
 
@@
 
-\begin{figure*}[tp]
-  \centering \includegraphics[width=0.75\textwidth]{figures/discussion_schematic}
-
-  \caption{\textbf{Timecourse of encoding and retrieval effects of
-  feature-based and location-based attention.} The focus of location-based
-  attention (green) may be modulated quickly and rapidly enhances memory
-  encoding for nearby stimuli. The focus of feature-based attention (purple) is
-  modulated more slowly, and serves to suppress unattended stimulus features.
-  The effects of location-based attention on memory persist for longer than the
-  effects of feature-based attention. Sustained attention (darker shading)
-  yields more robust enhancement and suppression than shorter-term (variable)
-  attention (light shading). The vertical gray line on the left denotes the
-  duration of a single stimulus presentation (the upper bound by which
-  location-based attention begins to affect encoding, and the lower-bound by
-  which feature-based attention begins to affect encoding). The vertical gray
-  line on the right separates encoding from immediate subsequent retrieval of
-  the encoded information.}
-
-\label{fig:model}
-\end{figure*}
+% \begin{figure*}[tp]
+%   \centering \includegraphics[width=0.75\textwidth]{figures/discussion_schematic}
+
+%   \caption{\textbf{Timecourse of encoding and retrieval effects of
+%   feature-based and location-based attention.} The focus of location-based
+%   attention (green) may be modulated quickly and rapidly enhances memory
+%   encoding for nearby stimuli. The focus of feature-based attention (purple) is
+%   modulated more slowly, and serves to suppress unattended stimulus features.
+%   The effects of location-based attention on memory persist for longer than the
+%   effects of feature-based attention. Sustained attention (darker shading)
+%   yields more robust enhancement and suppression than shorter-term (variable)
+%   attention (light shading). The vertical gray line on the left denotes the
+%   duration of a single stimulus presentation (the upper bound by which
+%   location-based attention begins to affect encoding, and the lower-bound by
+%   which feature-based attention begins to affect encoding). The vertical gray
+%   line on the right separates encoding from immediate subsequent retrieval of
+%   the encoded information.}
+
+% \label{fig:model}
+% \end{figure*}
 

### 2023-03-26 paper/main.tex
finished draft of results section and supplement

@@
 \newcommand{\ratingsByCategory}{S3}
+\newcommand{\sequenceLength}{S4}
+\newcommand{\responseBias}{S5}
 
@@
 same physical (objective) experience may give rise to very different perceived
-(subjective) experiences across people~\citep{FreeSimo11, ChanEtal18}.
+(subjective) experiences across people~\citep{FreeSimo11, ChanEtal21a}.
 
@@
 sustained volitional attention enhances memory relative to unconscious
-attentional processes~\citep{UncaEtal11, GoloEtal13}. However, volitional
+attentional processes~\citep{UncaEtal11, TurkEtal13}. However, volitional
 attention takes many forms, such as attention to particular spatial locations
@@
 
-\textbf{JRM STOPPED HERE}
-%note: discuss response bias analyses next (also add to supplement)
+Our finding that location-attended items appear to receive a familiarity boost
+in the variable attention condition but not the sustained attention condition
+is consistent with two possible interpretations. One possibility is that
+focusing attention requires just a brief trigger (in this case, an attention
+cue), but different forms of attention (in this case, category-based attention
+versus location-based attention) require different amounts of time to ``ramp
+up'' to full efficacy such that they begin to affect memory encoding. For
+example, if category-based attention ramps up more slowly than location-based
+attention, this might explain why the relative ordering of category-matched
+versus location-matched unattended images changes between the sustained
+attention and variable attention conditions (orange and yellow bars in
+Fig.~\ref{fig:familiarity}). A second possibility is that each attention cue
+provides a ``boost'' to memory encoding for the relevant aspects of one's
+experience (e.g., image categories, spatial locations), but the size of the
+boost varies across different forms of attention. If so, the \textit{number} of
+successive attention cues one receives should predict how effectively the
+attended and partially attended images are encoded. We developed a sequence
+length analysis to distinguish between these possibilities. For each probed
+(target) image that had been presented as a composite image pair, we computed
+the number of matching attention cues the participant had received by the time
+the given images were presented (up to and including the image's composite
+pair). We computed these sequence lengths by defining ``matching'' cues in
+three ways: (a) a match means the cues are for the same category \textit{and}
+location, (b) a match means that the cues are for the same category, and (c) a
+match means that the cues are for the same location. This yielded, for each
+target image, an associated count of how many matching attention cues the
+participant had received up to and including that image's presentation. As
+shown in Figure~\sequenceLength, we used linear regressions of familiarity
+rating on sequence lengths to identify potential sequence length effects. For
+both experimental conditions, all attention levels, and for all three
+approaches to defining matching cue sequence lengths, we found virtually no
+reliable associations between cue sequence length and familiarity. This finding
+is most parsimonious with the first possiblity mentioned above-- i.e., that
+attention may be guided by a brief trigger, but that different forms of
+attention may take differently long to affect memory encoding.
 
-% We considered each image we probed in the memory phase with respect to whether
-% (and how) the participant had experienced and/or attended to that image during
-% the presentation phase (Fig.~\ref{fig:familiarity}). For example, if a given
-% face image had been presented as part of the composite image on the right of
-% the screen following an \texttt{attend to the face on the right} instruction,
-% then that face image would have been the focus of the participant's attention
-% during one stimulus presentation. The face image on the left (unattended side)
-% during that trial would have been captured by feature-based attention, but not
-% by location-based attention; and the place image (unattended category) on the
-% right during that trial would have been captured by location-based attention,
-% but not by feature-based attention. The place image on the left during that
-% trial remained outside of the focus of both feature-based and location-based
-% attention. In this way, we categorized each of the images that participants
-% experienced during the presentation phases of each experiment in terms of
-% whether they fell under the scope of feature-based and/or location-based
-% attention. We also categorized novel face and place images that we asked
-% participants to judge during the memory phase (i.e., images that the
-% participant hadn't seen before) as belonging to the attention-cued or uncued
-% category. These novel images were intended to serve as a baseline for
-% comparison. For example, we sought to measure how people rated the familiarity
-% of new images in general. We also used differences in familiarity ratings
-% between novel images of the attention-cued versus uncued categories to evaluate
-% potential \textit{prospective} affects of modulating the focus of feature-based
-% attention.
-
-% \begin{figure*}[tp]
-%   \centering
-%   \includegraphics[width=0.75\textwidth]{figs/familiarity_by_attention_level}
-
-%   \caption{\textbf{Familiarity ratings for attended, unattended, and novel
-%   stimuli.} The bars display the average familiarity ratings participants gave
-%   to images from the same category and location as the attention cue (full
-%   attention), the same category (but opposite location) as the attention cue
-%   (attended category), the same location (but opposite category) as the
-%   attention cue (attended location), the opposite category and location as the
-%   attention cue (unattended), or novel images. The left panel displays
-%   familiarity ratings from the sustained attention condition and the right
-%   panel displays familiarity ratings from the variable attention condition. All
-%   error bars denote across-participant bootstrap-estimated 95\% confidence
-%   intervals. See Figure~\ratingsByCategory~for analogous results broken down by
-%   stimulus category.}
-
-% \label{fig:familiarity}
-% \end{figure*}
-
-% Participants in both experiments rated stimuli they attended as more familiar
-% than unattended or novel stimuli (Fig.~\ref{fig:familiarity}; Sustained
-% Attention Experiment: $t(59) = 13.42, p = 1.39 \times 10^{-19}, d = 1.73$;
-% Variable Attention Experiment: $t(52) = 12.40, p = 3.70 \times 10^{-17}, d =
-% 1.70$). Participants in both experiments also rated attended scene stimuli as
-% more familiar than attended face stimuli (Sustained Attention Experiment:
-% $t(59) = 7.69, p = 1.85 \times 10^{-10}, d = 0.99$; Variable Attention
-% Experiment: $t(52) = 7.08, p = 3.63 \times 10^{-9}, d = 0.97$). These findings
-% indicate that aspects of experience that are captured by the focus of attention
-% are easier to recognize later, and that attention may preferentially benefit
-% memory for some aspects of experience to a greater extent than other aspects of
-% experience.
-
-% Participants in the Sustained Attention Experiment experiment also rated
-% unattended images that matched the attended category as more familiar than
-% unattended images that did not match the attended category (\textit{incidental
-% feature-based attention}; $t(59) = 7.17, p = 1.40 \times 10^{-9}, d = 0.93$).
-% This pattern did not hold for participants in the Variable Attention Experiment
-% ($t(52) = 0.44, p = 0.66, d = 0.06$). Participants in both experiments
-% displayed an incidental effect of location-based attention, whereby they rated
-% unattended-category images at the attended location as more familiar than
-% unattended-category images at the unattended location (Sustained Attention
-% Experiment: $t(59) = 4.32, p = 6.05 \times 10^{-5}, d = 0.56$; Variable
-% Attention Experiment: $t(52) = 2.57, p = 0.01, d = 0.35$). This indicates that
-% aspects of our experience that incidentally overlap with the focus of our
-% location-based attention are easier to recognize later, even if those aspects
-% do not fall within the intentional focus of our feature-based attention.
-
-% We defined the \textit{memory benefit of feature-based attention} as the
-% difference in mean familiarity ratings of attended stimuli and unattended
-% stimuli from the attended category versus the mean familiarity ratings of
-% unattended stimuli from the unattended category. Similarly, we defined the
-% \textit{memory benefit of location-based attention} as the difference in mean
-% familiarity ratings of attended stimuli and unattended stimuli from the
-% attended location versus the mean familiarity ratings of unattended stimuli
-% from the unattended location. Participants in the Sustained Attention
-% Experiment displayed a larger memory benefit of feature-based attention than
-% location-based attention ($t(59) = 3.25, p = 1.91 \times 10^{-3}, d = 0.42$),
-% whereas participants in the Variable Attention Experiment displayed a larger
-% memory benefit of location-based attention ($t(52) = 1.70, p = 9.99 \times
-% 10^{-2}, d = 0.23$). This appeared to be driven in part by a response bias
-% towards attended-category images. For example, relative to the most recent
-% attention cue, participants in the Sustained Attention Experiment rated
-% attended-category novel images as more familiar than unattended-category novel
-% images ($t(59) = 7.04, p = 2.35 \times 10^{-9}, d = 0.91$), whereas
-% participants in the Variable Attention Experiment responded similarly to
-% attended-category and unattended-category novel images ($t(52) = 0.23, p =
-% 0.82, d = 0.03$). The size of this attended-category response bias for novel
-% images was reliably smaller than the memory benefits of feature-based attention
-% in both experiments (Sustained Attention Experiment: $t(59) = 7.59, p = 2.68
-% \times 10^{-10}, d = 0.98$; Variable Attention Experiment: $t(52) = 6.74, p =
-% 1.31 \times 10^{-8}, d = 0.93$). This indicates that tuning the focus of
-% feature-based attention with respect to how ongoing experience is encoded in
-% memory takes longer than the duration of a single stimulus presentation
-% (including fixation, roughly 5.5~s). Further, once feature-based attention
-% comes ``online,'' it affects how \textit{new} stimuli are processed.
-
-% We also compared the relative sizes of the memory benefits of feature-based
-% attention and location-based attention across the two experiments. Participants
-% in the Sustained Attention Experiment displayed a larger difference between
-% these two effects than did participants in the Variable Attention Experiment
-% ($t(111) = 3.48, p = 7.24 \times 10^{-4}, d = 0.66$). Further, the difference
-% in mean familiarity ratings of attended-location images versus unattended
-% images was greater for participants in the Variable Attention Experiment
-% ($t(111) = 2.32, p = 0.02, d = 0.44$). The memory benefit of location-based
-% attention reliably distinguished between attended-category versus unattended
-% category images for participants in both experiments (Sustained Attention
-% Experiment: $t(59) = 9.50, p = 1.68 \times 10^{-13}, d = 1.23$; Variable
-% Attention Experiment: $t(52) = 9.72, p = 2.76 \times 10^{-13}, d = 1.33$). This
-% indicates that tuning the focus of location-based attention with respect to how
-% ongoing experience is encoded into memory occurs faster than the duration of a
-% single stimulus presentation.
-
-% We also compared reaction times to probes from the attended versus unattended
-% side. Participants in both experiments responded slightly faster on average to
-% attended-side probes, although the differences did not reach significance
-% (Sustained Attention Experiment: $t(59) = 1.03, p = 0.31, d = 0.13$; Variable
-% Attention Experiment: $t(52) = 0.65, p = 0.52, d = 0.09$). Participants in the
-% Sustained Attention Experiment displayed a slightly larger (and not
-% statistically significant) difference in attended-side versus unattended-side
-% reaction times than participants in the Variable Attention Experiment ($t(111)
-% = .87, p = 0.38, d = 0.20$). Because none of these reaction time effects were
-% statistically reliable, we are unable to draw meaningful conclusions about
-% reaction times to the attention probes on the attended versus unattended side,
-% nor are we able to draw meaningful conclusions about differences in those
-% reaction times that might be due to sustained versus variable attention.
-
-% \begin{figure}[tp]
-%   \centering
-%   \includegraphics[width=\textwidth]{figures/exps1_2_xgaze.pdf}
-
-%   \caption{\textbf{Horizontal coordinates of visual fixations.} Each violin
-%   plot displays a distribution of participant-wise average horizontal gaze
-%   positions relative to a presented image. The coordinates have been normalized
-%   such that a value of 1.0 denotes the furthest onscreen coordinate from the
-%   central fixation point \textit{towards} the direction of the given image, and
-%   -1.0 denotes the furthest onscreen coordinate from the central fixation point
-%   \textit{away from} the direction of the given image. The gray bars in each
-%   panel mark the boundaries of the presented images. The violin plots are
-%   broken down by participants' familiarity ratings during the memory phases of
-%   each experiment, and by each image's relation to the attention cue while that
-%   image appeared onscreen. Panel \textbf{a.} displays fixation data for the
-%   Sustained Attention Experiment and Panel \textbf{b.} displays fixation data
-%   for the Variable Attention Experiment. Figure~\fixation~displays these
-%   results broken down by participant cohort.}
-
-% \label{fig:fixation}
-% \end{figure}
-
-% Given that participants in both experiments rated attended-location images from
-% both the attended and unattended category as more familiar than
-% unattended-location images, we wondered whether this was truly a consequence of
-% covert attention, or whether it might be driven solely by where participants
-% were looking. In other words, we sought to distinguish the memory effects of
-% the focus of covert attention from the focus of visual gaze. We used
-% eyetracking to measure the horizontal positions of the participants' visual
-% fixations while each pair of composite stimuli appeared onscreen
-% (Fig.~\ref{fig:fixation}). For 94\% of presentation trials (Sustained Attention
-% Task: $\frac{4531}{4800}$ trials; Variable Attention Task: $\frac{3972}{4240}$
-% trials), we collected viable gaze data for analysis. In the remaining trials,
-% participant movement or other technical issues corrupted the gaze data. We
-% found that, though they generally followed our instruction to keep their gaze
-% fixed on the center of the screen, participants in both experiments exhibited a
-% slight tendency to look towards the side of the screen they were attending to
-% (Sustained Attention Task: $t(59) = 3.61, p = 6.31 \times 10^{-4}$; Variable
-% Attention Task: $t(52) = 2.86, p = 6.06 \times 10^{-3}$). When we limited our
-% analyses to trials with viable gaze data where participants successfully
-% maintained fixation on the center of the screen within 4.28$^\circ$ visual
-% angle (i.e., between the rightmost boundary of the left image and the leftmost
-% boundary of the right image) we observed (numerical) memory benefits of
-% feature-based attention in both experiments (Sustained Attention Experiment:
-% $t(59) = 4.73, p = 1.96 \times 10^{-5}, d = 0.67$; Variable Attention
-% Experiment: $t(52) = 0.64, p = 0.52, d = 0.09$) and location-based attention in
-% the Sustained Attention Experiment, but not the Variable Attention Experiment
-% (Sustained Attention Experiment: $t(59) = 0.67, p = 0.51, d = 0.09$; Variable
-% Attention Experiment: $t(52) = -0.79, p = 0.43, d = 0.11$). These analyses
-% indicate that although the focus of covert attention can affect where people
-% are looking, covert attention affects memory encoding beyond what may be
-% accounted for by gaze position alone.
-
-% The preceding results indicate that volitional covert attention affects memory,
-% and that feature-based and location-based covert attention may come online at
-% different timescales. We next sought to examine how long the memory effects of
-% feature-based and location-based covert attention persist. To gain additional
-% insights into the timecourse of the impact of feature-based and location-based
-% attention on memory, we used a sliding window analysis to measure how
-% participants' familiarity ratings of attended, partially attended, unattended,
-% and novel stimuli varied over the duration of the memory phases of both
-% experiments. During each block within the memory phases of each experiment,
-% participants made familiarity judgements about a total of 40 images (20 old
-% images and 20 novel images). We computed average familiarity ratings for images
-% appearing in each position of the memory stimulus sequence (positions 1--40),
-% as a function of how (or whether) they were attended during the preceding
-% presentation phase (old images) or whether they matched the category of the
-% most recent attention cue (novel images), for overlapping 20-image sliding
-% windows (Figs.~\ref{fig:familiarity_timecourse_category},
-% \ref{fig:familiarity_timecourse_location}, and
-% \ref{fig:familiarity_timecourse_novel}). We first calculated these values for
-% each participant, and then we averaged across participants.
-
-% \begin{figure*}[tp]
-%   \centering
-%   \includegraphics[width=1\textwidth]{figures/Cat_Cued_TimeSeries.pdf}
-
-%   \caption{\textbf{Familiarity ratings over time for images that matched the
-%   cued or uncued image category.} Each curve reflects the average familiarity
-%   ratings for attended, unattended, and novel images (denoted in the legends on
-%   the right) within a succession of overlapping 20-image sliding windows. Error
-%   ribbons denote 95\% confidence intervals, computed across participants.
-%   Panels \textbf{a.} and \textbf{c.} display results from the Sustained
-%   Attention Experiment and Panels \textbf{b.} and \textbf{d.} display results
-%   from the Variable Attention Experiment. The paired horizontal lines at the
-%   bottom of each panel denote timepoints when the given pair of curves was
-%   statistically distinguishable (i.e., the topmost line color was statistically
-%   greater than the bottommost line color at $\alpha = 0.05$, via a paired
-%   two-tailed $t$-test.) The gray lines in Panels b and d reflect familiarity
-%   ratings of novel stimuli from both the most recently attended and unattended
-%   image categories. Figures~\timecourseCuedCategory~and
-%   \timecourseUncuedCategory~display these results broken down by participant
-%   cohort.}
-
-% \label{fig:familiarity_timecourse_category}
-% \end{figure*}
-
-% Throughout the memory phase, participants from both experiments rated attended
-% images as more familiar than category-matched unattended and novel images
-% (Fig.~\ref{fig:familiarity_timecourse_category}, top row). This indicates that
-% the memory benefits of attending to specific stimulus features (versus
-% category-general features) persist for at least as long as the duration of the
-% memory phase (2~min). Early in the memory phase, participants in the Variable
-% Attention Experiment also rated category-matched unattended images as more
-% familiar than novel images. This pattern did not hold for participants in the
-% Sustained Attention Experiment. The short-lived boost in familiarity for
-% attended-category images at the unattended location following variable (but not
-% sustained) attention suggests that the timecourse of feature-based attention's
-% impact on memory depends on how long the focus of feature-based attention has
-% been held.
-
-% Participants in both experiments also rated unattended-category images at the
-% attended location as more familiar than unattended-category images at the
-% unattended location and novel unattended-category images
-% (Fig.~\ref{fig:familiarity_timecourse_category}, bottom row). This pattern
-% persisted throughout the memory phases of both experiments. This supports the
-% notion that location-based attention enhances memory in a (partially)
-% feature-independent way. Participants in the Variable Attention Experiment also
-% rated unattended-category images at the unattended location as (numerically)
-% more familiar than novel images (though this pattern was only statistically
-% reliable towards the middle of the memory phase). This pattern did not hold for
-% participants in the Sustained Attention Experiment. Participants in the
-% Sustained Attention Experiment rated unattended-category images (regardless of
-% location or novelty status) as less familiar than participants in the Variable
-% Attention Experiment (e.g., compare heights of the lines in the bottom left
-% versus bottom right panels of Fig.~\ref{fig:familiarity_timecourse_category}).
-% This suggests that, after sustained feature-based attention to a particular
-% image category, the encodings of stimuli from the unattended category are
-% suppressed. This suppression effect appears to persist at least as long as the
-% memory phase of the experiment (2~min). Further, the magnitude of this
-% suppression effect appears to become stronger following longer-term sustained
-% (versus shorter-term variable) feature-based attention.
-
-% \begin{figure*}[tp]
-%   \centering
-%   \includegraphics[width=\textwidth]{figures/Side_Cued_TimeSeries_2.pdf}
-
-%   \caption{\textbf{Familiarity ratings over time for images that matched the
-%   cued or uncued image location.} This figure follows the same format and
-%   conventions as Figure~\ref{fig:familiarity_timecourse_category}.
-%   Figures~\timecourseCuedLocation~and \timecourseUncuedLocation~display these
-%   results broken down by participant cohort.}
-
-% \label{fig:familiarity_timecourse_location}
-% \end{figure*}
-
-% We next examined how participants' familiarity ratings varied over the duration
-% of the memory phases of each experiment as a function of the attended location.
-% Participants in the Sustained Attention Experiment rated attended-category
-% images as more familiar, at both the attended and unattended locations
-% (Fig.~\ref{fig:familiarity_timecourse_location}, left panels). In contrast,
-% participants in the Variable Attention Experiment rated attended-category
-% images as more familiar than unattended-category images only at the attended
-% locations (Fig.~\ref{fig:familiarity_timecourse_location}, right panels). The
-% primary difference in familiarity ratings between Sustained Attention
-% Experiment versus Variable Attention Experiment participants was in how they
-% rated unattended-category images. Participants in the Variable Attention Task
-% rated unattended-category images as more familiar than did participants in the
-% Sustained Attention Task; this pattern persisted throughout the memory phase
-% and held for images at both the attended and unattended locations (compare
-% heights of blue lines in the left versus right panels of
-% Fig.~\ref{fig:familiarity_timecourse_location}). This suggests that lower
-% familiarity ratings of unattended-category stimuli in the Sustained Attention
-% Experiment are due to suppression of the encoding of unattended-category
-% features (e.g., as opposed to enhancement of the encoding of attended-category
-% features). This suppression effect appears to build over an interval that is
-% longer than the duration of a single stimulus presentation (5.5~s).
-
-% \begin{figure*}[tp]
-%   \centering
-%   \includegraphics[width=1\textwidth]{figures/Novel_Timecourse_Panels.pdf}
-
-%   \caption{\textbf{Familiarity ratings over time for attended-category and
-%   unattended-category novel images.} The top panels of this figure follow the
-%   same formats and conventions as
-%   Figures~\ref{fig:familiarity_timecourse_category} and
-%   \ref{fig:familiarity_timecourse_location}. The bottom panels display the
-%   differences between the timecourses of familiarity ratings of
-%   attended-category and unattended-category novel stimuli. The error ribbons
-%   denote 95\% confidence intervals, computed across participants. The dotted
-%   horizontal line in each panel denotes a difference of 0-- i.e., the value
-%   above which attended-category novel images were rated as more familiar than
-%   unattended-category novel images. The black lines in the bottom panels
-%   display linear regression fits to the data (error ribbons denote 95\%
-%   confidence intervals). Figures~\timecourseNovel~and \timecourseDiff~display
-%   these results broken down by participant cohort.}
-
-% \label{fig:familiarity_timecourse_novel}
-% \end{figure*}
-
-% Finally, we examined how participants in both experiments rated the familiarity
-% of novel images. These ratings provide insights into how modulating the focus
-% of attention to \textit{prior} stimuli can affect the perception of
-% \textit{future} stimuli. We considered how participants rated novel stimuli
-% that matched versus did not match the category (face or scene) of the most
-% recent attention cue. Participants in the Sustained Attention Experiment rated
-% attended-category novel stimuli as more familiar than unattended-category novel
-% stimuli throughout the entire memory phase
-% (Fig.~\ref{fig:familiarity_timecourse_novel}a). By contrast, participants in
-% the Variable Attention Experiment rated attended-category and
-% unattended-category novel images similarly throughout the memory phase
-% (Fig.~\ref{fig:familiarity_timecourse_novel}b). The difference in familiarity
-% ratings between the two experiments primarily reflects that participants in the
-% Variable Attention Experiment rated unattended-category novel images as more
-% familiar than did participants in the Sustained Attention Experiment (e.g.,
-% compare blue lines in Fig.~\ref{fig:familiarity_timecourse_novel}a versus
-% \ref{fig:familiarity_timecourse_novel}b). This may indicate that the processing
-% of unattended-category novel stimuli is suppressed following sustained
-% attention (e.g., as opposed to enhancing the processing of attended-category
-% novel stimuli). The differences in familiarity between attended-category versus
-% unattended-category novel images increased slightly but reliably throughout the
-% memory phases of both experiments (Fig.~\ref{fig:familiarity_timecourse_novel},
-% bottom panels; slope of regression line fit to differences in Sustained
-% Attention Experiment: $\beta = 2.05 \times 10^{-3}, p = 1.07 \times 10^{-14} $;
-% slope of regression for Variable Attention Experiment: $\beta = 1.54 \times
-% 10^{-3}, p = 5.63 \times 10^{-13} $). This might reflect a process whereby the
-% suppression of unattended features continues to build for a short duration even
-% after the participant stops volitionally focusing on the attended features.
+Finally, we wondered whether participants' familiarity ratings might be
+influenced in part by response bias effects. For example, a participant who had
+recently received an ``attend to face images'' cue might rate a probed face
+images as more ``familiar'' even if they had no specific memories for the given
+image. Indeed, participants in the sustained attention condition do show some
+response biases. For example, participants tended to rate novel images as more
+familiar if they came from the just-cued category (Fig.~\responseBias A; $t(29)
+= 4.371, p < 0.001$). Responses biases are more difficult to evaluate in the
+variable attention condition. For example, should cue recency be defined as the
+number studied composite image pairs that came between the image whose
+familiarity the participant is judging and the most recent save-category cue
+(i.e., distance to the nearest same-category probe)? Or might response biases
+instead arise when a given category is cued more often near the end of the
+just-studied list? We assigned each probed image a label based on these two
+measures of category-matched cue recency. We then used linear regressions of
+familiarity on these recency measures to identify potential response biases
+(Fig.~\responseBias B). Altogether we found no evidence that participants in
+the variable attention condition tended to rate images as more familiar solely
+due to how recently they had received a same-category attention cue.
 
 \section*{Discussion}
+
+\textbf{JRM NOTE: STOPPED HERE}
 
@@
 between attention and memory~\citep{PallWagn02, ChunTurk07, AlyTurk16,
-AlyTurk17, WittEtal18, MorrEtal14, BaleEtal19}. Whereas much of this prior work
+AlyTurk17, WittEtal18, MorrEtal14, BaleEtal21}. Whereas much of this prior work
 focused on elucidating the neural basis of these interactions, our work extends
@@
 imaging or electroencephalography), and then using neural decoding
-approaches~\citep[e.g.,][]{HaxbEtal01, NormEtal06, MannEtal18} to follow how
+approaches~\citep[e.g.,][]{HaxbEtal01, NormEtal06b, MannEtal18} to follow how
 neural representations of attended (or unattended) stimuli are transfered from
@@
 \bibliographystyle{apacite}
-\bibliography{./CDL-bibliography/memlab}
+\bibliography{CDL-bibliography/cdl}
 

### 2023-03-26 paper/supplemental_materials.tex
finished draft of results section and supplement

@@
 
-%\begin{titlepage}
 \maketitle
-%\end{titlepage}
 
@@
 
-  \label{fig:intersections}
-  \end{figure*}
-
   \label{fig:gaze-histograms}
@@
 
+\begin{figure*}[tp]
+  \centering
+  \includegraphics[width=1\textwidth]{figs/sequence_length_effects}
+
+\caption{\textbf{Effects of attention cue sequence length on familiarity.} 
+\textbf{A. Sequence effects (sustained attention condition).} Each heatmap
+displays the proportions of images that participants rated at each familiarity
+rating (rows), broken down by the number of successive matching attention cues
+the participant received at the time the given image was presented as part of a
+composite pair (up to and including the image's composite pair; columns). The
+trend lines (with bootstrap-estimated 95\% confidence intervals) show
+regressions fit to the corresponding heatmap's data ($x$: sequence length; $y$:
+familiarity rating). Heatmaps are organized into rows based on how the sequence
+lengths were computed (top row: successive attention cues had the same category
+and location; middle row: successive attention cues had the same category;
+bottom row: successive attention cues had the same location). Columns (and
+colors) denote attention levels (as in Figs.~\familiarity~and
+\ref{fig:ratings-by-category}). \textbf{B. Sequence effects (variable attention
+condition).} This Panel is in the same format as Panel A, but displays results
+from the variable attention condition.}
+
+\label{fig:sequence-effects}
+\end{figure*}
+
+\begin{figure*}[tp]
+  \centering
+  \includegraphics[width=1\textwidth]{figs/response_bias.pdf}
+
+\caption{\textbf{Response bias analyses.} \textbf{A. Sustained attention
+condition.} The bars display the mean familiarity ratings participants gave to
+novel memory probes (lures) that matched (``True'') versus did not match
+(``False'') the prior run's attention-cued category. Error bars denote
+across-participant bootstrap-estimated 95\% confidence intervals. \textbf{B.
+Variable attention condition.} Each heatmap displays the proportions of images
+that participants rated at each familiarity rating (rows), broken down by
+metrics related to recent same-category attention cues participants received on
+the prior run (columns). The trend lines (with bootstrap-estimated 95\%
+confidence intervals) show regressions fit to the corresponding heatmap's data
+($x$: metrics related to same-category cues; $y$: familiarity rating). The top
+panels's columns reflect the temporal distances to the most recent
+same-category attention cues, measured in numbers of presented items (where 1
+denotes the final item on the most recent run). The bottom panel's columns
+denote the recency-weighted average numbers of same-category cues presented on
+the most recent run. Each column of matrices corresponds to a different
+attention level, as in Figures~\familiarity~and \ref{fig:ratings-by-category}.
+\textbf{C. Weights by recency.} The panel displays the weights used to compute
+recency-weighted numbers of same-category cues on the most recent run. The
+$x$-axis displays the presentation positions of each attention cue, and the
+$y$-axis displays the weight assigned to same-category cues at the given
+presentation position. The weights are first computed using $w = \max\left[1 -
+\exp\{-\frac{x}{\tau}\} , \epsilon \right]$, where $\tau = 2$, $\epsilon =
+0.05$, and $x$ is the cue's presentation position. To obtain the $y$-values
+shown in the Panel (and used in Panel B), the weights for $x \in \left[0, 1, 2,
+..., 9\right]$ are normalized to sum to 1.}
+
+\label{fig:response-bias}
+\end{figure*}
+
 \end{document}

### 2023-03-26 paper/main.tex
added discussion figure, backing up progress on discussion section [WIP]

@@
 0.001$), or novel images they had never seen before (sustained: $t(29) =
-10.259, p < 0.001$; variable: $t(22) = 7.874, p < 0.001$). We also observed a
-``boost'' in familiarity over novel images for attended \textit{or} unattended
-images from the cued category (sustained: $t(29) = 10.578, p < 0.001$;
-variable: $t(22) = 7.354, p < 0.001$) and location (sustained: $t(29) = 8.917,
-p < 0.001$; variable: $t(22) = 5.726, p < 0.001$).
+10.259, p < 0.001$; variable: $t(22) = 7.874, p < 0.001$).
 
@@
 people rated fully attended images ($t(51) = -0.649, p = 0.519$),
-attended-category (but not location) images ($t(51) = 1.163, p = 0.250$),
-unattended category and location images ($t(51) = -1.600, p = 0.116$), or novel
-images ($t(51) = -0.435, p = 0.665$) differently across the two conditions.
-However, participants in the variable attention condition rated
+attended-category (but not location) images ($t(51) = 1.163, p = 0.250$), or
+novel images ($t(51) = -0.435, p = 0.665$) differently across the two
+conditions. However, participants in the variable attention condition rated
 attended-location (but unattended category) images as more familiar than
 participants in the sustained attention condition ($t(51) = 2.174, p = 0.034$).
-This suggests that category-based versus location-based attention may operate
-over different timescales.
+We found a trending effect for unattended category and location images, whereby
+participants in the variable attention condition tended to rate these images as
+more familiar than participants in the sustained attention condition ($t(51) =
+1.600, p = 0.116$). We also observed some within-condition differences in how
+participants rated partially attended versus novel images. In the sustained
+attention condition, participants rated attended-category images at the
+unattended location as more familiar than novel images ($t(29) = 6.205, p <
+0.001$), but participants in the variable attention condition did not show this
+pattern ($t(22) = 1.042, p = 0.309$). On the other hand, whereas participants
+in the sustained attention condition showed no reliable differences in
+familiarity between attended-location images from the unattended category and
+novel images ($t(29) = 0.165, p = 0.870$), participants in the variable
+attention condition rated attended-location images as more familiar than novel
+images ($t(22) = 3.026, p = 0.006$). Taken together, our analyses highlight
+several familiarity differences in partially attended images from the attended
+category or at the attended location across the two experimental conditions.
+These differences suggest that category-based versus location-based attention
+operate over different timescales.
 
@@
 
-\textbf{JRM NOTE: STOPPED HERE}
+We ran a covert attention experiment with two conditions that asked
+participants to sustain or vary the focus of their covert attention,
+respectively. We then administered recognition memory tests that asked
+participants to rate the ``familiarity'' of attended, unattended, and novel
+images. In our analyses, we used eyetracking data to focus in on trials where
+participants were specifically varying their focus of \textit{covert} attention
+(i.e., with no change in external behavior), as opposed to simply moving their
+eyes to look at the to-be-attended images. In both conditions, we found that
+participants recognized images from the attended category and location more
+readily than unattended or novel images. This effect was substantial and robust
+(in both conditions) and also held for individual image categories. Whereas
+prior work has focused primarily on \textit{overt} changes in attention (e.g.,
+changes in eye movements associated with attention cues), we show that what
+people \textit{covertly} attend to also affects how they remember their ongoing
+experiences.  Specifically, covert attention appears to boost memory encoding
+such that the focus of covert attention is recognized more readily later on.
 
-We ran two covert attention experiments that asked participants to sustain or
-vary the focus of their covert attention, respectively. When participants held
-the focus of their feature-based (face versus scene) and location-based (left
-versus right) attention for a sustained interval, they judged stimuli they had
-seen as familiar when they overlapped with respect to the features and
-locations they had attended. The increase in familiarity was larger for
-attended-feature images than attended-location images. The increase also
-extended to novel stimuli from the attended image category. By contrast, when
-participants varied the focus of their feature-based and location-based
-attention more rapidly, the boost in familiarity for feature-matched stimuli
-was smaller than that for location-matched stimuli, and did not extend to novel
-stimuli. Our findings suggest that participants were able to more rapidly
-modulate their focus of location-based attention than their focus of
-feature-based attention. The tuning of location-based attention appears to be
-mediated by enhanced encoding and faster processing at the attended location.
-The tuning of feature-based attention appears to be mediated by a suppression
-in the encoding and processing of unattended stimulus features. This
-suppression effect also affects how new stimuli are processed, and it persists
-for a longer duration following an interval when the focus of feature-based
-attention was held constant over a longer duration. Taken together, our
-findings suggest that feature-based and location-based attention are mediated
-by different mechanisms and affect memory at different timescales
-(Fig.~\ref{fig:model}).
+\begin{figure*}[tp]
+  \centering \includegraphics[width=0.75\textwidth]{figs/discussion_schematic}
+
+  \caption{\textbf{How do covert location-based and category-based attention
+  affect memory encoding?}\textbf{A. Hypothesized timecourses of the impact of
+  location-based and category-based attention on memory encoding.} Shifting the
+  focus of location-based attention increases memory encoding at the attended
+  locations (blue curve). This increase can be observed after 5.5~s (the
+  duration of one presentation from the variable attention condition). Shifting
+  the focus of category-based attention suppresses memory encoding for the
+  unattended category. However, this suppression effect occurs relatively
+  slowly (longer than the duration of a single image presentation in the
+  experiment). \textbf{B. Location-based attention.} Focusing covert attention
+  on one \textit{location} enhances encoding of stimuli at the attended
+  location (red and yellow bars), regardless of stimulus category.  (This panel
+  is based on the variable attention results presented in Fig.~\ref{fig:familiarity}.)
+  \textbf{C. Category-based attention.}  Focusing covert attention on one \textit{category}
+  supresses encoding of stimuli from the unattended category (yellow and green bars),
+  regardless of spatial location.  (This panel is based on the sustained attention
+  results presented in Fig.~\ref{fig:familiarity}.)}
+
+\label{fig:discussion}
+\end{figure*}
+
+We also found that partially attended images (e.g., from the attended category
+but unattended location, or at the attended location but unattended category)
+were rated as more familiar than novel images. However, these encoding benefits
+differed across the two experimental conditions. In the sustained attention
+condition, attended-category images from the unattended location were rated as
+more familiar than novel images, but attended-location images from the
+unattended category were not. Participants in the variable attention condition
+showed the opposite pattern. The variable attention participants rated
+attended-\textit{location} images from the unattended category as more familiar
+than novel images, but they rated attended-category images from the unattended
+location similarly to novel images. Because the primary difference between the
+sustained and variable attention conditions was the duration of the attention
+cues, our analyses of partially attended images suggest that the effects of
+different aspects of attention on memory may unfold over different timescales
+(Fig.~\ref{fig:discussion}). Specifically, location-based attention appears to
+affect memory encoding relatively quickly, which would explain why
+attended-location images from both the attended \textit{and} unattended
+category receive a memory encoding benefit in the variable attention condition.
+In contrast, category-based attention appears to affect memory encoding more
+slowly, and it appears to operate in a ``suppressive'' manner (i.e., supressing
+encoding of the unattended category, as opposed to enhancing encoding of the
+attended category). This would explain why unattended-category images at the
+attended location are rated as \textit{less} familiar in the sustained
+attention condition.
+
+\textbf{JRM STOPPED HERE}
+
+When participants held the focus of their category-based (face
+versus place) and location-based (left versus right) attention for a sustained
+interval, they judged stimuli they had seen as familiar when they overlapped
+with respect to the features and locations they had attended. The increase in
+familiarity was larger for attended-feature images than attended-location
+images. The increase also extended to novel stimuli from the attended image
+category. By contrast, when participants varied the focus of their
+feature-based and location-based attention more rapidly, the boost in
+familiarity for feature-matched stimuli was smaller than that for
+location-matched stimuli, and did not extend to novel stimuli. Our findings
+suggest that participants were able to more rapidly modulate their focus of
+location-based attention than their focus of feature-based attention. The
+tuning of location-based attention appears to be mediated by enhanced encoding
+and faster processing at the attended location. The tuning of feature-based
+attention appears to be mediated by a suppression in the encoding and
+processing of unattended stimulus features. This suppression effect also
+affects how new stimuli are processed, and it persists for a longer duration
+following an interval when the focus of feature-based attention was held
+constant over a longer duration. Taken together, our findings suggest that
+feature-based and location-based attention are mediated by different mechanisms
+and affect memory at different timescales (Fig.~\ref{fig:model}).
 

### 2023-03-26 paper/main.tex
finished complete draft of discussion section

@@
 
-\textbf{JRM STOPPED HERE}
-
-When participants held the focus of their category-based (face
-versus place) and location-based (left versus right) attention for a sustained
-interval, they judged stimuli they had seen as familiar when they overlapped
-with respect to the features and locations they had attended. The increase in
-familiarity was larger for attended-feature images than attended-location
-images. The increase also extended to novel stimuli from the attended image
-category. By contrast, when participants varied the focus of their
-feature-based and location-based attention more rapidly, the boost in
-familiarity for feature-matched stimuli was smaller than that for
-location-matched stimuli, and did not extend to novel stimuli. Our findings
-suggest that participants were able to more rapidly modulate their focus of
-location-based attention than their focus of feature-based attention. The
-tuning of location-based attention appears to be mediated by enhanced encoding
-and faster processing at the attended location. The tuning of feature-based
-attention appears to be mediated by a suppression in the encoding and
-processing of unattended stimulus features. This suppression effect also
-affects how new stimuli are processed, and it persists for a longer duration
-following an interval when the focus of feature-based attention was held
-constant over a longer duration. Taken together, our findings suggest that
-feature-based and location-based attention are mediated by different mechanisms
-and affect memory at different timescales (Fig.~\ref{fig:model}).
-
-% \begin{figure*}[tp]
-%   \centering \includegraphics[width=0.75\textwidth]{figures/discussion_schematic}
-
-%   \caption{\textbf{Timecourse of encoding and retrieval effects of
-%   feature-based and location-based attention.} The focus of location-based
-%   attention (green) may be modulated quickly and rapidly enhances memory
-%   encoding for nearby stimuli. The focus of feature-based attention (purple) is
-%   modulated more slowly, and serves to suppress unattended stimulus features.
-%   The effects of location-based attention on memory persist for longer than the
-%   effects of feature-based attention. Sustained attention (darker shading)
-%   yields more robust enhancement and suppression than shorter-term (variable)
-%   attention (light shading). The vertical gray line on the left denotes the
-%   duration of a single stimulus presentation (the upper bound by which
-%   location-based attention begins to affect encoding, and the lower-bound by
-%   which feature-based attention begins to affect encoding). The vertical gray
-%   line on the right separates encoding from immediate subsequent retrieval of
-%   the encoded information.}
-
-% \label{fig:model}
-% \end{figure*}
-
 The notion that location-based attention operates at a faster timescale than
-feature-based attention is supported by prior work on the deployment of visual
+category-based attention is supported by prior work on the deployment of visual
 attention~\citep{SotoBlan04, StopEtal07}. Our findings that location-based
-attention enhances the processing of attended stimuli whereas feature-based
+attention enhances the processing of attended stimuli whereas category-based
 attention suppresses the processing of unattended stimuli is also consistent
 with prior work on location-based attention~\citep[e.g.,][]{IttiKoch01} and
-feature-based attention~\citep[e.g.,][]{MoheEtal14}. Our finding that people
+category-based attention~\citep[e.g.,][]{MoheEtal14}. Our finding that people
 better remember attended stimuli also follows prior work on interactions
@@
 these prior studies by elucidating the specific and separable behavioral
-impacts of feature-based attention (inhibition with a slow onset) and
-location-based attention (enhancement with a fast onset) on subsequent memory.
-Both of these effects persisted throughout the 2~min memory phases of both
-experiments. Therefore future work is needed to elucidate the longevity of
-these effects beyond 2 minutes.
+impacts of location-based attention (enhancement with a fast onset) and
+category-based attention (inhibition with a slow onset) and on subsequent
+recognition memory. Both of these effects persisted throughout the 2~min memory
+phases of both experiments. Therefore future work is needed to elucidate the
+longevity of these effects beyond 2 minutes.
 
@@
 representations~\citep{VartEtal07, LaRoEtal14}. Prior work suggests that
-feature-based attention may be supported by changes in connectivity with the
+category-based attention may be supported by changes in connectivity with the
 thalamus~\citep{Schn11}, whereas location-based attention may be supported by
 changes in connectivity with primary visual cortex~\citep{NoudEtal10}. That
-feature-based and location-based attention are mediated by different brain
+category-based and location-based attention are mediated by different brain
 structures may explain why these different aspects of attention operate on
@@
 imaging or electroencephalography), and then using neural decoding
-approaches~\citep[e.g.,][]{HaxbEtal01, NormEtal06b, MannEtal18} to follow how
-neural representations of attended (or unattended) stimuli are transfered from
-primary sensory regions, to higher order sensory regions, to memory areas. If
-the effects of attention on memory are mediated by changes in network dynamics,
-the transmission rates of the representations of attended stimuli from primary
-sensory regions to memory areas should be facilitated relative to the
-transmission rates of unattended stimuli. Further, variability in these neural
-changes (e.g., as a participant focuses their attention with more or less
-success) should track with behavioral measures of memorability.
+approaches~\citep[e.g.,][]{HaxbEtal01, NormEtal06b, MannEtal18, OwenEtal21} to
+follow how neural representations of attended (or unattended) stimuli are
+transfered from primary sensory regions, to higher order sensory regions, to
+memory areas. If the effects of attention on memory are mediated by changes in
+network dynamics, the transmission rates of the representations of attended
+stimuli from primary sensory regions to memory areas should be facilitated
+relative to the transmission rates of unattended stimuli. Further, variability
+in these neural changes (e.g., as a participant focuses their attention with
+more or less success) should track with behavioral measures of memorability.
 
@@
 process and remember those experiences later. Different forms of
-attention---e.g., to specific features or spatial locations---operate and
-affect memory at different timescales, and are likely mediated by different
-brain networks. Elucidating the behavioral and neural consequences of
-volitional changes in attention is central to discovering how our thoughts,
-feelings, goals, and situational understanding fluctuate from moment to moment.
+attention---e.g., to specific stimulus categories or spatial
+locations---operate and affect memory at different timescales, and are likely
+mediated by different brain networks. Elucidating the behavioral and neural
+consequences of volitional changes in attention is central to discovering how
+our thoughts, feelings, goals, and situational understanding fluctuate from
+moment to moment.
 

### 2023-03-26 paper/main.tex
minor formatting fixes

@@
 
-\author{Kirsten Ziman$^1, 2$,
+\author{Kirsten Ziman\textsuperscript{$1, 2$},
 Madeline R. Lee$^1$,
@@
 encoding~\citep[i.e., they rated attended images as more familiar than
-unattended images][]{Yone02}. After maintaining the focus of attention to a
+unattended images;][]{Yone02}. After maintaining the focus of attention to a
 single image category and location (Sustained Attention Experiment),

### 2023-03-27 paper/main.tex
complete draft-- ready for review!

@@
 \usepackage{hyperref}
-\usepackage{natbib}
+\usepackage[sort]{natbib}
 \usepackage{pxfonts}
@@
 and
-Jeremy R. Manning\textsuperscript{$1, \dagger$}\\[0.1in]$^1$Dartmouth College\\
+Jeremy R. Manning\textsuperscript{$1, *$}\\[0.1in]$^1$Dartmouth College\\
 $^2$Princeton University\\
-\textsuperscript{$\dagger$}Address correspondence to jeremy.r.manning@dartmouth.edu}
+\textsuperscript{*}Address correspondence to jeremy.r.manning@dartmouth.edu}
 
@@
 
-\noindent\textbf{Keywords: covert attention, spatial attention, category-based
-attention, recognition memory, perception}
+\noindent\textbf{Keywords: covert attention, volitional attention,
+location-based attention, category-based attention, recognition memory}
 
@@
 to a given setting or situation~\citep{ChunTurk07, AlyTurk17, HardNade09,
-RangRitc12}. There is also substantial variability across people with respect
+RangRitc12, JayaEtal23, HirsAly22, deBeEtal21, KeenEtal22, HakiEtal20,
+AdamdeBe19}. There is also substantial variability across people with respect
 to which aspects of experience (sensory, social, emotional, etc.) are noticed,
@@
 manipulate our experience, even when our sensory input remains largely
-static~\citep[i.e., constant physical stimuli, retinal image, etc.][]{YiEtal06,
+static~\citep[i.e., constant physical stimulus, retinal image, etc.;][]{YiEtal06,
 OcraEtal99}.
 
-Here we examine the ways different types of volitional covert attention
+Here we examine the ways two different types of volitional covert attention
 interact to affect memory. We designed an experimental
@@
 central point. The image pairs comprised a left and right image, each
-constructed by blending an image of a face and place. The stimuli and
-presentation durations were constant across the two experiments, but the
-experiments differed in how often we asked participants to change the focus of
-their attention with respect to image category (face versus place) and image
-location (left versus right). After the participants attended to a series of
-images, we used a recognition memory test to assess which aspects of the
-presented images had been encoded into memory. In both experiments we found
-that the images participants covertly attended to were better recognized than
-other images, supporting the notion that attention enhances memory
-encoding~\citep[i.e., they rated attended images as more familiar than
-unattended images;][]{Yone02}. After maintaining the focus of attention to a
-single image category and location (Sustained Attention Experiment),
-participants also recognized the attended-category image at the unattended
-location, and (to a lesser extent) the unattended-category image at the
-attended location. After more rapidly varying their focus of attention
-(Variable Attention Experiment), participants showed a similar boost in
-recognition for the unattended-category image at the attended location, but
-they did not recognize images at the unattended location. This suggests that
-participants were able to shift the location of their covert attentional focus
-more rapidly than they were able to shift their focus of covert attention to
-stimulus features. We also found differences in the timecourses of these memory
-effects, suggesting that the impact of location-based attention on memory
-persists on the order of several seconds longer than the impact of
-feature-based attention.
+constructed by blending an image of a face and place (indoor or outdoor scene).
+The stimuli and presentation durations were held constant across the two
+experimental conditions, but the conditions differed in how often we asked
+participants to change the focus of their attention with respect to image
+category (face versus place) and image location (left versus right). After the
+participants attended to a series of images, we used a recognition memory test
+to assess which aspects of the presented images had been encoded into memory.
+In both conditions we found that the images participants covertly attended to
+were better recognized than other images, supporting the notion that attention
+enhances memory encoding~\citep[i.e., they rated attended images as more
+familiar than unattended images;][]{Yone02}. To a lesser extent, participants
+in both conditions also recognized partially attended images (e.g., images from
+the attended category but unattended location, or images at the attended
+location but from the unattended category). However, the ways the
+category-based and location-based attention affected participants' memories for
+these partially attended stimuli differed across the two experimental conditions.
+These partial attention differences suggest that different forms of attention
+affect memory encoding on different timescales.
 
@@
 cued participants to change the focus of their attention. All code and
-documentation pertaining to our experiments and analyses, along with the
+documentation pertaining to our experiment and analyses, along with the
 experimental stimuli and data, may be downloaded from
@@
   in sequence (Panel F). \textbf{G. Variable attention condition.} Participants
-  study a succession of 10 composite image pairs, each preceded by an attention cue.
-  After studying the images, they make a series of 40 familiarity judgements about
-  face and place images, as in the sustained attention condition (Panel F).}
+  study a succession of 10 composite image pairs, each preceded by an attention
+  cue. After studying the images, they make a series of 40 familiarity
+  judgements about face and place images, as in the sustained attention
+  condition (Panel F). Note: illustrations are not drawn to scale; see the main
+  text for sizing information.}
 
@@
 condition). Following a pilot study using a similar experimental design, we
-aimed to enroll 30 participants in each condition. However, we fell short of
+had aimed to enroll 30 participants in each condition. However, we fell short of
 our enrollment target in the variable attention condition when in-person
-testing was discontinued at our institution due to the COVID-19 pandemic. All
-participants had self-reported normal or corrected-to-normal vision, memory,
-and attention. Participants gave written consent to enroll in the study under a
-protocol approved by the Committee for the Protection of Human Subjects at
-Dartmouth College.
+testing was discontinued at our institution due to the COVID-19 pandemic. We
+nonetheless chose to analyze and report on our findings from this
+smaller-than-anticipated cohort of participants using all of the viable data we
+were able to collect. All participants in our study had self-reported normal or
+corrected-to-normal vision, memory, and attention. Participants gave written
+consent to enroll in the study under a protocol approved by the Committee for
+the Protection of Human Subjects at Dartmouth College.
 
@@
 18.7 years; standard deviation: 0.8 years). Participants reported their genders
-as female (34 particiapnts), male (18 participants), and gender non-binary (1
+as female (34 participants), male (18 participants), and gender non-binary (1
 participant). Participants reported their ethnicities as Not Hispanic or Latino
-(44 particiapnts), Hispanic or Latino (7 participants), or declined to respond
-(2 participant). Participants reported their race as White (37 participants),
+(44 participants), Hispanic or Latino (7 participants), or declined to respond
+(2 participants). Participants reported their race as White (37 participants),
 Asian (13 participants), American Indian or Alaska Native (4 participants),
@@
 
-Fourty-nine participants reported having no reading impairments, and 4
-participants reported having reading impairments such as dyslexia. Fifty
+Forty-nine participants reported having no reading impairments, and 4
+participants reported having reading impairments such as mild dyslexia. Fifty
 participants reported having normal color vision and 3 reported having abnormal
@@
 had recently ``hit [their] head very hard.'' Another reported having taken
-concerta in the past, but mentioned they had not taken it recently. One
-participant reported using amphetamines regularly, but also clarified that they
-were not currently on amphetamines at the time of testing.
+concerta (methylphenidate) in the past, but mentioned they had not taken it
+recently. One participant reported using amphetamines regularly, but also
+clarified that they had not used amphetamines on their testing day.
 
@@
 points), and ``Very sluggish'' (1 point). Across all participants, the full
-range of alertness values were used (maximum: 5; minimum: 1; mean: 3.44;
-standard deviation: 1.0). Participants reported having consumed between 0 and 2
-cups of coffee so far on their testing day (mean: 0.3 cups; standard deviation:
-0.5 cups).
+range of alertness values were used (maximum: 5 points; minimum: 1 point; mean:
+3.4 points; standard deviation: 1.0 point). Participants reported having
+consumed between 0 and 2 cups of coffee so far on their testing day (mean: 0.3
+cups; standard deviation: 0.5 cups).
 
@@
 and intensity. We selected 20 face images and 20 place images from the stimulus
-pool to use in the instructional and practice phases of the experiments
+pool to use in the instructional and practice phases of the experiment
 (Fig.~\ref{fig:paradigm}A--D).
@@
  sized to occupy $6.7^\circ$ (width and height) of the participant's field of
- view from the chin rest. We maintained a black background (with any text
- displayed in white) throughout the experiment.
+ view from the chin rest. We maintained a black background (with any text or
+ cues displayed in white) throughout the experiment.
 
-\subsection*{Eyetracking}
+\subsection*{Eye-tracking}
 
 We recorded participants' eye gaze positions using a desk-mounted video-based
-eyetracker with a spatial resolution of 0.1$^\circ$ visual angle root mean
+eye tracker with a spatial resolution of 0.1$^\circ$ visual angle root mean
 squared error and a sampling rate of 30~Hz (Eye Tribe, The Eye Tribe,
-Copenhagen, Denmark). We calibrated the eyetracker using a 9-point gaze
-pattern. As described below, we re-calibrated the eyetracker at regular
+Copenhagen, Denmark). We calibrated the eye tracker using a 9-point gaze
+pattern. As described below, we re-calibrated the eye tracker at regular
 intervals throughout the experiment to protect against camera drift.
 
-We used the eyetracking data to home in specifically on behavioral effects
+We used the eye-tracking data to home in specifically on behavioral effects
 related to \textit{covert} attention, as opposed to overt looking effects.
@@
 memory phase. The practice and presentation phases differed across the two
-experiments, and the memory phases were identical across the two experiments.
-Both experiments were implemented using PsychoPy~\citep{PeirEtal19}.
+conditions, and the memory phases were identical across the two conditions.
+We implemented (coded) the experiment using PsychoPy~\citep{PeirEtal19}.
 
@@
 
-Several participants in pilot versions of our experiments reported that they
-found it difficult to modulate the focus of their attention quickly on command.
-We therefore designed a practice sequence to orient the participant to the
-process of quickly modulating the focus of their attention without moving their
-eyes. The experimenter remained in the testing room throughout the practice
-phase and answered any questions about the experiment. The practice sequence
-builds up incrementally to provide a gradual on-ramping for the participant
-prior to beginning the main experimental tasks that we focused on in our
-analyses.
+Several participants in pilot versions of our experiment reported that they
+found it difficult to modulate the focus of their attention quickly on command
+without moving their eyes. We therefore designed a practice sequence to orient
+the participant to the process of quickly modulating their focus of covert
+attention. The experimenter remained in the testing room throughout the
+practice phase and answered any questions about the experiment. The practice
+sequence builds up incrementally to provide a gradual on-ramping for the
+participant prior to beginning the main experimental tasks that we focused on
+in our analyses.
 
@@
 After answering the participant's questions, the experimenter calibrated the
-eyetracker and exited the testing room.
+eye tracker and exited the testing room.
 
@@
 a fixation cross (1~s), composite image (3~s), and a reaction time probe. The
-attention cues were selected pseudorandomly across trials within each block,
-with the constraints that no single attention cue pair could appear more than
-three times across the 10 composite image pairs within a single task block.
+attention cues were selected randomly across trials within each block.
 
@@
 (10 faces and 10 places) were novel images that the participant had not
-encountered during any part of the experiment. At the end of each memory block,
+encountered during any part of the experiment. At the end of each memory phase,
 the participant was given the opportunity to take a short break. When they were
@@
 the experimenter. The experimenter then entered the testing room, re-ran the
-eyetracker calibration sequence, and exited the testing room prior to the next
+eye tracker calibration sequence, and exited the testing room prior to the next
 task block.
@@
 any images presented during trials where the participant's gaze touched on any
-part of the attended composite image (see \textit{Eyetraciking},
+part of the attended composite image (see \textit{Eye-tracking},
 Figs.~\gazeLocations~and \excludedTrials). For the remaining trials, the
@@
 screen while \textit{covertly} shifting the focus of their attention to the
-cued category component of the composite image on the cued location. In other
+cued category component of the composite image at the cued location. In other
 words, during these remaining trials, participants' physical (external)
@@
 remained relatively constant across trials (up to our ability to accurately
-measure where participants were looking using the eyetracker).
+measure where participants were looking using the eye tracker).
 
@@
 0.001$) and variable ($t(22) = 5.144, p < 0.001$) conditions. In addition, to
-the extent that participants were following the attention cues, there
+the extent that participants were following the attention cues, their
 \textit{internal} experiences of each image should depend on their internal
@@
 images might depend on image-specific properties like the images' categories.
-We repeated the analyis displayed in Figure~\ref{fig:familiarity} separately
+We repeated the analysis displayed in Figure~\ref{fig:familiarity} separately
 for face and place images (Fig.~\ratingsByCategory). The same general patterns
-held for each category, as when we combined across the two stimulus categories
-as reported above. For example, fully attended face and place images were both
-rated as more familiar than the category-matched images from the unattended
-location (sustained: $t$s$(29) \geq 3.36, p$s$ \leq 0.002$; variable: $t$s$(22)
-\geq 6.205, p$s$ \leq 0.001$), attended-location images from the unattended
-category (sustained: $t$s$(29) \geq 5.886, p$s$ \leq 0.001$; variable:
-$t$s$(29) \geq 4.277, p$s$ \leq 0.001$), images from the unattended category
-and location (sustained: $t$s$(29) \geq 6.628, p$s$ \leq 0.001$; variable:
-$t$s$(29) \geq 5.624, p$s$ \leq 0.001$), and novel images (sustained: $t$s$(29)
-\geq 5.987, p$s$ \leq 0.001$; variable: $t$s$(29) \geq 5.132, p$s$ \leq
-0.001$). Taken together, the above results suggest that what we remember is
-guided in part by what we attended to, even after accounting for where we look
-or what specifically we are looking at.
+reported above also held for each stimulus category individually. For example,
+fully attended face and place images were both rated as more familiar than the
+category-matched images from the unattended location (sustained: $t$s$(29) \geq
+3.366, p$s$ \leq 0.002$; variable: $t$s$(22) \geq 4.773, p$s$ \leq 0.001$),
+attended-location images from the unattended category (sustained: $t$s$(29)
+\geq 5.886, p$s$ \leq 0.001$; variable: $t$s$(29) \geq 4.277, p$s$ \leq
+0.001$), images from the unattended category and location (sustained: $t$s$(29)
+\geq 6.628, p$s$ \leq 0.001$; variable: $t$s$(29) \geq 5.624, p$s$ \leq
+0.001$), and novel images (sustained: $t$s$(29) \geq 5.987, p$s$ \leq 0.001$;
+variable: $t$s$(29) \geq 5.132, p$s$ \leq 0.001$). Taken together, the above
+results suggest that what we remember is guided in part by what we attended to,
+even after accounting for where we look or what specifically we are looking at.
 
-Splitting participants' responses to face versus place images also revealted
+Splitting participants' responses to face versus place images also revealed
 that participants often rated attended (and partially attended) place images as
@@
 eyes, nose, mouth, head shape, etc.), the average place image does not show
-place-specific features as clearly, aside from a general tendancy for the tops
+place-specific features as clearly, aside from a general tendency for the tops
 of place images to be lighter than the bottoms of place images. We also
@@
 category or at the attended location across the two experimental conditions.
-These differences suggest that category-based versus location-based attention
+These differences suggest that the aspects of category-based versus
+location-based attention that affect how people remember what they attend
 operate over different timescales.
@@
   denotes the position of each probed image within the sequence of 40 images
-  that participants judged during the memory phase of the experiemnt. The
+  that participants judged during the memory phase of the experiment. The
   $y$-axis denotes the average familiarity ratings given to the corresponding
@@
 shown in Figure~\sequenceLength, we used linear regressions of familiarity
-rating on sequence lengths to identify potential sequence length effects. For
+ratings on sequence lengths to identify potential sequence length effects. For
 both experimental conditions, all attention levels, and for all three
@@
 reliable associations between cue sequence length and familiarity. This finding
-is most parsimonious with the first possiblity mentioned above-- i.e., that
+is most parsimonious with the first possibility mentioned above-- i.e., that
 attention may be guided by a brief trigger, but that different forms of
@@
 influenced in part by response bias effects. For example, a participant who had
-recently received an ``attend to face images'' cue might rate a probed face
-images as more ``familiar'' even if they had no specific memories for the given
-image. Indeed, participants in the sustained attention condition do show some
-response biases. For example, participants tended to rate novel images as more
-familiar if they came from the just-cued category (Fig.~\responseBias A; $t(29)
-= 4.371, p < 0.001$). Responses biases are more difficult to evaluate in the
-variable attention condition. For example, should cue recency be defined as the
-number studied composite image pairs that came between the image whose
-familiarity the participant is judging and the most recent save-category cue
-(i.e., distance to the nearest same-category probe)? Or might response biases
-instead arise when a given category is cued more often near the end of the
-just-studied list? We assigned each probed image a label based on these two
-measures of category-matched cue recency. We then used linear regressions of
-familiarity on these recency measures to identify potential response biases
+recently received an ``attend to face images'' cue might rate even a novel face
+image as more ``familiar'' if they leveraged their memory of the attention cue
+(as opposed to solely relying on their memories of the composite images they
+studied) to help guide their familiarity ratings. Indeed, participants in the
+sustained attention condition do show some response biases. For example,
+participants tended to rate novel images as more familiar if they came from the
+just-cued category (Fig.~\responseBias A; $t(29) = 4.371, p < 0.001$).
+Responses biases are more difficult to evaluate in the variable attention
+condition. For example, should cue recency be defined as the number studied
+composite image pairs that came between the image whose familiarity the
+participant is judging and the most recent same-category cue (i.e., distance to
+the nearest same-category attention cue)? Or might response biases instead
+arise when a given category is cued more often near the end of the just-studied
+list? We assigned each probed image a label based on these two measures of
+category-matched cue recency. We then used linear regressions of familiarity
+ratings on these recency measures to identify potential response biases
 (Fig.~\responseBias B). Altogether we found no evidence that participants in
@@
 participants to rate the ``familiarity'' of attended, unattended, and novel
-images. In our analyses, we used eyetracking data to focus in on trials where
+images. In our analyses, we used eye-tracking data to focus in on trials where
 participants were specifically varying their focus of \textit{covert} attention
-(i.e., with no change in external behavior), as opposed to simply moving their
-eyes to look at the to-be-attended images. In both conditions, we found that
-participants recognized images from the attended category and location more
-readily than unattended or novel images. This effect was substantial and robust
-(in both conditions) and also held for individual image categories. Whereas
-prior work has focused primarily on \textit{overt} changes in attention (e.g.,
-changes in eye movements associated with attention cues), we show that what
-people \textit{covertly} attend to also affects how they remember their ongoing
-experiences.  Specifically, covert attention appears to boost memory encoding
-such that the focus of covert attention is recognized more readily later on.
+(i.e., with no change in where they were looking), as opposed to simply moving
+their eyes to look at the to-be-attended images. In both conditions, we found
+that participants recognized images from the attended category and location
+more readily than unattended or novel images. This effect was substantial and
+robust (in both conditions) and also held for individual image categories.
+Whereas prior work has focused primarily on \textit{overt} changes in attention
+(e.g., changes in eye movements associated with attention cues), we show that
+what people \textit{covertly} attend to also affects how they remember their
+ongoing experiences. Specifically, covert attention appears to boost memory
+encoding such that the focus of covert attention is recognized more readily
+later on.
 
@@
   \caption{\textbf{How do covert location-based and category-based attention
-  affect memory encoding?}\textbf{A. Hypothesized timecourses of the impact of
+  affect memory encoding?}\textbf{A. Hypothesized time courses of the impact of
   location-based and category-based attention on memory encoding.} Shifting the
@@
   location (red and yellow bars), regardless of stimulus category. (This panel
-  is based on the variable attention results presented in Fig.~\ref{fig:familiarity}.)
-  \textbf{C. Category-based attention.}  Focusing covert attention on one \textit{category}
-  supresses encoding of stimuli from the unattended category (yellow and green bars),
-  regardless of spatial location.  (This panel is based on the sustained attention
-  results presented in Fig.~\ref{fig:familiarity}.)}
+  is based on the variable attention results presented in
+  Fig.~\ref{fig:familiarity}.) \textbf{C. Category-based attention.} Focusing
+  covert attention on one \textit{category} suppresses encoding of stimuli from
+  the unattended category (yellow and green bars), regardless of spatial
+  location. (This panel is based on the sustained attention results presented
+  in Fig.~\ref{fig:familiarity}.)}
 
@@
 location similarly to novel images. Because the primary difference between the
-sustained and variable attention conditions was the duration of the attention
-cues, our analyses of partially attended images suggest that the effects of
-different aspects of attention on memory may unfold over different timescales
-(Fig.~\ref{fig:discussion}). Specifically, location-based attention appears to
-affect memory encoding relatively quickly, which would explain why
+sustained and variable attention conditions was the duration of participants'
+focus of attention, our analyses of partially attended images suggest that the
+effects of different aspects of attention on memory may unfold over different
+timescales (Fig.~\ref{fig:discussion}). Specifically, location-based attention
+appears to affect memory encoding relatively quickly, which would explain why
 attended-location images from both the attended \textit{and} unattended
@@
 In contrast, category-based attention appears to affect memory encoding more
-slowly, and it appears to operate in a ``suppressive'' manner (i.e., supressing
-encoding of the unattended category, as opposed to enhancing encoding of the
-attended category). This would explain why unattended-category images at the
-attended location are rated as \textit{less} familiar in the sustained
-attention condition.
+slowly, and it appears to operate in a ``suppressive'' manner (i.e.,
+suppressing encoding of the unattended category, as opposed to enhancing
+encoding of the attended category). This would explain why unattended-category
+images at the attended location are rated as \textit{less} familiar in the
+sustained attention condition.
 
@@
 recognition memory. Both of these effects persisted throughout the 2~min memory
-phases of both experiments. Therefore future work is needed to elucidate the
+phases of both conditions. Therefore future work is needed to elucidate the
 longevity of these effects beyond 2 minutes.
@@
 All of the data analyzed in this manuscript, along with all of the code for
-running our experiment and carying out the analyses may be found at
+running our experiment and carrying out the analyses may be found at
 \url{http://www.github.com/ContextLab/attention-memory-task}.
@@
 Christina Liu and Eowyn Pak for their help running pilot versions of the
-experiments reported here.
+experiment reported here.
 

### 2023-03-27 paper/supplemental_materials.tex
minor formatting fixes
complete draft-- ready for review!

@@
 
-\title{Supporting Materials for \textit{Category-based and location-based volitional covert attention affect
+\title{Supplemental materials for \textit{Category-based and location-based volitional covert attention affect
 memory at different timescales}}
 
-\author{Kirsten Ziman$^1, 2$,
+\author{Kirsten Ziman\textsuperscript{$1, 2$},
 Madeline R. Lee$^1$,
@@
 proportions of presentations across different runs where the given
-pariticapants looked at any part of the attended composite image, for any
+participants looked at any part of the attended composite image, for any
 non-zero duration. Error bars denote across-run bootstrap-estimated 95\%
@@
 \caption{\textbf{Effects of attention cue sequence length on familiarity.} 
-\textbf{A. Sequence effects (sustained attention condition).} Each heatmap
+\textbf{A. Sequence effects (sustained attention condition).} Each heat map
 displays the proportions of images that participants rated at each familiarity
@@
 regressions fit to the corresponding heatmap's data ($x$: sequence length; $y$:
-familiarity rating). Heatmaps are organized into rows based on how the sequence
+familiarity rating). Heat maps are organized into rows based on how the sequence
 lengths were computed (top row: successive attention cues had the same category
@@
 across-participant bootstrap-estimated 95\% confidence intervals. \textbf{B.
-Variable attention condition.} Each heatmap displays the proportions of images
+Variable attention condition.} Each heat map displays the proportions of images
 that participants rated at each familiarity rating (rows), broken down by

### 2023-03-27 code/helpers.py

@@ -191,9 +191,9 @@ def parse_gaze_data(datadir):
 
 
 def intersect_image(xs, ys):
-    im_len = 59.8 / 2 - 9
+    im_len = 6.7 * (52.96 / 59.8)
     y = (33.6 - im_len) / 2
-    x1 = 4.5
+    x1 = (59.8 / 2) - 4.5 - im_len
     x2 = (59.8 / 2) + 4.5
 
     xs = np.array(xs)

### 2023-03-27 paper/main.tex
minor wording tweaks, typo and formatting fixes

@@
 shaped by our prior experiences, goals, and situational understanding. These
-factors shape how we allocate our attentional resources over different aspects
-of our ongoing experiences. These attentional shifts may happen overtly (e.g.,
-when we change where we are looking) or covertly (e.g., without any explicit
-physical manifestation). Additionally, we may attend to what is happening at a
-specific spatial location (e.g., because we think something important is
-happening there) or we may attend to particular features irrespective of their
-locations (e.g., when we search for a friend's face in a crowd versus a
-location on a map). We ran a covert attention experiment with two conditions
-that differed in how long they asked participants to maintain the focus of the
-categories and locations they were attending. Later, the participants performed
-a recognition memory task for attended, unattended, and novel stimuli.
-Participants were able to shift the location of their covert attentional focus
-more rapidly than they were able to shift their focus of covert attention to
-stimulus categories, and the effects of location-based attention on memory were
-longer-lasting than the effects of category-based attention.
+factors influence how we allocate our attentional resources over different
+aspects of our ongoing experiences. These attentional shifts may happen overtly
+(e.g., when we change where we are looking) or covertly (e.g., without any
+external physical manifestation). Additionally, we may attend to what is
+happening at a specific spatial location (e.g., because we think something
+important is happening there) or we may attend to particular features
+irrespective of their locations (e.g., when we search for a friend's face in a
+crowd versus a desired item in a grocery store). We ran a covert attention
+experiment with two conditions that differed in how long they asked
+participants to maintain the focus of the categories and locations they were
+attending. Later, the participants performed a recognition memory task for
+attended, unattended, and novel stimuli. Participants were able to shift the
+location of their covert attentional focus more rapidly than they were able to
+shift their focus of covert attention to stimulus categories, and the effects
+of location-based attention on memory were longer-lasting than the effects of
+category-based attention.
 
@@
 
-We ran a total of 53 participants in across two experimental conditions
-(Fig.~\ref{fig:paradigm}). The two conditions differed in how often we
-cued participants to change the focus of their attention. All code and
-documentation pertaining to our experiment and analyses, along with the
-experimental stimuli and data, may be downloaded from
+We ran a total of 53 participants across two experimental conditions
+(Fig.~\ref{fig:paradigm}). The two conditions differed in how often we cued
+participants to change the focus of their attention. All code and documentation
+pertaining to our experiment and analyses, along with the experimental stimuli
+and data, may be downloaded from
 \url{http://www.github.com/ContextLab/attention-memory-task}.
@@
 selected from the FERET database~\citep{PhilEtal98}. The pool of 360 place
-images included photographs of indoor and outdoor places selected from the SUN
+images included photographs of indoor and outdoor scenes selected from the SUN
 database~\citep{XiaoEtal10}. The images we used from both databases came from a
@@
 
-We used the eye-tracking data to home in specifically on behavioral effects
-related to \textit{covert} attention, as opposed to overt looking effects.
-Specifically, we excluded from further analysis any images from trials where
-participants shifted their gaze (for any non-zero amount of time) to any part
-of the attended composite image during a presentation trial
-(see Figs.~\gazeLocations,~and \excludedTrials).
+We used the eye-tracking data to home in on behavioral effects related to
+\textit{covert} attention, as opposed to overt looking effects. Specifically,
+we excluded from further analysis any images from trials where participants
+shifted their gaze (for any non-zero amount of time) to any part of the
+attended composite image during a presentation trial (see
+Figs.~\gazeLocations,~and \excludedTrials).
 
@@
 category-matched images from the unattended location (sustained: $t$s$(29) \geq
-3.366, p$s$ \leq 0.002$; variable: $t$s$(22) \geq 4.773, p$s$ \leq 0.001$),
+3.366,~p$s~$\leq 0.002$; variable: $t$s$(22) \geq 4.773,~p$s~$\leq 0.001$),
 attended-location images from the unattended category (sustained: $t$s$(29)
-\geq 5.886, p$s$ \leq 0.001$; variable: $t$s$(29) \geq 4.277, p$s$ \leq
+\geq 5.886,~p$s~$\leq 0.001$; variable: $t$s$(29) \geq 4.277,~p$s~$\leq
 0.001$), images from the unattended category and location (sustained: $t$s$(29)
-\geq 6.628, p$s$ \leq 0.001$; variable: $t$s$(29) \geq 5.624, p$s$ \leq
-0.001$), and novel images (sustained: $t$s$(29) \geq 5.987, p$s$ \leq 0.001$;
-variable: $t$s$(29) \geq 5.132, p$s$ \leq 0.001$). Taken together, the above
+\geq 6.628,~p$s~$\leq 0.001$; variable: $t$s$(29) \geq 5.624,~p$s~$\leq
+0.001$), and novel images (sustained: $t$s$(29) \geq 5.987,~p$s~$\leq 0.001$;
+variable: $t$s$(29) \geq 5.132,~p$s~$\leq 0.001$). Taken together, the above
 results suggest that what we remember is guided in part by what we attended to,
@@
 according to whether it matched the cued category and/or location. We discarded
-any face or place images that did not appear in the participants' memory phase.
-We tagged the remaining (probed) images with the familiarity ratings that
-participants would later give the images during the memory phase and plotted
-these ratings against the images' presentation positions
+any face or place images that did not appear in the participants' memory
+phases. We tagged the remaining (probed) images with the familiarity ratings
+that participants would later give the images during the memory phase and
+plotted these ratings against the images' presentation positions
 (Figs.~\ref{fig:timecourses}A and B). Across both experimental conditions and
@@
 match means that the cues are for the same location. This yielded, for each
-target image, an associated count of how many matching attention cues the
-participant had received up to and including that image's presentation. As
-shown in Figure~\sequenceLength, we used linear regressions of familiarity
-ratings on sequence lengths to identify potential sequence length effects. For
-both experimental conditions, all attention levels, and for all three
-approaches to defining matching cue sequence lengths, we found virtually no
-reliable associations between cue sequence length and familiarity. This finding
-is most parsimonious with the first possibility mentioned above-- i.e., that
-attention may be guided by a brief trigger, but that different forms of
+target image, an associated count of how many successive matching attention
+cues the participant had received up to and including that image's
+presentation. As shown in Figure~\sequenceLength, we used linear regressions of
+familiarity ratings on sequence lengths to identify potential sequence length
+effects. For both experimental conditions, all attention levels, and for all
+three approaches to defining matching cue sequence lengths, we found virtually
+no reliable associations between cue sequence length and familiarity. This
+finding is most parsimonious with the first possibility mentioned above-- i.e.,
+that attention may be guided by a brief trigger, but that different forms of
 attention may take differently long to affect memory encoding.
@@
 participants tended to rate novel images as more familiar if they came from the
-just-cued category (Fig.~\responseBias A; $t(29) = 4.371, p < 0.001$).
-Responses biases are more difficult to evaluate in the variable attention
-condition. For example, should cue recency be defined as the number studied
-composite image pairs that came between the image whose familiarity the
-participant is judging and the most recent same-category cue (i.e., distance to
-the nearest same-category attention cue)? Or might response biases instead
-arise when a given category is cued more often near the end of the just-studied
-list? We assigned each probed image a label based on these two measures of
-category-matched cue recency. We then used linear regressions of familiarity
-ratings on these recency measures to identify potential response biases
-(Fig.~\responseBias B). Altogether we found no evidence that participants in
-the variable attention condition tended to rate images as more familiar solely
-due to how recently they had received a same-category attention cue.
+just-cued category versus the unattended category (Fig.~\responseBias A; $t(29)
+= 4.371, p < 0.001$). Responses biases are more difficult to evaluate in the
+variable attention condition. For example, should cue recency be defined as the
+number studied composite image pairs that came between the image whose
+familiarity the participant is judging and the most recent same-category cue
+(i.e., temporal distance to the nearest same-category attention cue)? Or might
+response biases instead arise when a given category is cued more often near the
+end of the just-studied list? We assigned each probed image a label based on
+these two measures of category-matched cue recency. We then used linear
+regressions of familiarity ratings on these recency measures to identify
+potential response biases (Fig.~\responseBias B). Altogether we found no
+evidence that participants in the variable attention condition tended to rate
+images as more familiar solely due to how recently they had received a
+same-category attention cue.
 
@@
   \caption{\textbf{How do covert location-based and category-based attention
-  affect memory encoding?}\textbf{A. Hypothesized time courses of the impact of
+  affect memory encoding?} \textbf{A.~Hypothesized time courses of the impact of
   location-based and category-based attention on memory encoding.} Shifting the
@@
   slowly (longer than the duration of a single image presentation in the
-  experiment). \textbf{B. Location-based attention.} Focusing covert attention
+  experiment). \textbf{B.~Location-based attention.} Focusing covert attention
   on one \textit{location} enhances encoding of stimuli at the attended
@@
   is based on the variable attention results presented in
-  Fig.~\ref{fig:familiarity}.) \textbf{C. Category-based attention.} Focusing
+  Fig.~\ref{fig:familiarity}.) \textbf{C.~Category-based attention.} Focusing
   covert attention on one \textit{category} suppresses encoding of stimuli from
@@
 unattended category were not. Participants in the variable attention condition
-showed the opposite pattern. The variable attention participants rated
-attended-\textit{location} images from the unattended category as more familiar
-than novel images, but they rated attended-category images from the unattended
-location similarly to novel images. Because the primary difference between the
-sustained and variable attention conditions was the duration of participants'
-focus of attention, our analyses of partially attended images suggest that the
-effects of different aspects of attention on memory may unfold over different
-timescales (Fig.~\ref{fig:discussion}). Specifically, location-based attention
-appears to affect memory encoding relatively quickly, which would explain why
-attended-location images from both the attended \textit{and} unattended
-category receive a memory encoding benefit in the variable attention condition.
-In contrast, category-based attention appears to affect memory encoding more
-slowly, and it appears to operate in a ``suppressive'' manner (i.e.,
-suppressing encoding of the unattended category, as opposed to enhancing
-encoding of the attended category). This would explain why unattended-category
-images at the attended location are rated as \textit{less} familiar in the
-sustained attention condition.
+showed the opposite pattern. In particular, variable attention participants
+rated attended-\textit{location} images from the unattended category as more
+familiar than novel images, but they rated attended-category images from the
+unattended location similarly to novel images. Because the primary difference
+between the sustained and variable attention conditions was the duration of
+participants' focus of attention, our analyses of partially attended images
+suggest that the effects of different aspects of attention on memory unfold
+over different timescales (Fig.~\ref{fig:discussion}). Specifically,
+location-based attention appears to affect memory encoding relatively quickly,
+which would explain why attended-location images from both the attended
+\textit{and} unattended category receive a memory encoding benefit in the
+variable attention condition. In contrast, category-based attention appears to
+affect memory encoding more slowly, and it appears to operate in a
+``suppressive'' manner (i.e., suppressing encoding of the unattended category,
+as opposed to enhancing encoding of the attended category). This would explain
+why unattended-category images at the attended location are rated as
+\textit{less} familiar in the sustained attention condition.
 
@@
 impacts of location-based attention (enhancement with a fast onset) and
-category-based attention (inhibition with a slow onset) and on subsequent
+category-based attention (suppression with a slow onset) and on subsequent
 recognition memory. Both of these effects persisted throughout the 2~min memory
-phases of both conditions. Therefore future work is needed to elucidate the
+phases of both conditions. However, future work is needed to elucidate the
 longevity of these effects beyond 2 minutes.
@@
 JRM and KZ developed the concept for this study. Experiment code was written by
-KZ and ARM, and testing and data collection were conducted by MRL and KZ. KZ,
-MRL, ARM, and JRM analyzed the data. JRM supervised the project. All authors
-contributed to writing and editing the manuscript.
+ARM and KZ, and testing and data collection were conducted by KZ and MRL. All
+authors contributed to analyzing the data. All authors contributed to writing
+and editing the manuscript.  JRM supervised the project.
 

### 2023-03-27 paper/supplemental_materials.tex
minor wording tweaks, typo and formatting fixes

@@
  roughly 0.5~cm square. The panels display the average proportions of time
- (throughout the duration of the experiment) participants spend looking at each
+ (throughout the duration of the experiment) participants spent looking at each
  location. The left panel displays data from participants in the sustained
@@
 Fig.~\ref{fig:gaze-histograms}). \textbf{A--B. Proportions of excluded trials,
-by run.} Across both experimental conditions (left: sustained attention; right:
-variable attention), the bars display the average proportions of presentations
-from each run where participants looked at any part of the attended composite
-image, for any non-zero duration. Error bars denote across-participant
-bootstrap-estimated 95\% confidence intervals. \textbf{C--D. Proportions of
-excluded trials, by participant.} Across both experimental conditions (left:
-sustained attention; right: variable attention), the bars display the average
-proportions of presentations across different runs where the given
-participants looked at any part of the attended composite image, for any
-non-zero duration. Error bars denote across-run bootstrap-estimated 95\%
+by trial block.} Across both experimental conditions (left: sustained
+attention; right: variable attention), the bars display the average proportions
+of presentations from each trial block where participants looked at any part of the
+attended composite image, for any non-zero duration. Error bars denote
+across-participant bootstrap-estimated 95\% confidence intervals. \textbf{C--D.
+Proportions of excluded trials, by participant.} Across both experimental
+conditions (left: sustained attention; right: variable attention), the bars
+display the average proportions of presentations across different runs where
+the given participants looked at any part of the attended composite image, for
+any non-zero duration. Error bars denote across-block bootstrap-estimated 95\%
 confidence intervals.}
 
-  \label{fig:gaze-histograms}
+  \label{fig:gaze-intersections}
 \end{figure*}
@@
 \caption{\textbf{Effects of attention cue sequence length on familiarity.} 
-\textbf{A. Sequence effects (sustained attention condition).} Each heat map
+\textbf{A. Sustained attention condition.} Each heat map
 displays the proportions of images that participants rated at each familiarity
@@
 colors) denote attention levels (as in Figs.~\familiarity~and
-\ref{fig:ratings-by-category}). \textbf{B. Sequence effects (variable attention
-condition).} This Panel is in the same format as Panel A, but displays results
+\ref{fig:ratings-by-category}). \textbf{B. Variable attention
+condition.} This panel is in the same format as Panel A, but displays results
 from the variable attention condition.}
@@
 0.05$, and $x$ is the cue's presentation position. To obtain the $y$-values
-shown in the Panel (and used in Panel B), the weights for $x \in \left[0, 1, 2,
+shown in the panel (and used in Panel B), the weights for $x \in \left[0, 1, 2,
 ..., 9\right]$ are normalized to sum to 1.}

### 2023-03-27 paper/admin/cover_letter.tex
lots of bug fixes (no results are affected; all bugs were related to running the code in a fresh environment)

@@
-\title{Psychological Science Submission Letter}
-%
-% See http://texblog.org/2013/11/11/latexs-alternative-letter-class-newlfm/
-% and http://www.ctan.org/tex-archive/macros/latex/contrib/newlfm
-% for more information.
-%
 \documentclass[10pt,stdletter,orderfromtodate,sigleft]{newlfm}
@@
 
-\greetto{To the editors of \textit{Psychological Science}:}
+\greetto{To the editors of \textit{Scientific Reports}:}
 
@@
 \begin{newlfm}
-We have enclosed our manuscript entitled \textit{Feature-based and
-  location-based volitional covert attention affect memory at different timescales}, which we wish
-to submit for publication as a Research Article in
-\textit{Psychonomic Bulletin \& Review}.
 
-Our manuscript reports two experiments that examine how feature-based
-and location-based attention affect recognition memory.  We asked our
-participants to view a series of composite (blended face-scene) image
-pairs.  We instructed the participants to focus their attention to a
-specific image category (face or scene) and location (left or right)
-without moving their eyes from a central fixation point.  The two
-experiments differed in how often we changed the attention cue.  We
-found that the memory consequences of location-based attention were
-measurable after just a single attention cue instruction
-(5.5~seconds), and persisted for at least 2~minutes.  Our data suggest
-that location-based attention enhances memory encoding at the attended
-location.  By contrast, feature-based attention must be sustained for
-an extended interval to substantially affect memory.  Our data suggest
-that feature-based attention suppresses the encoding into memory of
-unattended stimulus features.
+We have enclosed our manuscript entitled \textit{Category-based and
+location-based volitional covert attention affect memory at different
+timescales}, which we wish to submit for publication as an Article in
+\textit{Scientific Reports}.
+
+Our manuscript reports our findings from an experiment designed to study how
+different aspects of covert attention affect memory. Our experiment comprised
+two conditions that asked participants to \textit{sustain} or \textit{vary} the
+focus of their covert attention, respectively, with respect to each of a series
+of stimuli. Each stimulus comprised a pair of images (one on the left of the
+screen and the other on the right), and each image comprised an equal blend of
+a photograph of a face and a photograph of a scene. During each stimulus
+presentation, we instructed participants to focus in on either the face or
+scene component of either the left or right image \textit{without moving their
+eyes}. (This is quite difficult to do naively, so we trained participants to do
+this quickly and at will using a practice session prior to the main
+experiment.) We used eye-tracking data to focus in on trials where participants
+were specifically varying their focus of \textit{covert} attention (i.e., with
+no change in where they were looking), as opposed to simply moving their eyes
+to look at the to-be-attended images. We then administered recognition memory
+tests that asked participants to rate the ``familiarity'' of attended,
+unattended, and novel images.
+
+As we anticipated, participants in both conditions remembered stimuli they
+attended to better than unattended stimuli, and they rated both attended and
+unattended stimuli they had seen as more ``familiar'' than novel images, during
+a recognition memory test. We also found some interesting differences across
+the two experimental conditions pertaining to how participants remembered
+``partially attended'' stimuli. When participants varied the focus of their
+attention more often, their memory was more influenced by location-based
+attention (regardless of which image category they were attending). In
+contrast, when participants sustained the focus of their attention over longer
+intervals, their memory was more influenced by category-based attention
+(regardless of which location they were attending). Our findings highlight a
+dissociation between how location-based and category-based attention affect
+memory encoding (and subsequent recognition). Location-based attention appears
+to affect memory encoding on relatively short timescales by enhancing encoding
+for stimuli at the attended location. On the other hand, category-based
+attention appears to affect memory encoding on longer timescales by
+\textit{suppressing} stimuli from the unattended category.
 
@@
 
-We have suggested the following scientists as expert reviewers: Marvin
-Chun (Marvin.Chun@Yale.edu), Brice Kuhl (bkuhl@uoregon.edu), Joel Voss (Joel-Voss@Northwestern.edu),
-Edward Vogel (Ed\-Vogel@UChi\-ca\-go.edu), and Judith Fan
-(jefan@ucsd.edu).  We have also published and documented all of our
-experimental stimuli, code, and data, along with the code used to
-generate the figures and analyses we report in our manuscript.  These
-may be found at
+We have suggested the following scientists as expert reviewers: Marvin Chun
+(Marvin.Chun@Yale.edu), Brice Kuhl (bkuhl@uoregon.edu), Joel Voss
+(Joel-Voss@Northwestern.edu), Edward Vogel (Ed\-Vogel@UChi\-ca\-go.edu), and
+Judith Fan (jefan@ucsd.edu). We have also published and documented all of our
+experimental stimuli, code, and data, along with the code used to generate the
+figures and analyses we report in our manuscript. These may be found at
 \href{https://github.com/ContextLab/attention-memory-task}{\texttt{https://github.com/ContextLab/attention-memory-task}}.

### 2023-03-27 code/helpers.py

@@ -1,4 +1,6 @@
 import os
+import shutil
+import time
 import requests
 import pandas as pd
 import numpy as np
@@ -9,6 +11,7 @@ from matplotlib import pyplot as plt
 
 from tqdm import tqdm
 from glob import glob as lsdir
+from datetime import datetime
 
 basedir = os.path.split(os.getcwd())[0]
 datadir = os.path.join(basedir, 'data')
@@ -32,7 +35,7 @@ attention_colors = {
 
 
 def download_data():
-    data_url = 'https://www.dropbox.com/s/99ty0ok8p4m5ijc/data.zip?dl=1'
+    data_url = 'https://www.dropbox.com/s/6w8iemlqjyubn05/data.zip?dl=1'
     data_fname = os.path.join(basedir, 'data.zip')
     checkfile_fname = os.path.join(datadir, 'checkfile.txt')
 
@@ -43,9 +46,9 @@ def download_data():
 
     if os.path.exists(data_fname) and not os.path.exists(checkfile_fname):
         print('Unzipping data...')
-        os.system(f'unzip -q {data_fname} -d {basedir}')
-        os.system(f'rm {data_fname}')
-        os.system(f'rm -rf {basedir}/__MACOSX')
+        shutil.unpack_archive(data_fname, basedir)        
+        shutil.rmtree(os.path.join(basedir, '__MACOSX'))
+        os.remove(data_fname)
 
         with open(checkfile_fname, 'w') as f:
             f.write('download complete.')
@@ -144,7 +147,7 @@ def parse_gaze_data(datadir):
              'y': ['values', 'frame', 'avg', 'y'],
             'Pupil size': [['values', 'frame', 'lefteye', 'psize'], ['values', 'frame', 'righteye', 'psize']]}
 
-    str2unix = lambda t: time.mktime(datetime.strptime(t, '%Y-%m-%d %H:%M:%S.%f').timetuple())
+    str2unix = lambda t: time.mktime(datetime.strptime(t, '%Y-%m-%d %H:%M:%S.%f').timetuple()) if type(t) is str else -1
     
     def helper(subjdir):
         subj = os.path.basename(subjdir)

### 2023-03-27 code/helpers.py
confirm all analyses run in a clean environment

@@ -46,8 +46,7 @@ def download_data():
 
     if os.path.exists(data_fname) and not os.path.exists(checkfile_fname):
         print('Unzipping data...')
-        shutil.unpack_archive(data_fname, basedir)        
-        shutil.rmtree(os.path.join(basedir, '__MACOSX'))
+        shutil.unpack_archive(data_fname, datadir)
         os.remove(data_fname)
 
         with open(checkfile_fname, 'w') as f:

### 2023-03-27 paper/admin/cover_letter.tex
udpated cover letter

@@
 \usepackage{blindtext, xfrac, animate, hyperref, pxfonts}
+\usepackage[subtle]{savetrees}
 
@@
 \newlfmP{dateskipbefore=0pt}
-\newlfmP{sigsize=20pt}
+\newlfmP{sigsize=10pt}
 \newlfmP{sigskipbefore=10pt}
@@
 \namefrom{Jeremy R. Manning, Ph.D.}
-\addrfrom{
-	Dartmouth College\\
-  Department of Psychological \& Brain Sciences\\
-  HB 6207 Moore Hall\\
-	Hanover, NH  03755}
+\addrfrom{}
 
 \addrto{}
-\dateset{\today}
+\dateset{}
 
-\greetto{To the editors of \textit{Scientific Reports}:}
+\greetto{\vspace{-1in}To the editors of \textit{Scientific Reports}:}
 
@@
 
-As we anticipated, participants in both conditions remembered stimuli they
+As we had expected, participants in both conditions remembered stimuli they
 attended to better than unattended stimuli, and they rated both attended and
 unattended stimuli they had seen as more ``familiar'' than novel images, during
-a recognition memory test. We also found some interesting differences across
-the two experimental conditions pertaining to how participants remembered
-``partially attended'' stimuli. When participants varied the focus of their
-attention more often, their memory was more influenced by location-based
-attention (regardless of which image category they were attending). In
-contrast, when participants sustained the focus of their attention over longer
-intervals, their memory was more influenced by category-based attention
-(regardless of which location they were attending). Our findings highlight a
-dissociation between how location-based and category-based attention affect
-memory encoding (and subsequent recognition). Location-based attention appears
-to affect memory encoding on relatively short timescales by enhancing encoding
-for stimuli at the attended location. On the other hand, category-based
-attention appears to affect memory encoding on longer timescales by
-\textit{suppressing} stimuli from the unattended category.
+a recognition memory test. In addition, we also found some interesting
+(unexpected) differences across the two experimental conditions pertaining to how
+participants remembered ``partially attended'' stimuli. When participants
+varied the focus of their attention more often, their memory was more
+influenced by location-based attention (regardless of which image category they
+were attending). In contrast, when participants sustained the focus of their
+attention over longer intervals, their memory was more influenced by
+category-based attention (regardless of which location they were attending).
+Our findings highlight a dissociation between how location-based and
+category-based attention affect memory encoding (and subsequent recognition).
+Location-based attention appears to affect memory encoding on relatively short
+timescales by enhancing encoding for stimuli at the attended location. On the
+other hand, category-based attention appears to affect memory encoding on
+longer timescales by \textit{suppressing} stimuli from the unattended category.
 
-The impact of attention on memory is of central importance to a wide
-variety of scientifically and socially current issues.  For example,
-the interplay between attention and memory affects how we remember our
-ongoing experiences in everyday life, how students learn in the
-classroom (and which teaching strategies might be most effective), how
-(or whether) we recognize a face we notice in a crowd and
-happen to encounter later, and so on.  These issues also relate to
-attention disorders (e.g., ADD, ADHD) and memory disorders
-(e.g., age-related memory impairment, Alzheimer's, etc.).  Discovering
-the mechanisms that underlie how our experiences are encoded into
-memories can lead to new tools for identifying when those mechanisms
-are not operating within their expected parameters.
+The impact of attention on memory is of central importance to a wide variety of
+scientifically and socially current issues. For example, the interplay between
+attention and memory affects how we remember our ongoing experiences in
+everyday life, how students learn in the classroom (and which teaching
+strategies might be most effective), how (or whether) we recognize a face we
+notice in a crowd and happen to encounter later, and so on. These issues also
+relate to attention disorders (e.g., ADD, ADHD) and memory disorders (e.g.,
+age-related memory impairment, Alzheimer's, etc.). Discovering the processes
+that guide how our experiences are encoded into memories can lead to new tools
+for identifying when those processes are not operating within their expected
+parameters.
 
-We have suggested the following scientists as expert reviewers: Marvin Chun
-(Marvin.Chun@Yale.edu), Brice Kuhl (bkuhl@uoregon.edu), Joel Voss
-(Joel-Voss@Northwestern.edu), Edward Vogel (Ed\-Vogel@UChi\-ca\-go.edu), and
-Judith Fan (jefan@ucsd.edu). We have also published and documented all of our
-experimental stimuli, code, and data, along with the code used to generate the
-figures and analyses we report in our manuscript. These may be found at
+In the spirit of reproducibility and transparency, we have also published and
+documented all of our experimental stimuli, code, and data, along with the code
+used to generate the figures and analyses we report in our manuscript. These
+may be found at
 \href{https://github.com/ContextLab/attention-memory-task}{\texttt{https://github.com/ContextLab/attention-memory-task}}.
 
-Thank you for considering our manuscript for publication in
-Psychonomic Bulletin \& Review.
+Thank you for considering our manuscript for publication in \textit{Scientific Reports}.
 

### 2023-03-29 paper/main.tex
updated abstract (removed/replaced some sentences that no longer apply to the updated version of the manuscript)

@@
 crowd versus a desired item in a grocery store). We ran a covert attention
-experiment with two conditions that differed in how long they asked
-participants to maintain the focus of the categories and locations they were
-attending. Later, the participants performed a recognition memory task for
-attended, unattended, and novel stimuli. Participants were able to shift the
-location of their covert attentional focus more rapidly than they were able to
-shift their focus of covert attention to stimulus categories, and the effects
-of location-based attention on memory were longer-lasting than the effects of
-category-based attention.
+experiment with two conditions that asked participants to either sustain or
+vary the focus of the categories and locations they were attending. Later, the
+participants performed a recognition memory task for attended, unattended, and
+novel stimuli. Participants in both conditions recognized attended stimuli more
+readily than unattended or novel stimuli. Participants in the ``sustained
+attention'' condition also exhibited a recognition advantage for
+attended-category images from the unattended location, whereas participants in
+the ``variable attention'' condition exhibited a recognizing advantage for
+attended-location images from the unattended category. Our findings suggest
+that covert attention enhances memory encoding of attended stimuli, and that
+different aspects of partial attention affect memory encoding over different
+timescales.
 

### 2023-03-31 paper/main.tex
Several changes and fixes:   - Added statistical tests for the "place versus face" familiarity differences in both conditions   - Added several citations recommended by reviewers from previous versions of the manuscript

@@
 more familiar than attention-matched face images (compare dark versus light
-bars in Fig.~\ratingsByCategory). We hypothesized that this might be
-explainable by some property of the relevant cognitive processes or by
-properties of the stimuli themselves. To help elucidate this distinction, we
-examined individual exemplars of the face and place images used in our paradigm
-(Fig.~\ref{fig:stimuli}A). By design, the face images had consistent head
-sizes, viewing angles, expressions, and so on. In contrast, the place images
-varied more substantially across images. For example, some place images
-depicted human-made structures; others depicted natural scenes; some depicted
-indoor views; others depicted outdoor views; etc. This can also be seen by
-averaging the pixel intensity values across images, separately for the face and
-place stimuli (Fig.~\ref{fig:stimuli}B). Whereas the average face image retains
-many of the landmarks characteristic of most faces (e.g., clearly defined hair,
-eyes, nose, mouth, head shape, etc.), the average place image does not show
-place-specific features as clearly, aside from a general tendency for the tops
-of place images to be lighter than the bottoms of place images. We also
-computed the pairwise similarities across images from each stimulus category
-(Fig.~\ref{fig:stimuli}C) and found that face images tended to be much more
-similar to each other than place images (Fig.~\ref{fig:stimuli}D; $t(115258) =
-254.764, p < 0.001$). This analysis indicated to us that our experimental
-paradigm was not well-suited to identifying cognitively meaningful stimulus
-category differences, since participants' category-specific judgements may be
-confounded with within-category image similarity differences.
+bars in Fig.~\ratingsByCategory; sustained attention: $t(29) = 1.746, p =
+0.091$; variable attention: $t(22) = 2.660, p = 0.014$). We hypothesized that
+this might be explainable by either some property of the relevant cognitive
+processes or by properties of the stimuli themselves. To help elucidate this
+distinction, we examined individual exemplars of the face and place images used
+in our paradigm (Fig.~\ref{fig:stimuli}A). By design, the face images had
+consistent head sizes, viewing angles, expressions, and so on. In contrast, the
+place images varied more substantially across images. For example, some place
+images depicted human-made structures; others depicted natural scenes; some
+depicted indoor views; others depicted outdoor views; etc. This can also be
+seen by averaging the pixel intensity values across images, separately for the
+face and place stimuli (Fig.~\ref{fig:stimuli}B). Whereas the average face
+image retains many of the landmarks characteristic of most faces (e.g., clearly
+defined hair, eyes, nose, mouth, head shape, etc.), the average place image
+does not show place-specific features as clearly, aside from a general tendency
+for the tops of place images to be lighter than the bottoms of place images. We
+also computed the pairwise similarities across images from each stimulus
+category (Fig.~\ref{fig:stimuli}C) and found that face images tended to be much
+more similar to each other than place images (Fig.~\ref{fig:stimuli}D;
+$t(115258) = 254.764, p < 0.001$). This analysis indicated to us that our
+experimental paradigm was not well-suited to identifying cognitively meaningful
+stimulus category differences, since participants' category-specific judgements
+may be confounded with within-category image similarity differences.
 
@@
 between attention and memory~\citep{PallWagn02, ChunTurk07, AlyTurk16,
-AlyTurk17, WittEtal18, MorrEtal14, BaleEtal21}. Whereas much of this prior work
-focused on elucidating the neural basis of these interactions, our work extends
-these prior studies by elucidating the specific and separable behavioral
-impacts of location-based attention (enhancement with a fast onset) and
-category-based attention (suppression with a slow onset) and on subsequent
-recognition memory. Both of these effects persisted throughout the 2~min memory
-phases of both conditions. However, future work is needed to elucidate the
-longevity of these effects beyond 2 minutes.
+AlyTurk17, WittEtal18, MorrEtal14, BaleEtal21, UncaEtal11, TurkEtal13,
+LaRoEtal15}. Whereas much of this prior work focused on elucidating the neural
+basis of these interactions, our work extends these prior studies by
+elucidating the specific and separable behavioral impacts of location-based
+attention (enhancement with a fast onset) and category-based attention
+(suppression with a slow onset) and on subsequent recognition memory. Both of
+these effects persisted throughout the 2~min memory phases of both conditions.
+However, future work is needed to elucidate the longevity of these effects
+beyond 2 minutes.
 
@@
 category-based and location-based attention are mediated by different brain
-structures may explain why these different aspects of attention operate on
-different timescales and affect memory differently. A strong test of this
-hypothesis would entail directly measuring neural activity patterns as people
-modulate their focus of attention (e.g., using functional magnetic resonance
-imaging or electroencephalography), and then using neural decoding
-approaches~\citep[e.g.,][]{HaxbEtal01, NormEtal06b, MannEtal18, OwenEtal21} to
-follow how neural representations of attended (or unattended) stimuli are
-transfered from primary sensory regions, to higher order sensory regions, to
-memory areas. If the effects of attention on memory are mediated by changes in
-network dynamics, the transmission rates of the representations of attended
-stimuli from primary sensory regions to memory areas should be facilitated
-relative to the transmission rates of unattended stimuli. Further, variability
-in these neural changes (e.g., as a participant focuses their attention with
-more or less success) should track with behavioral measures of memorability.
+structures~\citep[e.g.,][ and others]{GiesEtal03} may explain why these
+different aspects of attention operate on different timescales and affect
+memory differently. A strong test of this hypothesis would entail directly
+measuring neural activity patterns as people modulate their focus of attention
+(e.g., using functional magnetic resonance imaging or electroencephalography),
+and then using neural decoding approaches~\citep[e.g.,][]{HaxbEtal01,
+NormEtal06b, MannEtal18, OwenEtal21} to follow how neural representations of
+attended (or unattended) stimuli are transfered from primary sensory regions,
+to higher order sensory regions, to memory areas. If the effects of attention
+on memory are mediated by changes in network dynamics, the transmission rates
+of the representations of attended stimuli from primary sensory regions to
+memory areas should be facilitated relative to the transmission rates of
+unattended stimuli. Further, variability in these neural changes (e.g., as a
+participant focuses their attention with more or less success) should track
+with behavioral measures of memorability.
 

### 2023-04-08 paper/main.tex
added a new response bias analysis comparing attended-category targets vs. lures in the sustained condition

@@
 just-cued category versus the unattended category (Fig.~\responseBias A; $t(29)
-= 4.371, p < 0.001$). Responses biases are more difficult to evaluate in the
-variable attention condition. For example, should cue recency be defined as the
-number studied composite image pairs that came between the image whose
+= 4.371, p < 0.001$). Nonetheless, participants' familiarity ratings in the
+sustained attention condition cannot be explained solely by response biases.
+For example, participants rate attended-category targets (i.e.,
+attended-category images they encountered at the unattended location) as more
+familiar than attended-category lures (i.e., attended-category novel images);
+$t(29) = 2.645, p = 0.013$. Responses biases are more difficult to evaluate in
+the variable attention condition. For example, should cue recency be defined as
+the number studied composite image pairs that came between the image whose
 familiarity the participant is judging and the most recent same-category cue

### 2023-04-10 paper/main.tex
typo fix in abstract

@@
 attended-category images from the unattended location, whereas participants in
-the ``variable attention'' condition exhibited a recognizing advantage for
+the ``variable attention'' condition exhibited a recognition advantage for
 attended-location images from the unattended category. Our findings suggest

### 2023-04-16 paper/main.tex
formatting changes requested by editor

@@
 \usepackage{hyperref}
-\usepackage[sort]{natbib}
+\usepackage[sort, square, numbers, compress]{natbib}
 \usepackage{pxfonts}
@@
 and data, may be downloaded from
-\url{http://www.github.com/ContextLab/attention-memory-task}.
+\url{http://www.github.com/ContextLab/attention-memory-task}. All methods were
+performed in accordance with the relevant duidelines and regulations, and our
+experimental protocol was approved by the Committee for the Protection of Human
+Subjects at Dartmouth College.
 
@@
 positions) in general the average ordering of familiarity ratings by attention
-level (Fig.~\ref{fig:familiarity}) were preserved. This suggests that the
-retrieval-related affects of attention on subsequent recognition memory are
-relatively stable over time (e.g., we did not observe clear primacy or recency
-effects during the memory phase of the experiment).
+level (Fig.~\ref{fig:familiarity}) were preserved (Figs.~\ref{fig:timecourses}C
+and D). This suggests that the retrieval-related affects of attention on
+subsequent recognition memory are relatively stable over time (e.g., we did not
+observe clear primacy or recency effects during the memory phase of the
+experiment).
 

### 2023-04-16 paper/main.tex
more formatting fixes to address editor requests

@@
 \usepackage{setspace}
-\usepackage{apacite}
+%\usepackage{apacite}
 \usepackage{hyperref}
 \usepackage[sort, square, numbers, compress]{natbib}
+%\usepackage[english]{babel}
+%\usepackage[backend=biber, natbib=true, style=numeric, sorting=true]{biblatex}
 \usepackage{pxfonts}
@@
 \url{http://www.github.com/ContextLab/attention-memory-task}. All methods were
-performed in accordance with the relevant duidelines and regulations, and our
+performed in accordance with the relevant guidelines and regulations, and our
 experimental protocol was approved by the Committee for the Protection of Human
@@
 
-\bibliographystyle{apacite}
+\bibliographystyle{naturemag}
 \bibliography{CDL-bibliography/cdl}
